\chapter{CGL extensions}\label{sec:cgl_extensions}
\chaptertoc

\noindent
In this chapter we will look at a purely algebraic method of placing a quantum cluster
algebra structure on a certain class of algebras as first presented by
\textcite{GoodearlYakimov2017QCA}. Not only do these have the structure of a quantum
cluster algebra, they also equal the corresponding upper cluster algebra. This class of
algebras are the so-called CGL extensions. Among this class of algebras are the quantum
Schubert cell algebras which include quantized matrix coordinate algebras as a special
case. In a follow-up paper \cite{GoodearlYakimov2020BerensteinZelivinskyQCAC}, these
results were used to place quantum cluster algebra structures on the coordinate
algebras of double Bruhat cells by viewing them as localizations of certain CGL
extensions. This resolved some open conjectures at the time.

We will first look at what CGL extensions are, and then build up some intuition for why
one should expect a quantum cluster algebra structure on them. Afterwards we will make
explicit the quantum cluster algebra structure, and prove its existence. Along the way
we will work out examples to show how the results can be used to construct the quantum
cluster algebra structure in practice. As mentioned the method is purely algebraic, and
does not rely on geometric structures related to the algebra. In the end, constructing
the initial quantum seed can be done almost algorithmically from the data of the CGL
extension.

Throughout this chapter, we use the same notation as in
\cref{sec:quantum_cluster_algebras}. Thus, in particular, $\bbK$ is a field of
arbitrary characteristic, and $N$ is a strictly positive integer.

\section{Quantum tori and mutations hidden in CGL extensions}\label{sec:cgl_introduction}

We start with a quick introduction to CGL extensions, and work our way to understanding
how a cluster algebra structure arises naturally. The focus is on building a solid
understanding and intuition, and as such, plenty of examples are worked out. The later
sections will be devoted to formulating a precise statement about the cluster algebra
structure, and proving this statement.

\subsection{CGL extensions}

Before studying the quantum cluster algebra structure on a CGL extension, we must first
know what a CGL extension is. The building block is an \emph{Ore extension}. These
noncommutative analogues of polynomial algebras appear naturally in different contexts
such as group algebras and coordinate algebras.

\begin{definition}
	Let $R$ be a ring with unit, $\sigma \colon R \to R$ a ring endomorphism and
	$\delta \colon R \to R$ a $\sigma$-\emph{derivation}\index{ring!-derivation}\index{s@$\sigma$-derivation}, i.e.,
	$\delta$ is a group homomorphism $(R, +) \to (R, +)$ such that $\delta (r s) =
		\sigma(r)\delta(s) + \delta(r) s$. Then we write $R[x;\sigma, \delta]$\index{R@$R[x;\sigma,\delta]$} for the ring generated by $R$ and a formal variable $x$ with the additional relation that
	\begin{equation*}
		x r = \sigma(r) x + \delta(r)
	\end{equation*}
	%
	for all $r \in R$. We call $R[x;\sigma, \delta]$ an \emph{Ore extension}\index{Ore
		extension} or \emph{skew polynomial ring}\index{ring!skew polynomial}. The conditions
	on $\sigma$ and $\delta$ ensure that there are no ``hidden'' relations.
\end{definition}
%
\begin{convention}
	%
	In what follows, when $R[x;\sigma, \delta]$ is an Ore extension, $R$ is a
	$\bbK$-algebra, $\sigma$ is a $\bbK$-algebra \emph{automorphism} and $\delta$ is a
	$\bbK$-linear $\sigma$-derivation. In this case, $R[x;\sigma, \delta]$ is also a
	$\bbK$-algebra.
\end{convention}
%
Under these assumptions, the Ore extension $R[x; \sigma, \delta]$ is Noetherian when
$R$ is Noetherian. It will also be a domain if $R$ is a domain.

\begin{example}
	Let $A_1(\bbK)$\index{A@$A_1(\bbK)$} be the $\bbK$-algebra generated by two variables $x$ and $y$ such that $yx =
		xy + 1$. This algebra is known as the \emph{Weyl algebra}\index{algebra!Weyl}. It can
	also be viewed as an Ore extension $\bbK[x][y; \id, \partial_x]$:
	\begin{itemize}
		\item The base algebra is the polynomial ring $\bbK[x]$.
		\item The algebra endomorphism $\sigma$ is the identity.
		\item The $\sigma$-derivation $\delta$ is the formal derivative with respect to $x$:
		      \begin{equation*}
			      \partial_x \left(\sum_{i=0}^n a_i x^i \right) \defeq \sum_{i=1}^{n} a_i i x^{i-1}.
		      \end{equation*}
		      %
		      That $\partial_x$ is a derivation follows from the ordinary product rule for derivatives.
	\end{itemize}
\end{example}

Starting from the base field $\bbK$, one can iteratively construct Ore extensions,
obtaining an algebra of the form
\begin{align*}
	R = \bbK[x_1][x_2; \sigma_2, \delta_2]\cdots[x_N; \sigma_N, \delta_N],
\end{align*}
%
Such algebras will be referred to as \emph{iterated Ore extensions}\index{Ore
	extension!iterated}. Because they share many similarities with polynomial algebras, it
will be convenient to re-use some terminology. First note that $R$ has a $\bbK$-basis
consisting of the \emph{monomials}\index{monomial}
\begin{equation*}
	\{x^f = x_1^{f_1}x_2^{f_2}\cdots x_N^{f_N} \mid f = (f_1, \dots, f_N)^T \in \bbZ_{\geq 0}^N\}.
\end{equation*}
%
This basis has a natural ordering given by the \emph{reverse lexicographic
	order}\index{reverse lexicographic order} on the exponents. Namely, $x^f \succ x^{f'}$
if and only if there exists some $i \in [1, N]$ such that $f_i > f'_i$ and $f_j = f'_j$
for all $j \in [1, N]$ with $j > i$. This is most easily understood with some examples:
\begin{equation*}
	x_N \succ x_{N-1} \succ \cdots \succ x_1, \quad x_1^2x_2 \succ x_1x_2, \quad x_2x_4 \succ x_1x_2^4 x_3^3.
\end{equation*}
%
We will write the elements of $R$ with respect to this basis, where the monomials are
ordered in descending order. For an element $a \in R \setminus \{0\}$ with
\begin{equation*}
	a = \alpha_f x^f + \sum_{g \prec f} \alpha_g x^g, \quad \alpha_f \in \bbK^\times,
\end{equation*}
%
we will say that $a$ has \emph{leading term}\index{leading term} $\lt(a) = \alpha_f
	x^f$\index{lt@$\lt(a)$} and \emph{leading coefficient}\index{leading coefficient}
$\alpha_f$.

A CGL extension will be an iterated Ore extension, together with a particular action of
a $\bbK$-torus. This ensures some uniformity between the different generators. We now
briefly introduce the necessary definitions using \cite{GoodearlBrown2002LecturesAQC}
as a reference.

Let $\mcH$ be a group, and $A$ a $\bbK$-algebra. We say that $\mcH$ \emph{acts on $A$
	by automorphisms}\index{action!by automorphisms} if for every $h \in \mcH$, the map $A
	\to A \colon x \mapsto h \cdot x$ is a $\bbK$-algebra automorphism. A nonzero element
$u \in A$ is called an \emph{$\mcH$-eigenvector}\index{H@$\mcH$!-eigenvector} if $\mcH
	\cdot u \subseteq \bbK u$. So, for each $h \in \mcH$ there exists some $\lambda_h \in
	\bbK$ such that $h \cdot u = \lambda_h u$. Since $\mcH$ acts by automorphisms,
$\lambda_h \neq 0$ for all $h \in \mcH$. So, we get a group homomorphism $\chi_u \colon
	\mcH \to \bbK^\times$ given by $\chi_u(h) = \lambda_h$. We call $\chi_u$\index{chi
	u@$\chi_u$} the \emph{$\mcH$-eigenvalue}\index{H@$\mcH$!-eigenvalue} of $u$. Associated
to each $\mcH$-eigenvalue, $\chi$, is its
\emph{$\mcH$-eigenspace}\index{H@$\mcH$!-eigenspace}
\begin{equation*}
	A_\chi = \{u \in A \mid h \cdot x = \chi(h)x,\, \forall h \in \mcH \}.
\end{equation*}
%
Finally, we say that the action is \emph{semisimple}\index{action!semisimple} if $A$ is
the direct sum of its $\mcH$-eigenspaces.

Now, let $\mcH$ be a \emph{$\bbK$-torus}\index{torus}, that is, a group of the form
$(\bbK^\times)^N$. By identifying $\mcH$ with the affine algebraic variety $\{(x_1,
	\dots, x_N, y) \in \bbK^{N+1} \mid x_1 \cdots x_N y = 1\}$, we can view it as an
algebraic group. Assume that $\mcH$ acts on a $\bbK$-algebra $A$ by $\bbK$-algebra
automorphisms. Then we say that the action of $\mcH$ on $A$ is
\emph{rational}\index{action!rational} if it is semisimple, and all the corresponding
$\mcH$-eigenvalues are morphisms of affine varieties, i.e., monomials in the $x_1^{\pm
	1}, \dotsc, x_N^{\pm 1}$.

Write
\begin{equation*}
	X(\mcH) = \{\chi \in \Hom(\mcH, \bbK^\times) \mid \chi \text{ is a morphism of algebraic varieties}\},
\end{equation*}
%
for the \emph{character group}\index{group!character} of $\mcH$. Then a rational action
is the same as an $X(\mcH)$-grading\index{grading} of $A$. Indeed, if we have a
rational action on $A$, then we can write
\begin{equation*}
	A = \bigoplus_{\chi \in X(\mcH)} A_\chi,
\end{equation*}
which is graded because for $a \in A_\chi, b \in A_{\chi'}$ and all $h \in \mcH$:
\begin{align*}
	h \cdot (a b) = (h\cdot a)(h\cdot b)= \chi(h)a \chi'(h)b = (\chi \chi')(h)ab,
\end{align*}
so that $ab \in A_{\chi \chi'}$. Conversely, if
\begin{equation*}
	A = \bigoplus_{g \in X(\mcH)} A_g
\end{equation*}
is a grading, then we get a rational action through
\begin{equation*}
	h \cdot x = h \cdot \left(\sum_{g \in X(\mcH)} x_g \right) = \sum_{g \in X(\mcH)} g(h)x.
\end{equation*}
%
Recall that a \emph{homogeneous} element of a graded ring is an element which is
contained in only one of the components. Under this correspondence, the
$\mcH$-eigenvectors are precisely the nonzero homogeneous\index{element!homogeneous}
elements under the grading.

\begin{example}
	Consider the noncommutative $\bbK$-algebra $A$ generated by $x,y,z$ with relations $xy
		-qyx = z$ and $zx = qxz$. We have an action on $A$ by $\mcH = (\bbK^\times)^2$, given
	on the generators by
	\begin{align*}
		(\xi, \eta)\cdot x & = \xi x      \\
		(\xi, \eta)\cdot y & = \eta y     \\
		(\xi, \eta)\cdot z & = \xi\eta z.
	\end{align*}
	%
	Because the action respects the relations on the generators, it follows that we can
	extend the action to the whole of $A$, such that $\mcH$ acts by automorphisms. Note
	that the generators are $\mcH$-eigenvectors, with $\mcH$-eigenvalues given by
	polynomial functions. Thus, the action is rational.

\end{example}

The combination of a rational action by a torus and iterated Ore extensions gives rise
to the following definition:
\begin{definition}[\protect{\cite[Definition 3.3]{GoodearlYakimov2017QCA}}]\label{def:cgl_extension}
	An iterated Ore extension
	\begin{equation*}
		R = \bbK[x_1][x_2; \sigma_2, \delta_2]\cdots [x_N; \sigma_N, \delta_N]
	\end{equation*}
	\index{sigma k@$\sigma_k$}\index{delta k@$\delta_k$}%
	%
	is called a \emph{CGL\footnote{CGL extensions are named after G. Cauchon, K. Goodearl
			and E. Letzter.} extension}\index{CGL extension} if it is equipped with a rational
	action of a $\bbK$-torus $\mcH$ by $\bbK$-algebra automorphisms such that
	\begin{enumerate}[(i)]
		\item\label{itm:x_i-eigenvectors} The elements $x_1, \dots, x_N$ are $\mcH$-eigenvectors.
		\item\label{itm:sigma_k-is-h_k} For every $k \in [1, N]$, there exists $h_k \in \mcH$\index{h k@$h_k$} such that $\sigma_k$ is given by the action of $h_k$ on $R_{k-1}$ and the $h_k$-eigenvalue of $x_k$, is not a root of unity.
		\item For every $k\in [2, N]$, $\delta_k$ is \emph{locally
			      nilpotent}\index{nilpotent!locally}, i.e., for all $r \in R_{k-1}$, there exists some
		      $n \in \bbZ_{>0}$ such that $\delta_k^n (r) = 0$. Here, $R_{k-1}$ denotes the
		      intermediate algebra consisting of only the first $k-1$ extensions:
		      \begin{equation*}
			      R_{k-1} \defeq \bbK[x_1][x_2; \sigma_2, \delta_2]\cdots[x_{k-1};\sigma_{k-1}, \delta_{k-1}].
		      \end{equation*}
	\end{enumerate}
\end{definition}

We will call $N$ the \emph{length}\index{CGL extension!length of} of the CGL extension.
As mentioned in the definition, we denote by $R_k$\index{R k@$R_k$} the intermediate
subalgebra generated by the first $k$ variables. For $j, k \in [1, N]$ we will also use
the notation $R_{[j, k]}$\index{R j k@$R_{[j,k]}$} to denote the unital subalgebra
generated by $\{x_i \mid j \leq i \leq k\}$ where $R_{[j, k]} \defeq \bbK$ if $j \nleq
	k$.

We will write $\lambda_k$ for the $h_k$-eigenvalue of $x_k$, i.e., $h_k \cdot x_k =
	\lambda_k x_k$\index{lambda k@$\lambda_k$}. For $1 \leq j < k \leq N$, we have
$\sigma_k (x_j) = h_k \cdot x_j = \lambda_{kj} x_j$ for some $\lambda_{kj} \in
	\bbK^\times$ using conditions \labelcref{itm:x_i-eigenvectors,itm:sigma_k-is-h_k}. We
can complete this to a multiplicatively skew-symmetric matrix
\begin{equation}\label{eq:CGL_lambda}
	\boldsymbol{\lambda} \defeq (\lambda_{kj}) \in M_N(\bbK^\times)
\end{equation}
%
\index{lambda@$\bbl$} by setting $\lambda_{kk} \defeq 1$ and $\lambda_{jk} \defeq \lambda_{kj}\inv$ for $1 \leq j < k
	\leq N$.

\begin{lemma}\label{lem:h_after_delta}
	With the notations as in \cref{def:cgl_extension},
	\begin{equation*}
		(h\cdot )\delta_k = \chi_{x_k}(h)\delta_k(h\cdot),
	\end{equation*}
	for all $h \in \mcH$ and $k \in [2, N]$.
\end{lemma}
\begin{proof}
	Fix $k \in [2, N]$ and $h \in \mcH$. Note that any monomial $a = x_1^{m_1}\cdots x_{k-1}^{m_{k-1}} \in R_{k-1}$ is an $h$-eigenvector, and also a $\sigma_k$-eigenvector. In particular, $\chi_a = \chi_{\sigma_k(a)}$. Hence,
	\begin{align*}
		h \cdot(x_k a)  & = \chi_{x_k}(h)\chi_{a}(h)x_ka                                      \\
		                & = \chi_{x_k}(h)\chi_{a}(h)(\sigma_k (a)x_k +  \delta_k(a))          \\
		                & = h \cdot (\sigma_k (a) x_k) + \chi_{x_k}(h)\delta_k(\chi_{a}(h)a), \\
		\shortintertext{but also}
		h \cdot (x_k a) & = h \cdot (\sigma_k (a) x_k + \delta_k(a))                          \\
		                & = h \cdot (\sigma_k (a) x_k) + h\cdot \delta_k(a),
	\end{align*}
	which shows $h \cdot \delta_k (a) = \chi_{x_k}(h) \delta_k (h \cdot a)$. The result then follows from linearity of $(h \cdot)$ and $\delta_k$.
\end{proof}

The following theorem shows that the center of a CGL extension is not too big. It
crucially relies on the root of unity conditions to ensure that the $\mcH$-action is
nontrivial, and the generators commute in nontrivial ways.

\begin{theorem}[\protect{\parencite[Theorem II.6.4]{GoodearlBrown2002LecturesAQC}}]\label{thm:H_rationality} Let $R$
	be a CGL extension as in \cref{def:cgl_extension}, and let\footnote{In
		\cref{sec:ore_localizations}, we will see that every CGL extension is an Ore domain,
		thus it makes sense to consider $\Fract(R)$.} $Z(\Fract(R))$ be the center of
	$\Fract(R)$. Then
	\begin{equation*}
		Z(\Fract(R))^\mcH = \bbK,
	\end{equation*}
	where $Z(\Fract(R))^\mcH$ is the subalgebra fixed by $\mcH$.
\end{theorem}

Before proceeding, let us look at some examples of CGL extensions.

\begin{example}
	Let $A_1^q(\bbK)$\index{A q@$A_1^q (\bbK)$} be the $\bbK$-algebra generated by $x_1, x_2$ such that $x_2 x_1 - q x_1 x_2 = 1$. This algebra is known as the \emph{quantized Weyl algebra}\index{algebra!quantized Weyl}. It is an iterated Ore extension, with presentation
	\begin{equation*}
		A_1^q \defeq \bbK[x_1][x_2; \sigma, \delta],
	\end{equation*}
	%
	where $\sigma$ and $\delta$ are defined by $\sigma(x_1) = q x_1$ and $\delta(x_1) = 1$.
	After all,
	\begin{equation*}
		x_2 x_1 = \sigma(x_1) x_2 + \delta(x_1) = q x_1 x_2 + 1.
	\end{equation*}
	%
	If $q$ is not a root of unity, it becomes a CGL extension when we consider the action
	of $\mcH = \bbK^\times$ on $A_1^q$ given by $\xi \cdot x_1 = \xi x_1$ and $\xi \cdot
		x_2 = \xi\inv x_2$. Indeed, by construction of the action, the elements $x_1, x_2$ are
	$\mcH$-eigenvectors. Furthermore, since
	\begin{equation*}
		\delta(x_1^n) = \sigma(x_1)\delta(x_1^{n-1}) + \delta(x_1)x_1^{n-1} = q x_1 \delta(x_1^{n-1}) + x_1^{n-1}
	\end{equation*}
	%
	and $\delta(1) = 0$ we find (by induction) that $\delta^{n+1}(x_1^n) = 0$, which shows
	that it is locally nilpotent. In fact, a similar reasoning shows that it suffices to
	check local nilpotency on the generators for any Ore extension. Finally, it suffices to
	pick $h_2 = q$, since $q \cdot x_1 = qx_1 = \sigma(x_1)$ and $q \cdot x_2 = q^{-1}x_2$,
	and $q^{-1}$ is not a root of unity.
\end{example}

The following algebra will be studied extensively in what follows.
\begin{example}\label{exmp:heisenberg}
	Let $\Heis(\mcU_q(\mfn_2))$\index{Heis@$\HeisUqn$} be the $\bbK$-algebra generated by $E_1, E_2, F_1, F_2$ satisfying the quantum Serre relations:
	\begin{align*}
		E_1 E_2^2 - (q + q^{-1}) E_2 E_1 E_2 + E_2^2 E_1 & = 0,\quad &  & E_2 E_1^2 - (q + q^{-1}) E_1 E_2 E_1 + E_1^2 E_2 = 0, \\
		F_1 F_2^2 - (q + q^{-1}) F_2 F_1 F_2 + F_2^2 F_1 & = 0,\quad &  & F_2 F_1^2 - (q + q^{-1}) F_1 F_2 F_1 + F_1^2 F_2 = 0,
	\end{align*}
	and
	\begin{align*}
		F_1 E_1 - q^2 E_1 F_1 & = 1, \quad & F_2 E_1 = q^{-1}E_1 F_2, \\
		F_2 E_2 - q^2 E_2 F_2 & = 1, \quad & F_1 E_2 = q^{-1}E_2 F_1,
	\end{align*}
	%
	for $q \in \bbK^\times$ not a root of unity. This algebra is the Heisenberg algebra
	associated to the quantized enveloping algebra $\mcU_q(\mathfrak{n}_2)$. We will only
	need this explicit description of the algebra in terms of generators and relations. In
	order to view $\HeisUqn$ as a CGL extension, the quantum Serre relations pose a
	problem, as they are quadratic. To solve this, we introduce two new elements:
	\begin{align*}
		E_{12} & \defeq E_2 E_1 - q^{-1}E_1 E_2, \\
		\shortintertext{and}
		F_{12} & \defeq F_2 F_1 - qF_1 F_2.
	\end{align*}
	The quantum Serre relations then immediately give
	\begin{align*}
		E_{12}E_1 & = q E_1 E_{12}, \quad E_{12}E_2 = q\inv E_2 E_{12}, \quad F_{12}F_1 = q\inv F_1 F_{12}, \quad F_{12}F_2 = q F_2 F_{12}.
	\end{align*}
	%
	To view $\Heis(\mcU_q(\mfn_2))$ as an iterated Ore extension, we will use a
	presentation of the form
	\begin{equation}\label{eq:cgl_heisenberg}
		\Heis(\mcU_q(\mfn_2)) = \bbK[E_2][E_{12}; \sigma_2, \delta_2][E_1;\sigma_3, \delta_3][F_1; \sigma_4, \delta_4][F_{12}; \sigma_5, \delta_5][F_2; \sigma_6, \delta_6].
	\end{equation}
	%
	To determine the $\sigma_i$ and $\delta_i$ functions, some simple but tedious
	calculations show that the following relations are also satisfied in $A$:
	\begin{align*}
		F_1 E_{12}   & = q E_{12} F_1,                                        &  & F_{12}E_2 = q E_2 F_{12} + (q\inv - q) F_1, \\
		F_2 E_{12}   & = q E_{12}F_2 + (1 -q^{-2})E_1,                        &  & F_{12}E_1 = q E_1 F_{12},                   \\
		F_{12}E_{12} & = q^2 E_{12} F_{12} + (q\inv - q) (F_1 E_1 - E_1 F_1).
	\end{align*}
	%
	From this we obtain \cref{table:sigma_delta_heisenberg}.
	\begin{table}
		\begin{center}

			\begin{tabular}{c|lllll}
				           & $E_2$       & $E_{12}$       & $E_{1}$     & $F_1$       & $F_{12}$       \\
				\hline
				$\sigma_2$ & $q\inv E_2$                                                               \\
				$\sigma_3$ & $q E_2$     & $q\inv E_{12}$                                              \\
				$\sigma_4$ & $q\inv E_2$ & $q E_{12}$     & $q^2 E_1$                                  \\
				$\sigma_5$ & $q E_2$     & $q^2 E_{12}$   & $q E_1$     & $q\inv F_1$                  \\
				$\sigma_6$ & $q^2 E_2$   & $q E_{12}$     & $q\inv E_1$ & $q F_1$     & $q\inv F_{12}$
			\end{tabular}

			\begin{tabular}{c|lllll}
				           & $E_2$           & $E_{12}$                        & $E_{1}$ & $F_1$    & $F_{12}$ \\
				\hline
				$\delta_2$ & $0$                                                                               \\
				$\delta_3$ & $-q E_{12}$     & $0$                                                             \\
				$\delta_4$ & $0$             & $0$                             & $1$                           \\
				$\delta_5$ & $(q\inv -q)F_1$ & $(q\inv -q)(F_1 E_1 - E_1 F_1)$ & $0$     & $0$                 \\
				$\delta_6$ & $1$             & $(1- q^{-2})E_1$                & $0$     & $F_{12}$ & $0$
			\end{tabular}

		\end{center}

		\caption{The values of the functions $\sigma_i$ and $\delta_i$ in the CGL extension presentation \cref{eq:cgl_heisenberg} for the algebra of \cref{exmp:heisenberg}. }
		\label{table:sigma_delta_heisenberg}
	\end{table}

	We now show that $\Heis(\mcU_q(\mfn_2))$ is also a CGL extension. The local nilpotency
	of the $\delta_i$ can be seen in the table. Now, consider the action of $\mcH =
		(\bbK^\times)^3$ given by
	\begin{align*}
		\xi \cdot E_1 & = \xi_1\xi_2\inv E_1, \quad &  & \xi \cdot E_2 = \xi_2\xi_3^{-1} E_2, \quad &  & \xi E_{12} = \xi_1 \xi_3\inv E_{12}, \\
		\xi \cdot F_1 & = \xi_1\inv\xi_2F_1, \quad  &  & \xi \cdot F_2 = \xi_2\inv\xi_3 F_2, \quad  &  & \xi F_{12} = \xi_1\inv \xi_3 F_{12},
	\end{align*}
	%
	for $\xi = (\xi_1, \xi_2, \xi_3) \in (\bbK^\times)^3$. Using
	\cref{table:sigma_delta_heisenberg}, it is easily verified that the elements
	\begin{align*}
		h_1 & = (1, q\inv, q), \quad h_4 = (q, q\inv, 1), \\
		h_2 & = (q\inv,1, q), \quad h_5 = (q,1, q\inv),   \\
		h_3 & = (q\inv, q, 1), \quad h_6 = (1, q, q\inv),
	\end{align*}
	%
	satisfy the conditions for \cref{def:cgl_extension} \labelcref*{itm:sigma_k-is-h_k}. We
	thus have
	\begin{equation}\label{eq:heisenberg_lambda_k}
		\lambda_1 = \lambda_2 = \cdots = \lambda_6 = q^{-2}.
	\end{equation}
\end{example}

The final example is closely related to the quantum Grassmannians that we already
studied.
\begin{example}\label{exmp:quantum_matrices}
	For $q \in \bbK^\times$ not a root of unity and $m, n \in \bbZ_{> 0}$, we can consider the \emph{quantized matrix coordinate algebra}\index{algebra!quantized matrix coordinate}, $\mcO_q(M_{n \times m}(\bbK))$\index{O q M n@$\mcO_q(M_{n \times m}(\bbK))$} that we saw in \cref{sec:quantum_grassmannian}. We will not study the quantum cluster algebra structure on it in detail here, and refer the interested reader to \cite{GoodearlYakimov2017QCA} where it is taken as the central example.

	Let us restrict to the case where $m = n = 2$. In this case $R = \mcO_q(M_2(\bbK))$ is
	the $\bbK$-algebra generated by $a,b,c$ and $d$ subject to the relations
	\begin{equation*}
		ab =qba, \quad cd = qdc, \quad bc = cb, \quad ac = qca, \quad bd = qdb, \quad ad - da = (q-q\inv)bc.
	\end{equation*}
	%
	The relations become a lot easier to remember when we arrange the generators as a $2
		\times 2$ matrix:
	\begin{equation*}
		\begin{pmatrix}
			a & b \\
			c & d
		\end{pmatrix}.
	\end{equation*}
	The relations can then be summarized as follows:
	\begin{itemize}
		\item Elements on the same row $q$-commute, e.g., $ab = qba$.
		\item Elements on the same column $q$-commute, e.g., $ac = qca$.
		\item The elements on the off-diagonal commute, e.g., $bc = cb$.
		\item Finally, the two ways to compute the \emph{quantum determinant}\index{quantum
			      determinant}\index{quantum!determinant} are equal:
		      \begin{equation*}
			      ad - qbc = da -q\inv cb.
		      \end{equation*}
	\end{itemize}
	%
	It can be shown by a straightforward calculation that this quantum determinant is a
	central element, i.e., it commutes with every element of $R$. This will also follow
	indirectly from later theory (cf. \cref{exmp:quantum_matrices_hom_primes}).

	We now claim that $R$ can be written as an iterated Ore extension of the form
	\begin{equation*}
		R = \bbK[a][b; \sigma_2, \delta_2][c; \sigma_3, \delta_3][d; \sigma_4, \delta_4].
	\end{equation*}
	%
	Indeed, from $ab = qba$ we obtain $\sigma_2(a) = q\inv$ and $\delta_2(a) = 0$. Then,
	because $cb = bc$ we obtain $\sigma_3(b) = b$ and $\delta_3(b) = 0$, while $ac = qac$
	gives $\sigma_3(a) = q\inv(a)$ and $\delta_3(a) = 0$. Similarly, we find $\sigma_4(b) =
		q\inv b, \sigma_4(c) = q\inv c$ and $\delta_4(b) = \delta_4(c) = 0$. Finally, because
	$da = ad - (q - q\inv)bc$ we find $\sigma_4(a) = a$ and $\delta_4(a) = (q\inv - q)bc$.

	In order for $R$ to be a CGL extension, we need a rational action by a $\bbK$-torus.
	For this, one can take $\mcH \defeq (\bbK^\times)^4$ with action
	\begin{equation*}
		\xi \cdot \begin{pmatrix}
			a & b \\
			c & d
		\end{pmatrix}
		\defeq \begin{pmatrix}
			\xi_1 & 0     \\
			0     & \xi_2
		\end{pmatrix}
		\begin{pmatrix}
			a & b \\
			c & d
		\end{pmatrix}
		\begin{pmatrix}
			\xi_3\inv & 0         \\
			0         & \xi_4\inv
		\end{pmatrix}
		= \begin{pmatrix}
			\xi_1\xi_3\inv a & \xi_1\xi_4\inv b \\
			\xi_2\xi_3\inv c & \xi_2\xi_4\inv d
		\end{pmatrix}.
	\end{equation*}
	%
	That $\delta_2, \delta_3$ and $\delta_4$ are locally nilpotent follows from $\delta_2 =
		\delta_3 = 0$ and $\delta_4(b) = \delta_4(c) = 0$ so that $\delta_4^2(a) = (q\inv -
		q)\delta_4(bc) = 0$. For the elements $h_1, \dots, h_4$ one can take
	\begin{align*}
		 & h_1 = (q\inv, 1, q, 1),\quad h_2 = (q\inv, 1,1,q) \\
		 & h_3 = (1,q\inv,1,q),\quad h_4 =(1,q\inv, 1, q),
	\end{align*}
	and hence
	\begin{align*}
		\lambda_1 = \lambda_2 = \lambda_3 = \lambda_4 = q^{-2}.
	\end{align*}
\end{example}

\subsection{Homogeneous prime elements}

At this moment, it does not seem obvious at all that CGL extensions would admit the
structure of a quantum cluster algebra. The key observation comes from studying the
homogeneous prime elements of a CGL extension. It turns out that these will always
quasi-commute. This was first shown in \cite{GoodearlYakimov2016QuantumOre}. From this
one obtains a quantum torus, which is the starting point for creating a quantum cluster
algebra.

\medskip

A \emph{prime element}\index{element!prime} of a not necessarily commutative domain $R$
is a nonzero element $p \in R$ such that $p$ is \emph{normal}\index{element!normal},
that is, $Rp = pR$ and such that the quotient $R / Rp$ is a domain. To illustrate that
this definition corresponds to our intuition of what a prime element should be, we
prove the following small lemma.
\begin{lemma}\label{lem:prime_divides_product}
	%
	Let $p$ be a prime element in a ring $R$. If $p$ divides a product $ab$, i.e., $ab \in
		Rp = pR$, for some $a,b \in R$ then either $p$ divides $a$ or $p$ divides $b$.
	Conversely, any normal element with that property is prime.
\end{lemma}
\begin{proof}
	%
	Let $p$ be a normal element of $R$ and take $a,b \in R$. Write $\pi \colon R \to R /
		Rp$ for the quotient map. Then, for all $x \in R$, $x \in Rp$ if and only if $\pi(x) =
		0$. If $p$ is prime, and $\pi(ab) = \pi(a)\pi(b) = 0$, then either $\pi(a) = 0$ or
	$\pi(b) = 0$ as $R/Rp$ is a domain. Hence, $a \in Rp$ or $b \in Rp$. Conversely, if
	$\pi(a)\pi(b) = 0$ in $R/Rp$, then we have $ab \in Rp$ from which we obtain $a \in Rp$
	or $b \in Rp$ by assumption. Thus, $\pi(a) = 0$ or $\pi(b) = 0$ which shows that $R/
		Rp$ is a domain.
\end{proof}
%
We now state a theorem that is quite technical, but forms the heart of the main
theorem. Let us first fix some notation. For a function $\eta \colon [1, N] \to \bbZ$,
we can define a predecessor and successor
function\index{function!predecessor}\index{function!successor}:
\begin{align*}
	p \colon [1, N] \to [1, N] \sqcup \{-\infty\} & \colon k \mapsto  \max\{j < k \mid \eta(j) = \eta(k)\}  \\
	s \colon [1, N] \to [1, N] \sqcup \{+\infty\} & \colon k \mapsto  \min\{j > k \mid \eta(j) = \eta(k)\},
\end{align*}
%
where we take $\max \emptyset = - \infty$ and $\min \emptyset = + \infty$ (cf.
\cref{fig:predecessor_successor}).

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\draw[help lines, xstep =0] (0,0) grid (8,3);
		\draw plot[mark=*] coordinates {(1,1) (2,2) (3,1) (4,0) (5,1) (6,3) (7,2)};
		\node (neginf) at (-0.5,1) {$-\infty$};
		\node (a) at (1,1) {};
		\node (b) at (3,1) {};
		\node (c) at (5,1) {};
		\node (posinf) at (8.5, 1) {$+\infty$};
		\draw[Stealth-, red] (neginf) to [bend right = 20] (a);
		\draw[Stealth-Stealth, red] (a) to [bend right = 20] (b);
		\draw[Stealth-Stealth, red] (b) to [bend right = 20] (c);
		\draw[-Stealth, red] (c) to [bend right = 15] (posinf);
	\end{tikzpicture}
	\caption{The predecessor and successor functions move along the level sets (the horizontal lines) to the previous or the next point respectively.}
	\label{fig:predecessor_successor}
\end{figure}

\begin{theorem}[\protect{\cite[Theorem 3.6]{GoodearlYakimov2017QCA}}]\label{thm:homogeneous_primes}
	Let $R$ be a CGL extension of length $N$. There exists a function $\eta \colon [1, N] \to \bbZ$\index{eta@$\eta$} and nonzero elements
	\begin{equation*}
		c_k \in R_{k-1} \text{ for all } k \in [2,N] \text{ with } p(k) \neq - \infty
	\end{equation*}
	such that the elements $y_1, \dots, y_N \in R$, recursively defined by
	\begin{equation}\label{eq:y_k_recursive}
		y_k = \begin{cases}
			y_{p(k)}x_k - c_k & \text{ if } p(k) \neq -\infty \\
			x_k               & \text{ if } p(k) = -\infty,
		\end{cases}
	\end{equation}
	%
	\index{y k@$y_k$}
	are homogeneous and have the property that for every $k \in [1, N]$,
	\begin{equation}\label{eq:list_of_ys_in_R_k}
		\{y_j \mid j \in [1, k], s(j) > k\}
	\end{equation}
	%
	is a list of the homogeneous prime elements of $R_k$, up to scalar multiples. The
	elements $y_1, \dots, y_N \in R$ with the properties
	\cref{eq:y_k_recursive,eq:list_of_ys_in_R_k} are unique, and the function $p$ has the
	property that $p(k) = - \infty$ if and only if $\delta_k = 0$. The function $\eta$ is
	not uniquely defined, but its level sets are.
\end{theorem}

\begin{convention}

	In what follows, there will be plenty of formulas in which the predecessor and
	successor function of \cref{thm:homogeneous_primes} appear. It will be convenient to
	assume that $a_{\pm \infty}$ will be the neutral element in the context that it
	appears. For example, in the context of \cref{thm:homogeneous_primes} we would have
	$y_{p(k)} = 1$ when $p(k) = -\infty$. When $a \in \bbK^\times$, we will always mean
	$a_{\pm\infty} = 1$. When $a \in \bbZ^N$, we will always mean $a_{\pm\infty} = 0$.
\end{convention}

To compute the elements $y_1, \dots, y_N$, some additional facts come in handy. For
this, we introduce some further notation and relations related to CGL extensions. In
what follows, $R$ is a CGL extension and the elements $y_k, k \in [1, N]$ and the
functions $p$ and $s$ are as in \cref{thm:homogeneous_primes}.

Let $O_{\pm} \colon [1, N] \to \bbZ_{\geq 0}$\index{O pm k@$O_{\pm}(k)$} be the order
functions\index{function!order} given by
\begin{align*}
	O_{+}(k) & \defeq \max\{m \in \bbZ_{\geq 0} \mid s^m(k) \neq + \infty\}   \\
	O_{-}(k) & \defeq \max\{m \in \bbZ_{\geq 0} \mid p^m(k) \neq - \infty\} ,
\end{align*}
%
where we take $p^0 = s^0 \defeq \id$. Define
\begin{equation*}
	\overline{e}_k \defeq \sum_{m=0}^{O_{-}(k)} e_{p^m(k)} \in \bbZ^N,
\end{equation*}
\index{e k@$\oe_k$}%%
%
for $k \in [1, N]$. Then, for $j,k \in [1, N]$, set
\begin{equation*}
	\alpha_{kj} \defeq \Omega_{\bbl}(e_k, \overline{e}_j) = \prod_{m=0}^{O_{-}(j)}\lambda_{k, p^m(j)} \in \bbK^\times
\end{equation*}
\index{alpha kj@$\alpha_{kj}$}%%
and
\begin{equation}\label{eq:q_from_lambda}
	q_{kj} \defeq \Omega_{\bbl}(\overline{e}_k, \overline{e}_j) = \prod_{m=0}^{O_{-}(k)}\prod_{l=0}^{O_{-}(j)}\lambda_{p^m(k),p^l(j)} = \prod_{m=0}^{O_{-}(k)}\alpha_{p^m (k),j} \in \bbK^\times,
\end{equation}
\index{q kj@$q_{kj}$}%%
%
where $\bbl$ is as defined in \cref{eq:CGL_lambda}. Write $\bbq \defeq (q_{kj}) \in
	M_N(\bbK^\times)$\index{q@$\bbq$}.
\begin{proposition}[\protect{\cite[Proposition 3.11]{GoodearlYakimov2017QCA}}]\label{prop:y_quantum_torus}
	The $y_k$ quasi-commute:
	\begin{equation}\label{eq:y_quasi_commute}
		y_k y_j = q_{kj}y_jy_k, \quad \forall j, k \in [1, N].
	\end{equation}
	%
	The quantum torus $\mcT_{\bmq}$ embeds in $\Fract(R)$ via the $\bbK$-algebra
	homomorphism $\varphi \colon \mcT_{\bmq} \injto \Fract(R)$ given by $\varphi(Y_i) =
		y_i,\,\forall i \in [1, N]$, and this embedding gives rise to inclusions
	\begin{equation*}
		\varphi(\mcA_{\bmq}) \subseteq R \subset \varphi(\mcT_{\bmq}) \subset \Fract(R).
	\end{equation*}
\end{proposition}

Additionally, we have the following equations \cite[eq. (3.24) to
	(3.26)]{GoodearlYakimov2017QCA}.
\begin{align}\label{eq:y_x_quasi_commute}
	y_j x_k            & = \alpha_{kj}\inv x_k y_j, \text{ for all } j, k \in [1, N] \text{ such that } s(j) > k                                             \\
	\sigma_k (y_j)     & = \alpha_{kj}y_j, \text{ for } 1 \leq j \leq k \leq N \label{eq:sigma_of_y}                                                         \\
	\delta_k(y_{p(k)}) & = \alpha_{k, p(k)}(\lambda_k - 1)c_k, \text{ for all } k \in [2, N] \text{ such that } p(k) \neq - \infty \label{eq:delta_of_y_pk}.
\end{align}
%
From this we can deduce a small lemma that is useful for finding the sequence of
homogeneous prime elements $y_1, \dots, y_N$ of \cref{thm:homogeneous_primes}.
\begin{lemma}\label{lem:delta_nonzero_iff_predecessor}
	For all $1 \leq j < k \leq N$ such that $p(k) \neq -\infty$ and $s(j) \geq k$, we have $\delta_k(y_j) \neq 0$ if and only $s(j) = k$.
\end{lemma}
\begin{proof}
	First, suppose that $s(j) = k$. Then $p(k) = j$, and \cref{eq:delta_of_y_pk} gives that $\delta_k(y_j)$ is a scalar multiple of $c_k$, which is nonzero. Indeed, $c_k \neq 0$ because $p(k) \neq -\infty$ and $\lambda_k \neq 1$ because it is not a root of unity. Now, suppose that $s(j) > k$. Then \cref{eq:y_x_quasi_commute,eq:sigma_of_y} give that
	\begin{equation*}
		\alpha_{kj}y_jx_k = x_k y_j = \sigma_k(y_j) x_k + \delta_k(y_j) = \alpha_{kj}y_j x_k + \delta_k(y_j),
	\end{equation*}
	so that we must have $\delta_k(y_j) = 0$.
\end{proof}

\begin{example}\label{exmp:heisenberg_primes}

	The goal is to find the sequence $y_1, y_2, \dots, y_6$ of homogeneous prime elements
	from \cref{thm:homogeneous_primes} for $R = \HeisUqn$\index{Heis@$\HeisUqn$}. To do
	this, we make use of \cref{lem:delta_nonzero_iff_predecessor}.

	Since $\delta_1 = 0$ and $\delta_2 = 0$ we must have $y_1 = x_1 = E_2$ and $y_2 = x_2 =
		E_{12}$. Let $\eta \colon [1, 6] \to \bbZ$ denote the function from
	\cref{thm:homogeneous_primes}, and $p,s$ the corresponding predecessor and successor
	functions. Since $p(1) = p(2) = -\infty$, we must have $\eta(1) \neq \eta(2)$. Let us
	take $\eta(1) = 1$ and $\eta(2) = 2$.

	Because $\delta_3 \neq 0$, we know that $y_3$ is of the form $y_j x_3 - c_3 = y_j E_1 -
		c_3$ for some $j \in [1,2]$ and $c_3 \in R_{2}$. Since
	\begin{align*}
		\delta_3(y_2) = \delta_3(E_{12}) = 0,
	\end{align*}
	%
	we find, using \cref{lem:delta_nonzero_iff_predecessor}, that $p(3) \neq 1$. Thus, we
	must have $\eta(3) = 1$ and $j = p(3) = 1$. In this case,
	\begin{equation*}
		\delta_3(y_{p(3)}) = \delta_3(y_1) = \delta_3(E_2) = q E_{12}.
	\end{equation*}
	%
	Thus, from \cref{eq:delta_of_y_pk,eq:heisenberg_lambda_k}, we obtain
	\begin{equation*}
		c_3 = \alpha_{3,1}\inv (\lambda_3-1)\inv \delta_3(E_2) = q\inv \frac{1}{q^{-2}-1}(-q E_{12}) = \frac{1}{1 - q^{-2}}E_{12},
	\end{equation*}
	and hence
	\begin{equation*}
		y_3 = E_2 E_1 - \frac{1}{1-q^{-2}}E_{12} = \frac{1}{1-q^2}(E_2 E_1 - q E_1 E_2).
	\end{equation*}

	Again, since $\delta_4 \neq 0$, we know that $y_4 = y_j F_1 -c_4$ for some $j \in [1,
			3]$ and $c_4 \in R_3$. Furthermore, we know that $j = p(4)$. So, since $\eta(1) =
		\eta(3)$, we must have $j = 2$ or $j = 3$. The case $j = 2$ can be ruled out because,
	$\delta_4(y_2) = \delta_4(E_{12}) = 0$. Thus, $\eta(4) = 1$ and $j = p(4) = 3$. We can
	now compute $c_4$ using \cref{eq:delta_of_y_pk}. We have, using
	\cref{table:sigma_delta_heisenberg},
	\begin{align*}
		\delta_4(y_{p(4)})
		 & = \delta_4(y_3)                                                                                                                \\
		 & = \delta_4\Bigl(\frac{1}{1-q^2}(E_2 E_1 - q E_1 E_2)\Bigr)                                                                     \\
		 & = \frac{1}{1-q^2}\Bigl(\sigma_4 (E_2)\delta_4(E_1) + \delta_4(E_2)E_1 - q(\sigma_4(E_1)\delta_4(E_2) + \delta_4(E_1)E_2)\Bigr) \\
		 & = \frac{1}{1-q^2}\Bigl(q\inv E_2  - qE_2\Bigr)                                                                                 \\
		 & = \frac{1}{1-q^2} q\inv (1- q^2) E_2                                                                                           \\
		 & = q\inv E_2.
	\end{align*}
	%
	Hence, from \cref{table:sigma_delta_heisenberg,eq:heisenberg_lambda_k}, we obtain
	\begin{align*}
		c_4 & = \alpha_{4,3}\inv (\lambda_4 - 1)\inv \delta_4(y_3)           \\
		    & = \lambda_{4,3}\inv\lambda_{4,1}\inv (q^{-2} -1)\inv q\inv E_2 \\
		    & = \frac{q^{-2}qq\inv}{q^{-2} - 1} E_2                          \\
		    & = \frac{1}{1 - q^2} E_2,
	\end{align*}
	and consequently
	\begin{equation*}
		y_4 = y_3 F_1 - \frac{1}{1-q^2}E_2.
	\end{equation*}

	For $y_5$ we must have either $p(5) = 2$ or $p(5) = 4$. Let us first assume that $p(5)
		= 4$. Then we would have
	\begin{align*}
		\delta_5(y_{p(5)})
		 & = \delta_5(y_4)                                                                                 \\
		 & = \delta_5\Bigl(y_3F_1 - \frac{1}{1-q^2}\delta_5(E_2)\Bigr)                                     \\
		 & = \delta_5(y_3)F_1 - \frac{1}{1-q^2}(q\inv -q) F_1                                              \\
		 & = \frac{1}{1-q^2}\Bigl(\delta_5(E_2)E_1 - q \sigma_5 (E_1) \delta_5(E_2) - (q\inv -q)\Bigr) F_1 \\
		 & = \frac{q\inv - q}{1-q^2}\bigl(F_1E_1 - q^2 E_1 F_1 - 1\bigr) F_1                               \\
		 & = 0,
	\end{align*}
	%
	and \cref{eq:delta_of_y_pk} gives $c_5 = 0$, a contradiction. So, $p(5) = 2$ and
	$\eta(5) = \eta(2)$. We find
	\begin{align*}
		\delta_5(y_{p(5)})
		 & = \delta_5(y_2)                                                          \\
		 & = \delta_5(E_{12})                                                       \\
		 & = (q\inv -q)(F_1E_1 - E_1F_1)                                            \\
		 & = (q\inv -q)(1 + (q^2 - 1)E_1 F_1),
		\intertext{and hence}
		c_5
		 & = \alpha_{5, 2}\inv (\lambda_5 - 1)\inv \delta_5(y_{p(5)})               \\
		 & = \lambda_{5, 2}\inv (q^{-2} - 1)\inv (q\inv - q)(1 + (q^2 - 1) E_1 F_1) \\
		 & = q^{-2} (q^{-2} - 1)\inv q (q^{-2} - 1)(1 + (q^2 - 1) E_1 F_1)          \\
		 & = q\inv + (q - q\inv) E_1 F_1.
	\end{align*}
	%
	We have thus shown that
	\begin{align*}
		y_5 = y_2 F_{12} + (q\inv - q) E_1 F_1 - q\inv.
	\end{align*}
	%
	Note that if we would have first calculated $\delta_5(y_2)$, then we could have avoided
	calculating $\delta_5(y_4)$, since we would already know that it is zero by
	\cref{lem:delta_nonzero_iff_predecessor}.

	We now move on to calculating the final homogeneous prime element, $y_6$. There are two
	possibilities, $p(6) = 4$ or $p(6) = 5$. We first determine $\delta_6(y_4)$:
	\begin{align*}
		\delta_6(y_4)
		 & = \delta_6\bigl(y_3F_1- \frac{1}{1-q^2}E_2\bigr)                                        \\
		 & = \delta_6\bigl(y_3F_1- \frac{1}{1-q^2}E_2\bigr)                                        \\
		 & = \sigma_6(y_3)F_{12} + \frac{1}{1-q^2}\delta_6(E_2E_1 - q E_1 E_2)F_1- \frac{1}{1-q^2} \\
		 & = qy_3F_{12} + \frac{1}{1-q^2}(E_1 - E_1)F_1- \frac{1}{1-q^2}                           \\
		 & = qy_3F_{12} - \frac{1}{1-q^2}.
	\end{align*}
	%
	Since it is nonzero, we conclude using \cref{lem:delta_nonzero_iff_predecessor} that
	$p(6) = 4$ and $\delta_6(y_5) = 0$. Hence,
	\begin{align*}
		c_6
		 & = \alpha_{6, 4}\inv (q^{-2} - 1)\inv \delta_6(y_4)                                                             \\
		 & = (\lambda_{6,4}\lambda_{6,3}\lambda_{6,1})\inv \frac{1}{q^{-2} - 1}\Bigl(q y_3 F_{12} - \frac{1}{1-q^2}\Bigr) \\
		 & = \frac{1}{1 -q^{2}}\Bigl(q y_3 F_{12} - \frac{1}{1-q^2}\Bigr),
	\end{align*}
	and
	\begin{equation*}
		y_6 = y_4 F_2 - \frac{1}{1-q^2}\Bigl(q y_3 F_{12} + \frac{1}{1-q^2}\Bigr).
	\end{equation*}

	We now briefly summarize all the findings. The $\eta$-function of
	\cref{thm:homogeneous_primes} for the algebra $\HeisUqn$ can be taken to be $\eta
		\colon [1, 6] \to \bbZ$ with $\eta(1)=\eta(3)=\eta(4)=\eta(6) = 1$ and $\eta(2) =
		\eta(5) = 2$. The sequence of homogeneous prime elements is given by
	\begin{equation}\label{eq:heisenberg_hom_primes}
		\begin{aligned}
			y_1 & = E_2                                                                      \\
			y_2 & = E_{12}                                                                   \\
			y_3 & = y_1 E_1 - \frac{1}{1- q^{-2}}E_{12}                                      \\
			y_4 & = y_3 F_1 - \frac{1}{1-q^2} E_2                                            \\
			y_5 & = y_2 F_{12} - (q - q\inv) E_1 F_1 - q \inv                                \\
			y_6 & = y_4 F_2 - \frac{1}{1-q^2} \Bigl(q y_3 F_{12} - \frac{1}{1 - q^2} \Bigr).
		\end{aligned}
	\end{equation}
	%
	To visualize $\eta$ as well as the predecessor and successor functions, we can think of
	them arranged as follows.
	\begin{equation*}
		\begin{tikzcd}[sep=tiny]
			& y_2 & & & y_5 \\
			y_1 & & y_3 & y_4 & & y_6
		\end{tikzcd}
	\end{equation*}

\end{example}

\begin{example}\label{exmp:quantum_matrices_hom_primes}
	We now work out the sequence of homogeneous primes of \cref{thm:homogeneous_primes} for the algebra $R = \mcO_q(M_2(\bbK))$ of \cref{exmp:quantum_matrices}. This will be significantly easier.

	First note that $\delta_2 = \delta_3 = 0$ so that $y_1 = a, y_2 = b$ and $y_3 = c$. For
	$y_4$ we know that $\delta_4(y_1) = \delta_4(a) = (q\inv -q)bc \neq 0$, so that we must
	have
	\begin{equation*}
		c_4 = \alpha_{41}\inv(\lambda_4 -1)\inv \delta_4(y_4) = (q^{-2} - 1)\inv(q\inv - q)bc = q bc,
	\end{equation*}
	and
	\begin{equation*}
		y_4 = y_1 d - c_4 = a d - q bc.
	\end{equation*}
	%
	Thus, $y_4$ is precisely the quantum determinant. Since we already knew that the
	quantum determinant is central, this was to be expected. Conversely, one could prove
	that it is central this way. Indeed, $q_{41} = \lambda_{41}\lambda_{11} = 1, \, q_{42}
		= \lambda_{42}\lambda_{12} = q\inv q = 1$ and $q_{43} = \lambda_{43}\lambda_{13} =
		q\inv q = 1$ so that \cref{prop:y_quantum_torus} gives that $y_4$ commutes with
	$y_1,y_2$ and $y_3$ which are precisely the other generators $a,b$ and $c$. That it
	commutes with $d$ follows from \cref{eq:y_x_quasi_commute} and the calculation
	$\alpha_{44} = \lambda_{44}\lambda_{14} = 1$.

	In the more general case of the algebra $\mcO_q(M_{n \times m}(\bbK))$, the homogeneous
	prime elements are given by certain types of quantum minors. Again, the reader is
	referred to \cite{GoodearlYakimov2017QCA} for more details.
\end{example}

\subsection{Almost mutations}

We have seen how one obtains a quantum torus from a CGL extension: by considering the
sequence $y_1, \dots, y_N$ of homogeneous prime elements from
\cref{thm:homogeneous_primes}. To obtain a quantum cluster algebra structure, we should
be able to find other elements in $R$ that are obtained by some mutation-like rule from
the $y$-elements. By construction, the sequence $y_1, \dots, y_N$ from
\cref{thm:homogeneous_primes} depends heavily on the order in which the generators $x_1
	\dots, x_N$ are adjoined. Changing the order will yield different sequences of
homogeneous prime elements. It turns out that these sequences are related to each other
by mutations.

\medskip

We consider the most basic case, when we swap the order of two adjacent variables $x_k,
	x_{k+1}$. So, we have a CGL extension
\begin{equation}\label{eq:default_cgl_presentation}
	R = \bbK[x_1][x_2; \sigma_2, \delta_2]\cdots[x_k; \sigma_k, \delta_k][x_{k+1};\sigma_{k+1}, \delta_{k+1}]\cdots[x_N; \sigma_N, \delta_N],
\end{equation}
%
such that we can also write $R$ as a CGL extension of the form
\begin{multline}\label{eq:swapped_cgl_presentation}
	R = \bbK[x_1][x_2; \sigma_2, \delta_2]\cdots[x_{k-1}; \sigma_{k-1}, \delta_{k-1}][x_{k+1}; \sigma_k', \delta_k'][x_k;\sigma_{k+1}', \delta_{k+1}']\\
	[x_{k+2}; \sigma_{k+2}, \delta_{k+2}]\cdots[x_N; \sigma_N, \delta_N].
\end{multline}
%
Such a pair of CGL extension presentations will be referred to as
\emph{adjacent}\index{adjacent presentations}. We will denote the chain of algebras as
\begin{equation*}
	\bbK = R'_0 \subset R'_1  = \bbK[x_1] \subset R'_2 = \bbK[x_1][x_2; \sigma_2, \delta_2] \subset \cdots \subset R'_N = R
\end{equation*}
%
for the presentation \eqref{eq:swapped_cgl_presentation}. We first look at what
restrictions this places on the $\sigma_i, \sigma_i '$ and $\delta_i,\delta_i'$
appearing in the CGL presentations.
\begin{lemma}\label{lem:swapped_cgl_sigma_delta}
	Let $R$ be a CGL extension with adjacent presentations of the form \eqref{eq:default_cgl_presentation} and \eqref{eq:swapped_cgl_presentation}. Then
	\begin{equation}\label{eq:sigma_prime}
		\begin{aligned}
			\sigma_k ' & = \sigma_{k+1}|_{R_{k-1}}    \\
			\sigma_k   & = \sigma_{k+1}' |_{R_{k-1}},
		\end{aligned}
	\end{equation}
	and
	\begin{equation}\label{eq:delta_prime}
		\begin{aligned}
			\delta_k ' & = \delta_{k+1}|_{R_{k-1}}    \\
			\delta_k   & = \delta_{k+1}' |_{R_{k-1}}.
		\end{aligned}
	\end{equation}
	Furthermore, $\delta_{k+1}(x_k) \in R_{k-1}$ and
	\begin{equation}\label{eq:sigma_delta_prime_x_k_1}
		\begin{aligned}
			\sigma_{k+1}'(x_{k+1}) & = \lambda_{k, k+1} x_{k+1}             \\
			\delta_{k+1}'(x_{k+1}) & = -\lambda_{k, k+1} \delta_{k+1}(x_k).
		\end{aligned}
	\end{equation}
	%
\end{lemma}
\begin{proof}
	%
	From \cref{eq:default_cgl_presentation} we have that $x_{k+1}a = \sigma_{k+1}(a)x_{k+1}
		+ \delta_{k+1}(a)$ for $a \in R_{k-1}$. On the other hand, also $x_{k+1}a =
		\sigma_k'(a)x_{k+1} + \delta_k'(a)$ using \cref{eq:swapped_cgl_presentation}. So
	\begin{equation*}
		\sigma_{k+1}(a)x_{k+1} + \delta_{k+1}(a) = \sigma_k'(a) x_{k+1} + \delta_k'(a).
	\end{equation*}
	%
	Using that $\sigma_k'(a)\in R_{k-1}, \sigma_{k+1}(a) \in R_k$ and $\delta_k'(a) \in
		R_{k-1}, \delta_{k+1}(a) \in R_{k}$ together with the fact that $x_{k+1}$ and 1 are
	linearly independent over $R_k$ it follows that $\sigma_k'(a) = \sigma_{k+1}(a)$ and
	$\delta_k'(a) = \delta_{k+1}(a)$. Applying the same reasoning, but swapping the roles
	of \cref{eq:default_cgl_presentation,eq:swapped_cgl_presentation} we obtain
	$\sigma_k(a) = \sigma_{k+1}'(a)$ and $\delta_k(a) = \delta_{k+1}'(a)$, and we have
	shown \cref{eq:delta_prime,eq:sigma_prime}.

	Recalling \cref{eq:CGL_lambda}, note that $x_k x_{k+1} = \lambda'_{k+1,k}x_{k+1}x_{k} +
		\delta'_{k+1}(x_{k+1})$, and $\lambda'_{k,k+1} = (\lambda_{k+1, k}')\inv$. So,
	\begin{equation*}
		\lambda'_{k,k+1}x_k x_{k+1} - \lambda'_{k,k+1} \delta'_{k+1}(x_{k+1}) = x_{k+1} x_k = \lambda_{k+1, k} x_k x_{k+1} + \delta_{k+1}(x_k).
	\end{equation*}
	%
	Then, since $\delta'_{k+1}(x_{k+1}) \in R'_k $ and $\delta_{k+1}(x_k) \in R_k$ are
	linearly independent from $x_k x_{k+1}$ over $R_{k-1}$, we must have $\lambda_{k,k+1}'
		= \lambda_{k+1,k}$ and
	\begin{equation*}
		-\lambda'_{k,k+1}\delta'_{k+1}(x_{k+1}) = \delta_{k+1}(x_k) \in R'_k \cap R_k = R_{k-1},
	\end{equation*}
	%
	as desired. Furthermore, this yields
	\begin{align*}
		\sigma'_{k+1}(x_{k+1}) & = \lambda'_{k+1,k}x_{k+1} = \lambda_{k, k+1}x_{k+1}         \\
		\delta'_{k+1}(x_{k+1}) & = -(\lambda_{k,k+1}')\inv \delta_{k+1}(x_k) = - \lambda_{k,
			k+1}\delta_{k+1}(x_k),
	\end{align*}
	showing \cref{eq:sigma_delta_prime_x_k_1}.
\end{proof}

Using the previous lemma, we can now describe what happens to the homogeneous prime
elements $y_1, \dots, y_N$.

\begin{theorem}\label{thm:y_prime_swapped_cgl}
	Assume that $R$ is a CGL extension of the form \eqref{eq:default_cgl_presentation}, with a second CGL presentation of the form \eqref{eq:swapped_cgl_presentation}. Denote with $y_1, \dots, y_N$ the sequence of homogeneous prime elements from \cref{thm:homogeneous_primes}, and $\eta : [1, N] \to \bbZ$ the associated function for \eqref{eq:default_cgl_presentation}. With respect to \eqref{eq:swapped_cgl_presentation} we can take $\eta' = \eta \circ (k, k+1)$ where $(k, k+1)$ denotes a transposition in $S_N$. Writing $y'_1, \dots, y'_N$ for the corresponding sequence of homogeneous prime elements we have:
	\begin{enumerate}[(a)]
		\item If $\eta(k) \neq \eta(k+1)$, then $y'_j = y_j$ for $j \neq k, k+1$ and $y'_k = y_{k+1},
			      y'_{k+1} = y_k$.

		\item \label{itm:eta_k_is_eta_k_plus_one} If $\eta(k) = \eta(k+1)$,
		      then
		      \begin{equation*}
			      y_k y'_k - \alpha_{k p(k)} y_{p(k)} y_{k+1}
		      \end{equation*}
		      is a homogeneous normal element of $R_{k-1}$, where we take $y_{-\infty} = 1 =
			      \alpha_{k, -\infty}$. It normalizes the elements of $R_{k-1}$ in exactly the same way that $y_{p(k)}y_{k+1}$ does. Namely, from \cref{eq:y_x_quasi_commute} we know that $y_{p(k)}y_{k+1}
			      x_j = \gamma_j x_j y_{p(k)}y_{k+1}$ for some $\gamma_j \in \bbK$ for each $j \in [1, k-1]$.
		      Then, also
		      \begin{equation*}
			      (y_ky'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1})x_j = \gamma_j x_j (y_ky'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1}).
		      \end{equation*}
		      Moreover,
		      \begin{equation}\label{eq:y_prime_in_swapped_cgl}
			      y'_j = \begin{dcases*}
				      \lambda_{k+1,k}y_j, & if $j=s^l(k+1)$ for some $l \in \bbZ_{\geq 0}$                               \\
				      y_j,                & if $j < k$, or $j>k+1$ and $j \neq s^l (k+1)$ for all $l \in \bbZ_{\geq 0}$.
			      \end{dcases*}
		      \end{equation}
	\end{enumerate}
	In both cases, we can take $\eta' = \eta \circ (k,k+1)$, where $(k, k+1)$ denotes a transposition in $S_N$.
\end{theorem}
\begin{proof}
	%
	Since $R'_j = R_j$ for $j\neq k, k+1$ we also have that $y'_j = y_j$ for $j\in [1,
			k-1]$ since they only depend recursively on the ones before. We can hence also choose
	$\eta'(j) = \eta(j)$ for all $j\in [1, k-1]$. As we already remarked in the previous
	lemma, $R'_k \cap R_k = R_{k-1}$, and hence $y'_k$ which lies in $R'_k$ but not in
	$R_{k-1}$ is not contained in $R_k$.

	If $\eta(k) \neq \eta(k+1)$, then $s(k) > k+1$, and hence $y_k$ is a homogeneous prime
	element of $R_{k+1}$ due to \cref{eq:list_of_ys_in_R_k}. So, $R_{k+1}$ has two
	homogeneous prime elements up to taking scalar multiples, $y_k$ and $y_{k+1}$, which do
	not belong to $R_{k-1}$. Since $R_{k-1}' = R_{k-1}$ and $R_{k+1}' = R_{k+1}$, it
	follows that $\eta'(k) \neq \eta'(k+1)$. Indeed, $s'(k) = k+1$ would mean that $y'_k$
	is not a homogeneous prime element of $R'_{k+1}$, and $R'_{k+1}$ would only have one
	homogeneous prime element up to taking associates which doesn't belong to $R_{k-1}$.
	Now, by the uniqueness up to taking associates of the homogeneous prime elements and
	the fact that $y'_k \notin R_k$, we have that $y'_k = \xi_{k+1}y_{k+1}$ and $y'_{k+1} =
		\xi_{k}y_k$ for some $\xi_k, \xi_{k+1} \in \bbK^\times$. Since $y_j' = y_j$ for $j \in
		[1, k-1]$, \cref{thm:homogeneous_primes} gives that $\xi_{k} = 1 = \xi_{k+1}$, and that
	we may choose $\eta'(k) = \eta(k+1)$ and $\eta'(k+1) = \eta(k)$. Additionally, since
	$R'_j = R_j$ for $j \in [k+1, N]$, we have $y'_j = \xi_j y_j$ for some $\xi_j \in
		\bbK^\times$. Applying \cref{thm:homogeneous_primes} and looking at the leading
	coefficients, we find that $\xi_j = 1$ and that we may choose $\eta'(j) = \eta(j)$ for
	all $j \in [k+1, N]$. \medskip

	If $\eta(k) = \eta(k+1)$, then $s(k) = k+1$ so that $y_k$ is not a homogeneous prime
	element of $R_{k+1}$. So, $y_{k+1}$ is the only homogeneous prime element, up to taking
	associates, in $R_{k+1}\setminus R_{k-1}$. Since $R'_{k+1} = R_{k+1}$ and $R'_{k-1} =
		R_{k-1}$ we must have that $y'_{k+1}$ is a scalar multiple of $y_{k+1}$, and that
	$\eta'(k) = \eta'(k+1)$. Because $\eta'(k) = \eta'(p(k)) = \eta(p(k))$ if $p(k) \neq
		-\infty$, we may choose $\eta'(k) = \eta'(k+1) = \eta(k+1) = \eta(k)$. Using this
	information, \cref{thm:homogeneous_primes} gives
	\begin{equation}\label{eq:recursive_yk_y_k_prime}
		\begin{alignedat}{2}
			y_k &= \begin{dcases*}
				\mathrlap{y_{p(k)}x_k - c_k,}\hphantom{y_{p(k)}x_{k+1}-c'_k,} & if $p(k) \neq -\infty$ \\
				x_k,                                                          & if $p(k) = -\infty$
			\end{dcases*}
			&
			y_{k+1} &= y_k x_{k+1} - c_{k+1}\\
			y'_k    & = \begin{dcases*}
				y_{p(k)}x_{k+1} - c'_k, & if $p(k) \neq -\infty$ \\
				x_{k+1},                & if $p(k) = -\infty$
			\end{dcases*}
			\qquad
			&
			y_{k+1} & = y'_k x_k - c'_{k+1}
		\end{alignedat}
	\end{equation}
	%
	for some $c_k,c'_k \in R_{k-1}, c_{k+1} \in R_k$ and $c'_{k+1} \in R'_{k}$. Now,
	\begin{align*}
		y_{k+1}  & = y_k x_{k+1} - c_{k+1} = y_{p(k)} x_k x_{k+1} - c_{k+1} - c_k x_{k+1} ,                                                        \\
		\shortintertext{and}
		y'_{k+1} & = y'_k x_k - c'_{k+1} = y_{p(k)}x_{k+1}x_k - c'_{k+1} - c'_k x_k = \lambda_{k+1, k}y_{p(k)}x_k x_{k+1} - c'_{k+1} - c'_{k} x_k,
	\end{align*}
	%
	where we use the convention that $y_{p(k)} = 1$ and $c'_k = c_k = 0$ if $p(k) =
		-\infty$. Since $y'_{k+1}$ is a scalar multiple of $y_{k+1}$, we must have
	\begin{equation*}
		y'_{k+1} = \lambda_{k+1,k}y_{k+1}.
	\end{equation*}
	%
	Using again that $R'_j = R_j$ for $j \in [k+1, N]$, together with
	\cref{thm:homogeneous_primes} we find $\eta'(j) = \eta(j)$ for $j\in [k+1, N]$ and
	$y'_j = \lambda_{k+1,k} y_j$ if $j = s^l(k+1)$ for some $l \in \bbZ_{\geq 0}$ while
	$y'_j = y_j$ otherwise.

	We now verify that
	\begin{equation*}
		y_k y'_k - \alpha_{k p(k)}y_{p(k)}y_{k+1} \in R_{k-1}.
	\end{equation*}
	%
	If $p(k) = -\infty$, then $y_k = x_k$ and
	\begin{equation*}
		c_{k+1} \overset{\eqref{eq:delta_of_y_pk}}{=} \alpha_{k+1, p(k+1)}\inv (\lambda_{k+1} - 1)\inv\delta_{k+1}(y_{p(k+1)})
		= \alpha_{k+1, k}\inv (\lambda_{k+1} -1)\inv \delta_{k+1}(x_k) \in R_{k-1},
	\end{equation*}
	%
	as $\delta_{k+1}(x_k) \in R_{k-1}$ by \cref{lem:swapped_cgl_sigma_delta}. By
	convention, $y_{-\infty} = 1 = \alpha_{k, -\infty}$. Hence,
	\begin{equation}\label{eq:y_k_y_k_prime_when_pk_inf}
		y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1} = y_k y'_k - y_{k+1} =  x_k x_{k+1} - (x_k x_{k+1} - c_{k+1}) = c_{k+1} \in R_{k-1},
	\end{equation}
	as desired, and we also immediately obtain that it is homogeneous, as $c_{k+1} = y_k x_{k+1} -y_{k+1}$ is homogeneous.

	Now, let us tackle the case where $p(k) \neq -\infty$. We have
	\begin{align*}
		y_k y_{p(k)}  \overset{\eqref{eq:recursive_yk_y_k_prime}} & {=} (y_{p(k)}x_k - c_k)y_{p(k)}                       \\
		\overset{\eqref{eq:y_x_quasi_commute}}                    & {=} y_{p(k)}\sigma_k(y_{p(k)}) x_k - c_k y_{p(k)}     \\
		\overset{\eqref{eq:sigma_of_y}}                           & {=} \alpha_{kp(k)} y_{p(k)}y_{p(k)}x_k - c_k y_{p(k)} \\
		\overset{\eqref{eq:y_quasi_commute}}                      & {=} \alpha_{kp(k)}y_{p(k)}y_k,
	\end{align*}
	and hence
	\begin{align*}
		y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1} & = y_k (y_{p(k)}x_{k+1}-c'_k) -\alpha_{kp(k)}y_{p(k)}(y_kx_{k+1}-c_{k+1}) \\
		                                         & = -y_k c'_k + \alpha_{kp(k)}y_{p(k)}c_{k+1} \in R_k.
	\end{align*}
	%
	On the other hand,
	\begin{align*}
		\sigma'_{k+1}(y'_k)                          & = \sigma'_{k+1}(y_{p(k)}x_{x+1} - c'_k)                                \\
		\overset{\eqref{eq:sigma_delta_prime_x_k_1}} & {=} \alpha_{kp(k)}\lambda_{k,k+1}y_{p(k)}x_{k+1} - \sigma_{k+1}'(c'_k) \\
		\overset{\eqref{eq:sigma_of_y}}              & {=} \alpha_{kp(k)}\lambda_{k+1,k}\inv y'_k,
	\end{align*}
	from which we obtain
	\begin{align*}
		y_k y_k' - \alpha_{kp(k)}y_{p(k)}y_{k+1} & = (y_{p(k)}x_k -c_k)y'_k -\alpha_{kp(k)}y_{p(k)}\lambda_{k+1,k}\inv y_{p(k)} y'_{k+1}                                                       \\
		                                         & = y_{p(k)}(\sigma'_{k+1}(y'_k)x_k + \delta'_{k+1}(y'_k)) -c_k y'_k -\alpha_{kp(k)}y_{p(k)}\lambda_{k+1,k}\inv y_{p(k)}(y'_k x_{k}-c'_{k+1}) \\
		                                         & = y_{p(k)}\delta'_{k+1}(y'_k) -c_k y'_k -\alpha_{kp(k)}y_{p(k)}\lambda_{k+1,k}\inv y_{p(k)}c'_{k+1} \in R'_k.
	\end{align*}
	%
	So, $y_k y_k'- \alpha_{kp(k)}y_{p(k)}y_{k+1} \in R_k \cap R_k' = R_{k-1}$, which is
	what we wanted to show. Let us now show that it is also homogeneous in this case.

	By \cref{eq:delta_of_y_pk}, $c'_k$ and $c_{k+1}$ are scalar multiples of $\delta'_k
		(y_{p(k)}) = \delta_{k+1}(y_{p(k)})$ and $\delta_{k+1}(y_k)$ respectively. So, by
	\cref{lem:h_after_delta}, we have that
	\begin{align*}
		h \cdot (y_k c'_k)        & = \chi_{y_k}(h)y_k h \cdot (\xi \delta_{k+1}(y_{p(k)}))                              \\
		                          & = \chi_{y_k}(h)y_k \chi_{x_{k+1}}(h) \chi_{y_{p(k)}}(h)\xi \delta_{k+1}(y_{p(k)})    \\
		                          & = \chi_{y_k}(h)\chi_{x_{k+1}}(h)\chi_{y_{p(k)}}(h) y_k c'_k                          \\
		\shortintertext{and}
		h \cdot (y_{p(k)}c_{k+1}) & = \chi_{y_{p(k)}}(h) y_{p(k)} h \cdot (\xi' \delta_{k+1}(y_k))                       \\
		                          & = \chi_{y_{p(k)}}(h)y_{p(k)}  \chi_{x_{k+1}}(h) \chi_{y_k}(h) \xi' \delta_{k+1}(y_k) \\
		                          & = \chi_{y_{p(k)}}(h)  \chi_{x_{k+1}}(h) \chi_{y_k}(h) y_{p(k)}c_{k+1},
	\end{align*}
	%
	for all $h \in \mcH$. Hence, $-y_k c'_k + \alpha_{kp(k)}y_{p(k)}c_{k+1} = y_k y'_k -
		\alpha_{kp(k)}y_{p(k)}y_{k+1}$ is homogeneous.

	It remains to show that it is normal in $R_{k-1}$. By \cref{eq:y_x_quasi_commute}, we
	get that
	\begin{equation*}
		(y_k y_k')x_j = \beta_j x_j (y_k y'_k),
	\end{equation*}
	and
	\begin{equation*}
		(y_{p(k)}y_{k+1})x_j = \gamma_j x_j (y_{p(k)}y_{k+1}),
	\end{equation*}
	for all $j \in [1, k-1]$, where
	\begin{align*}
		\beta_j & = (\alpha'_{jk})\inv \alpha_{jk} \inv                                                                                   \\
		        & = \left(\prod_{m = 0}^{O_{-}(k)}\lambda_{j,p^m (k)} \prod_{l=0}^{O_{-}(k)}\lambda'_{j,p^l(k)}\right)\inv                \\
		        & = \left(\lambda_{j, k+1}\prod_{m = 0}^{O_{-}(k)}\lambda_{j,p^m (k)} \prod_{l=1}^{O_{-}(k)}\lambda_{j,p^l(k)}\right)\inv \\
		        & = \left(\prod_{m = 0}^{O_{-}(k+1)}\lambda_{j,p^m (k)} \prod_{l=0}^{O_{-}(p(k))}\lambda_{j,p^l(p(k))}\right)\inv         \\
		        & = (\alpha_{j,k+1} \alpha_{j, p(k)})\inv                                                                                 \\
		        & = \gamma_j.
	\end{align*}
	This completes the proof.
\end{proof}

Although \cref{thm:y_prime_swapped_cgl}~\ref*{itm:eta_k_is_eta_k_plus_one} does not
give an explicit formula for $y'_k$ in terms of $y_k$, we can make it more explicit, by
using the following fact, analogous to prime factorization.
\begin{theorem}[\protect{\cite[Proposition 3.1]{GoodearlYakimov2017QCA}}]\label{thm:normal_in_UFD}
	%
	Let $R$ be a CGL extension\footnote{The statement holds more generally for Noetherian
		$\mcH$-UFD's, but we only need this specific case.}. Every homogeneous normal element
	in $R$ is either a unit or a product of prime homogeneous elements. The factors are
	unique up to reordering and taking associates\index{associates}, i.e., multiplication
	by elements of $\bbK^\times$.
\end{theorem}
Let us write
\begin{equation}\label{eq:P_of_k}
	P(k) \defeq \{j \in [1,  k] \mid s(j) > k\}.
\end{equation}
\index{P k@$P(k)$}%%%
%
Then in the context of \cref{thm:homogeneous_primes}, the homogeneous primes of $R_k$
are given by $\{y_j \mid j \in P(k)\}$. The following theorem now describes $y'_k$ in
terms of $y_1, \dots, y_N$ in a way that is very reminiscent of quantum cluster
mutations.
\begin{theorem}\label{thm:almost_cluster_mutation}
	%
	With the same assumptions as
	\cref{thm:y_prime_swapped_cgl}~\ref*{itm:eta_k_is_eta_k_plus_one}, there exist a
	collection of nonnegative integers $\{m_i \mid i \in P(k-1), i\neq p(k)\}$ and $\kappa
		\in \bbK^\times$ such that
	\begin{equation*}
		y'_k = y_k\inv \left(\alpha_{kp(k)}y_{p(k)}y_{k+1} + \kappa \prod_{i \in P(k-1), i\neq p(k)} y_i^{m_i}\right).
	\end{equation*}
\end{theorem}
\begin{proof}
	Since $y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1}$ is a homogeneous normal element of $R_{k-1}$, it follows from \cref{thm:normal_in_UFD} that
	\begin{equation*}
		y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1} = \kappa \prod_{i \in P(k-1)} y_i^{m_i}
	\end{equation*}
	%
	for some $\kappa \in \bbK$ and a collection of nonnegative integers $\{m_i \mid i \in
		P(k-1)\}$, as the set $\{y_i \mid i \in P(k-1)\}$ contains all homogeneous prime
	elements of $R_{k-1}$ up to associates by \cref{thm:homogeneous_primes}. If $p(k) =
		-\infty$, then \cref{eq:y_k_y_k_prime_when_pk_inf} gives that the $\kappa$ can not be
	zero as $c_{k+1} \neq 0$. In this case, also $i \neq p(k)$ for all $i \in P(k-1)$.
	Thus, it remains to show that $\kappa \neq 0$ and $m_{p(k)} = 0$ if $p(k) \neq -
		\infty$.

	If $\kappa = 0$, then $y_k y'_k = \alpha_{kp(k)}y_{p(k)}y_{k+1}$, which is a
	contradiction, as $y_{k+1}$ is a prime element of $R_{k+1}$ which does not divide
	either $y_k$ or $y'_k$ (cf. \cref{lem:prime_divides_product}).

	If $m_{p(k)} \neq 0$ and $p(k) \neq -\infty$, then $y_{p(k)}$ is a prime element of
	$R_{k-1}$ since $s(p(k)) = k > k-1$, and
	\begin{equation*}
		y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1} \in y_{p(k)}R_{k-1},
	\end{equation*}
	which implies
	\begin{equation*}
		y_k y'_k \in y_{p(k)}R_{k+1}.
	\end{equation*}
	%
	From \cref{thm:homogeneous_primes} we know that we can write $y_k = y_{p(k)}x_k - c_k$
	and $y'_k = y_{p(k)}x_{k+1} - c'_k$ for some $c_k, c'_k \in R_{k-1}$. Then $y_{p(k)}$
	does not divide $c_k$, as otherwise $y_{p(k)}$ would divide $y_k$, and they would be
	associates by \cref{thm:normal_in_UFD}. Similarly, $y_{p(k)}$ does not divide $c'_k$.
	Hence,
	\begin{align*}
		c_kc'_k & = c_k (y'_k - y_{p(k)}x_{k+1})                         \\
		        & = y_ky'_k - y_{p(k)}x_ky'_k + c_k y_{p(k)}x_{k+1}      \\
		        & \in (y_{p(k)} R_{k+1}) \cap R_{k-1} = y_{p(k)}R_{k-1},
	\end{align*}
	%
	as $c_kc'_k \in R_{k-1}$ and $c_k y_{p(k)} \in R_{k-1}y_{p(k)} = y_{p(k)}R_{k-1}
		\subseteq y_{p(k)}R_{k+1}$ by normality of $y_{p(k)}$ in $R_{k-1}$. So, $y_{p(k)}$
	divides either $c_k$ or $c'_k$ in $R_{k-1}$, a contradiction.
\end{proof}

We explore the results of \cref{thm:almost_cluster_mutation} in
\cref{exmp:heisenberg_two_presentations}. Because it will be convenient for the example
to first introduce some additional notation and definitions, we defer it to the next
subsection.

\subsection{Symmetric CGL extensions}

In order to construct mutations, the previous subsection tells us that we should
consider different CGL extension presentations. It might not always be the case that a
CGL extension has different presentations. A symmetry condition ensures that the CGL
extension has enough presentations for our purposes of constructing a quantum cluster
algebra.

\begin{definition}[\protect{\cite[Definition 3.12]{GoodearlYakimov2017QCA}}]
	We call a CGL extension, $R$, \emph{symmetric}\index{CGL extension!symmetric} if the following conditions hold
	\begin{enumerate}
		\item For all $1\leq j < k \leq N$,
		      \begin{equation*}
			      \delta_k (x_j) \in R_{[j+1, k-1]}.
		      \end{equation*}
		      %
		      Recall that $R_{[j+1,k-1]} \defeq \bbK$ if $j +1 > k-1$.
		\item For all $j \in [1, N]$, there exists $h^*_j \in \mcH$ such that
		      \begin{equation*}
			      h^*_j \cdot x_k = \lambda_{kj}\inv x_k = \lambda_{jk}x_k, \, \forall k \in [j+1, N]
		      \end{equation*}
		      and $h^*_j \cdot x_j = \lambda^*_j x_j$\index{h k star@$h_k^*$}\index{lambda k star@$\lambda_k^*$} for some $\lambda_j^*\in \bbK^\times$ which is not a root of unity.
	\end{enumerate}
\end{definition}
For any symmetric CGL extension, we can make new CGL presentations as follows. Set
\begin{equation}\label{eq:sigma_star}
	\sigma_j^* \defeq (h_j^* \cdot) \in \End(R),\, \forall j \in [1, N-1].
\end{equation}
\index{sigma k star@$\sigma_k^*$}%%
Then, define the $\sigma_j^*$-derivation, $\delta_j^*$, of $R_{[j+1, N]}$ via
\begin{equation}\label{eq:delta_star}
	\delta_j^*(x_k) \defeq x_j x_k - \lambda_{jk}x_kx_j = -\lambda_{jk} \delta_k (x_j), \, \forall k \in [j+1, N].
\end{equation}
\index{delta k star@$\delta_k^*$}%%%
%
The conditions for $R$ to be a symmetric CGL extension then imply that $\sigma_k$ and
$\delta_k$ preserve $R_{[j, k-1]}$ and that $\sigma_k^*$ and $\delta_k^*$ preserve
$R_{[j+1, k]}$ for all $1 \leq j < k \leq N$. This allows us to view $R_{[j, k]}$ as
iterated Ore extension in two ways:
\begin{equation*}
	R_{[j, k]} = R_{[j, k-1]}[x_k; \sigma_k, \delta_k] \text{ and } R_{[j,k]} = R_{[j+1, k]}[x_j; \sigma_j^*, \delta_j^*].
\end{equation*}
So, we can always extend the interval $[j, k]$ to the left or the right. Doing this recursively gives rise to an iterated Ore extension presentation for $R$. For example, starting with the variable $x_N$ and always extending the interval to the left, we obtain the presentation
\begin{equation*}
	R = \bbK[x_N][x_{N-1}; \sigma_{N-1}^*, \delta_{N-1}^*]\cdots [x_1, \sigma_1^*, \delta_1^*].
\end{equation*}
%
The types of permutations that we obtain this way consist of the following subset of
the symmetric group $S_N$:
\begin{equation*}
	\Xi_N \defeq \{\tau \in S_N \mid \tau(k) = \max (\tau ([1, k-1])) + 1 \text{ or } \tau(k) = \min (\tau ([1, k-1])) - 1, \forall k \in [2, N]\}.
\end{equation*}
\index{Xi N@$\Xi_N$}%%
%
Each $\tau \in \Xi_N$ gives rise to a CGL presentation (cf. \cite[Proposition
	3.14]{GoodearlYakimov2017QCA}):
\begin{equation}\label{eq:cgl_presentation_tau}
	R = \bbK[x_{\tau(1)}][x_{\tau(2)}; \sigma_{\tau(2)}'', \delta_{\tau(2)}''] \cdots [x_{\tau(N)}; \sigma_{\tau(N)}'', \delta_{\tau(N)}''],
\end{equation}
%
where
\begin{itemize}
	\item $\sigma''_{\tau(k)} = \sigma_{\tau(k)}, \delta_{\tau(k)}'' = \delta_{\tau(k)}$
	      and $h_{\tau(k)}'' = h_{\tau(k)}$ if $\tau(k) = \max(\tau([1,k-1])) + 1$.
	\item
	      $\sigma''_{\tau(k)} = \sigma^*_{\tau(k)}, \delta_{\tau(k)}'' = \delta^*_{\tau(k)}$ and
	      $h_{\tau(k)}'' = h_{\tau(k)}^*$ if $\tau(k) = \min(\tau([1,k-1])) - 1$.
\end{itemize}

In what follows it will be convenient to use the following notation for $\tau \in S_N$:
\begin{equation*}
	\tau = [\tau(1), \tau(2), \dots, \tau(N)].
\end{equation*}
%
The elements of $\tau \in \Xi_N$ have the property that $\tau([1, k])$ is an interval
for each $k \in [1, N]$. Indeed, $\tau(1)$ is a singleton and hence an interval. Then,
by induction, $\tau([1, k-1])$ is an interval, say $[i, j] \subset [1, N]$ and $\tau(k)
	= j + 1$ or $\tau(k) = i - 1$ by definition. Hence, $\tau([1, k]) = [i-1, j]$ or
$\tau([1, k]) = [i, j+1]$ both of which are intervals. It helps to have the mental
picture in mind that an element $\tau \in \Xi_N$ is built iteratively by choosing some
$\tau(1) \in [1, N]$ and then appending iteratively to the left or right until the
whole interval $[1, N]$ has been made (cf. \cref{fig:mental_picture_Xi_N}).

\begin{figure}
	\centering
	\begin{tikzpicture}
		\tikzset{
			c/.style={insert path={circle[radius=0.5pt]}},
			d/.style={insert path={circle[radius=1.5pt]}},
		}
		\draw[fill] (0,0)[c]  (1,0) [c] (2,0) [d] (3,0) [c] (4,0) [c] (5,0) [c] (6,0) [c];
		\draw[fill] (0,-1)[c] (1,-1) [d] -- (2,-1) [d] (3,-1) [c] (4,-1) [c] (5,-1) [c] (6,-1) [c];
		\draw[fill] (0,-2)[c] (1,-2) [d] -- (2,-2) [d]  -- (3,-2) [d] (4,-2) [c] (5,-2) [c] (6,-2) [c];
		\draw[fill] (0,-3)[c] (1,-3) [d] -- (2,-3) [d]  -- (3,-3) [d] -- (4,-3) [d] (5,-3) [c] (6,-3) [c];
		\draw[fill] (0,-4)[d] -- (1,-4) [d] -- (2,-4) [d]  -- (3,-4) [d] -- (4,-4) [d] (5,-4) [c] (6,-4) [c];
		\draw[fill] (0,-5)[d] -- (1,-5) [d] -- (2,-5) [d]  -- (3,-5) [d] -- (4,-5) [d] -- (5,-5) [d] (6,-5) [c];
		\draw[fill] (0,-6)[d] -- (1,-6) [d] -- (2,-6) [d]  -- (3,-6) [d] -- (4,-6) [d] -- (5,-6) [d] -- (6,-6) [d];
		\node (t1) at (-1,0) {$\tau([1,1])$};
		\node (t2) at (-1,-1) {$\tau([1,2])$};
		\node (t3) at (-1,-2) {$\tau([1,3])$};
		\node (t4) at (-1,-3) {$\tau([1,4])$};
		\node (t5) at (-1,-4) {$\tau([1,5])$};
		\node (t6) at (-1,-5) {$\tau([1,6])$};
		\node (t7) at (-1,-6) {$\tau([1,7])$};
	\end{tikzpicture}
	\caption{The elements of $\Xi_N$ are built by iteratively appending to the left or the right. Shown is a visual representation of the element $[3,2,4,5,1,6,7] \in \Xi_7$.}
	\label{fig:mental_picture_Xi_N}
\end{figure}

\begin{remark}

	The property of being symmetric depends on the chosen presentation. It is possible that
	the conditions might be satisfied for one presentation, but not for another. If the
	symmetry condition was satisfied for every presentation, then every order of adjoining
	the generators would yield a valid presentation. Indeed, from the above we know that if
	$R$ is symmetric with respect to a certain presentation, then each $\tau \in \Xi_N$
	yields a valid CGL extension presentation by adjoining the generators in the order
	$x_{\tau(1)}, \dots, x_{\tau(N)}$. If $R$ was also symmetric for each of these
	presentations, then for each $\tau, \tau' \in \Xi_N$ we would have that $\tau'\tau$
	yields a valid presentation. By induction, we then conclude that each element of the
	subgroup of $S_N$ generated by $\Xi_N$ would yield a valid presentation. Call this
	subgroup $G$. It remains to show that $G = S_N$.

	For each $i \in [1, N]$, the cycle $(1,2, \dots, i) = [2,3,\dots,i , 1, i+1, i+2,
		\dots, N]$ is contained in $\Xi_N$. Then since $(1,2, \dots, i+1)\inv (1, 2, \dots, i)
		= (i, i+1)$ for all $i \in [1, N-1]$ and $S_N$ is generated by the transpositions $(i,
		i+1),\, i \in [1, N-1]$ it follows that $G = S_N$.
\end{remark}

\begin{example}

	We show that the algebra $\Heis(\mcU_q(\mfn_2))$ from \cref{exmp:heisenberg} is a
	symmetric CGL extension. The first condition is verified easily by using
	\cref{table:sigma_delta_heisenberg}. For example, for $k = 5$ we have
	\begin{align*}
		 & \delta_5(x_1) = \delta_5(E_2) = (q\inv - q)F_1 \in R_{[2,4]},                   \\
		 & \delta_5(x_2) = \delta_5(E_{12}) = (q\inv - q)(F_1E_1 - E_1 F_1) \in R_{[3,4]}, \\
		 & \delta_5(x_3) = \delta_5(E_{1}) = 0 \in R_{[4,4]},                              \\
		 & \delta_5(x_3) = \delta_5(F_{1}) = 0 \in R_{[5,4]} = \bbK.
	\end{align*}
	%
	For the second condition, we can take
	\begin{align*}
		h_1^* & = h_1\inv =(1, q, q\inv), \quad h_4^* = h_4\inv = (q\inv, q, 1), \\
		h_2^* & = h_2\inv =(q, 1, q\inv), \quad h_5^* = h_5\inv = (q\inv,1, q),  \\
		h_3^* & = h_3\inv =(q, q\inv, 1), \quad h_6^* = h_6\inv = (1, q\inv, q).
	\end{align*}
	%
	Furthermore, $\lambda_1^* = \lambda_2^* = \cdots = \lambda_6^* = q^2$ is not a root of
	unity.
\end{example}

We now look at an example of \cref{thm:almost_cluster_mutation} in action.

\begin{example}\label{exmp:heisenberg_two_presentations}

	Consider again the algebra $R = \HeisUqn$\index{Heis@$\HeisUqn$} from
	\cref{exmp:heisenberg}. We will now compute the sequence of homogeneous primes from
	\cref{thm:homogeneous_primes} for two different CGL extension presentations of the form
	\cref{eq:default_cgl_presentation,eq:swapped_cgl_presentation}. The two presentations
	that we consider correspond to the elements
	\begin{equation*}
		\tau = [2,3,4,1,5,6] \in \Xi_6 \quad \text{and}\quad \tau' = [2,3,1,4,5,6] \in \Xi_6.
	\end{equation*}
	%
	Recalling \cref{eq:cgl_presentation_tau,eq:sigma_star,eq:delta_star}, we find the
	presentations
	\begin{align*}
		R_\tau    & = \bbK[E_{12}][E_1; \sigma_3, \delta_3][F_1; \sigma_4, \delta_4][E_2; \sigma_1^*, \delta_1^*][F_{12};\sigma_5, \delta_5][F_2; \sigma_6, \delta_6], \\
		R_{\tau'} & = \bbK[E_{12}][E_1; \sigma_3, \delta_3][E_2; \sigma_1^*, \delta_1^*][F_1; \sigma_4, \delta_4][F_{12};\sigma_5, \delta_5][F_2; \sigma_6, \delta_6],
	\end{align*}
	where
	\begin{equation*}
		\sigma_1^*(E_{12}) = q E_{12}, \quad \sigma_1^*(E_1) = q\inv E_1, \quad \sigma_1^*(F_1) = q F_1,
	\end{equation*}
	and
	\begin{equation*}
		\delta_1^*(E_{12}) = 0, \quad \delta_1^*(E_1) = E_{12}, \quad \delta_1^*(F_1) = 0.
	\end{equation*}

	Luckily, we can re-use a lot of the computations from \cref{exmp:heisenberg_primes}.
	For example, using \cref{prop:eta_invariance} we find that the $\eta$-functions for the
	CGL extension presentations corresponding to $\tau$ and $\tau'$ can be taken to be
	$\eta\tau$ and $\eta \tau'$ respectively. So, the sequences of homogeneous primes will
	be of the following forms
	\begin{equation*}
		\begin{tikzcd}[column sep=0pt, row sep=tiny]
			y_{\tau,1} & & & & y_{\tau,5} \\
			& y_{\tau,2} & y_{\tau,3} & y_{\tau,4} & & y_{\tau,6}
		\end{tikzcd}
		\quad\text { and }\quad
		\begin{tikzcd}[column sep=0pt,row sep=tiny]
			y_{\tau',1} & & & & y_{\tau',5} \\
			& y_{\tau',2} & y_{\tau',3} & y_{\tau',4} & & y_{\tau',6}
		\end{tikzcd}.
	\end{equation*}
	%
	From this, $p_\tau(1) = p_\tau(2) = -\infty$ and hence $y_{\tau, 1} = E_{12}$ and
	$y_{\tau, 2} = E_1$, where $p_\tau$ is the predecessor function corresponding to
	$\eta\tau$. Similarly, $y_{\tau', 1} = E_{12}$ and $y_{\tau', 2} = E_1$. We now proceed
	by calculating $c_{\tau, i}$ and $c_{\tau', i}$ using \cref{eq:delta_of_y_pk}, for $i
		\in [3, 6]$.

	We have
	\begin{align*}
		\delta_{\tau, 3}(y_{\tau, p_\tau(3)})
		= \delta_4(y_{\tau, 2})
		= \delta_4(E_1)
		= 1,
	\end{align*}
	and hence
	\begin{align*}
		c_{\tau, 3}
		 & = \alpha_{\tau, 32}\inv (\lambda_{\tau, 3} - 1)\inv \delta_{\tau, 3}(y_{\tau, p_\tau(3)}) \\
		 & = \lambda_{43}\inv (\lambda_{4} - 1)\inv                                                  \\
		 & = q^{-2} (q^{-2} - 1)\inv                                                                 \\
		 & = \frac{1}{1-q^2}.
	\end{align*}
	Hence,
	\begin{equation*}
		y_{\tau, 3} = y_{\tau, 2}F_1 - \frac{1}{1-q^2} = E_1 F_1 - \frac{1}{1-q^2}.
	\end{equation*}
	For $c_{\tau', 3}$ we compute
	\begin{equation*}
		\delta_{\tau', 3}(y_{\tau', p_{\tau'}(3)}) = \delta_1^*(y_{\tau', 2}) = \delta_1^*(E_1) = E_{12},
	\end{equation*}
	and
	\begin{align*}
		c_{\tau', 3}
		 & = \alpha_{\tau', 32}\inv (\lambda_{\tau', 3} - 1)\inv \delta_{\tau', 3}(y_{\tau', p_{\tau'}(3)}) \\
		 & = \lambda_{13}\inv (\lambda_{1}^* - 1)\inv  E_{12}                                               \\
		 & =  \frac{q}{q^2 - 1} E_{12}.
	\end{align*}
	Thus,
	\begin{equation*}
		y_{\tau', 3} = y_{\tau', 2}E_2 - \frac{q}{q^2 -1} E_{12} = E_1 E_2 - \frac{q}{q^2-1}E_{12} = q y_3.
	\end{equation*}
	%
	Note that we already knew from \cref{thm:homogeneous_primes} that $y_{\tau', 3}$ and
	$y_3$ would be scalar multiples of each other, because $R_{\tau', 3} = R_3$. Since also
	$R_{\tau, 4} = R_{\tau', 4} = R_4$ it follows that $y_{\tau, 4}, y_{\tau', 4}$ and
	$y_4$ will be scalar multiples of each other. We have
	\begin{equation*}
		y_{\tau', 4} = y_{\tau',3} F_1 - c_{\tau',4} = q y_3 F_1 - c_{\tau',4},
	\end{equation*}
	from which we obtain
	\begin{equation*}
		y_{\tau', 4} = qy_4 = y_{\tau', 3} F_1 - \frac{q}{1-q^2}E_2.
	\end{equation*}
	%
	On the other hand, for $y_{\tau, 4}$ it will be a bit easier to calculate it directly
	using \cref{eq:delta_of_y_pk}.
	\begin{equation*}
		\delta_{\tau, 4}(y_{\tau, 3}) = \delta_1^*(E_1F_1) = E_{12}F_1,
	\end{equation*}
	so that
	\begin{align*}
		c_{\tau, 4}
		 & = \alpha_{\tau, 43}\inv (\lambda_{\tau, 4} - 1)\inv \delta_1^*(y_{\tau, 3})     \\
		 & = \lambda_{\tau, 43}\inv \lambda_{\tau, 42}\inv (\lambda_1^* - 1)\inv E_{12}F_1 \\
		 & = \frac{1}{q^2 - 1}E_{12}F_1,
	\end{align*}
	and
	\begin{align*}
		y_{\tau, 4}
		 & = y_{\tau, 3}E_2 + \frac{1}{1-q^2}E_{12}F_1                               \\
		 & = E_1F_1E_2  - \frac{1}{q^2 - 1}E_{12}F_1 - \frac{1}{1-q^2}E_2            \\
		 & = q\inv E_1E_2F_1  - q\inv\frac{q}{q^2 - 1}E_{12}F_1 - \frac{1}{1-q^2}E_2 \\
		 & = q\inv y_{\tau', 3}F_1 - \frac{1}{1-q^2}E_2                              \\
		 & = y_4.
	\end{align*}

	The remaing homogeneous prime elements are now easily determined. First note that
	$R_{\tau, 5} = R_5$ and $R_{\tau, 6} = R_6$ while also $y_{\tau, p_\tau(5)} = y_{\tau,
				1} = y_2 = y_{p(5)}$ and $y_{\tau, p_\tau(6)} = y_{\tau, 4} = y_4 = y_{p(6)}$. Thus, it
	follows that $y_{\tau, 5} = y_5$ and $y_{\tau, 6} = y_6$. Similar arguments show that
	$y_{\tau', 5} = y_5$ and $y_{\tau', 6} = q y_{6}$. Hence,
	\begin{align*}
		 & y_{\tau', 1} = y_{\tau, 1},\quad y_{\tau', 2} = y_{\tau, 2},\quad y_{\tau', 4} = qy_{\tau, 4},\quad y_{\tau', 5} = y_{\tau, 5},\quad y_{\tau', 6} = qy_{\tau, 6},
	\end{align*}
	in agreement with \cref{thm:y_prime_swapped_cgl}. Looking at the conclusion of \cref{thm:almost_cluster_mutation}, we should have
	\begin{equation*}
		y_{\tau, 3}y_{\tau', 3} = \alpha_{\tau, 32}y_{\tau, 2}y_{\tau, 4} + \kappa y_{\tau, 1}^m
	\end{equation*}
	%
	for some $m \in \bbZ_{\geq 0}$ and $\kappa \in \bbK^\times$. Indeed,
	\begin{align*}
		y_{\tau, 3}y_{\tau',3}
		 & = y_{\tau, 3}(E_1 E_2 - \frac{q}{q^2 - 1}E_{12})                                  \\
		 & = y_{\tau, 3}E_1 E_2 + \frac{q}{1-q^2}E_1 F_1 E_{12} - \frac{q}{(1-q^2)^2}E_{12},
	\end{align*}
	%
	and
	\begin{align*}
		q^2 y_{\tau, 2} y_{\tau, 4}
		 & = q^2 E_1 y_{\tau, 3} E_2 + \frac{q^2}{1-q^2}E_1 E_{12} F_1 \\
		 & = y_{\tau, 3} E_1 E_2 + \frac{q}{1-q^2} E_1 F_1 E_{12},
	\end{align*}
	so that we find $m = 1$, and $\kappa = -\frac{q}{(1-q^2)^2}$.
\end{example}

\subsection{CGL extensions as cluster algebras}

Let $R$ be a CGL extension. From \cref{thm:homogeneous_primes} we obtain a sequence
$y_1, \dots, y_N$ of homogeneous prime elements which quasi-commute. If a different CGL
extension presentation is chosen, then this yields a different sequence of homogeneous
prime elements. When $R$ is a symmetric CGL extension, we obtain a presentation for
each $\tau \in \Xi_N$. Suppose that $\tau, \tau' \in \Xi_N$ are a pair of
\emph{adjacent permutations}\index{adjacent permutation}, i.e., such that $\tau' = \tau
	(k, k+1)$ for some $k \in [1, N-1]$ where $(k, k+1) \in S_N$ denotes a transposition
(cf. \cref{fig:xi_6_graph}). Then the two presentations obtained this way will be
adjacent presentations as in the setting of \cref{thm:y_prime_swapped_cgl}:
\begin{align*}
	 & R = \bbK[x_{\tau(1)}]\cdots [x_{\tau(k)}; \sigma_{\tau, k}, \delta_{\tau, k}][x_{\tau(k+1)};\sigma_{\tau, k+1}, \delta_{\tau, k+1}] \cdots [x_\tau(N); \sigma_{\tau, N}, \delta_{\tau, N}]        \\
	 & R = \bbK[x_{\tau(1)}]\cdots [x_{\tau(k+1)}; \sigma_{\tau', k}, \delta_{\tau', k}][x_{\tau(k)};\sigma_{\tau', k+1}, \delta_{\tau', k+1}] \cdots [x_\tau(N); \sigma_{\tau', N}, \delta_{\tau', N}].
\end{align*}
%
Up to a suitable rescaling, \cref{thm:y_prime_swapped_cgl,thm:almost_cluster_mutation}
then tell us that the sequence of homogeneous prime elements $y_{\tau', 1}, \dots,
	y_{\tau', N}$ corresponding to the presentation corresponding to $\tau'$ is obtained
from $y_{\tau, 1}, \dots, y_{\tau, N}$ by a reordering or by a mutation of $y_{\tau,
			k}$. We summarize these findings (together with some extrapolated conjectures) in the
following imprecise statement. Formulating a precise statement will be done in the next
section (cf. \cref{thm:gy_main_result}).

\begin{theorem*}
	%
	Let $R$ be a symmetric CGL extension. Then it has the structure of a quantum cluster
	algebra which equals the corresponding upper cluster algebra. For each $\tau \in
		\Xi_N$, the sequence of homogeneous prime elements $y_{\tau, 1}, \dots, y_{\tau, N}$ of
	\cref{thm:homogeneous_primes} for the presentation corresponding to $\tau$ form the
	cluster variables of a quantum seed (up to a reordering and rescaling). All such
	quantum seeds are mutation-equivalent to each other, and mutations occur between seeds
	corresponding to pairs of adjacent permutations $\tau' = \tau(k, k+1)$.
\end{theorem*}

\begin{figure}
	\centering
	\begin{tikzpicture}[
			x = 0.01ex, y=0.01ex,
			scale=10, xscale= -3,
			every node/.style={font=\footnotesize}
		]

		\draw
		(99.0, 18.0) node (0){$[1, 2, 3, 4, 5, 6]$}
		(99.0, 90.0) node (1){$[2, 1, 3, 4, 5, 6]$}
		(99.0, 162.0) node (2){$[2, 3, 1, 4, 5, 6]$}
		(63.0, 234.0) node (3){$[3, 2, 1, 4, 5, 6]$}
		(135.0, 234.0) node (4){$[2, 3, 4, 1, 5, 6]$}
		(63.0, 306.0) node (5){$[3, 2, 4, 1, 5, 6]$}
		(27.0, 378.0) node (6){$[3, 4, 2, 1, 5, 6]$}
		(27.0, 450.0) node (7){$[4, 3, 2, 1, 5, 6]$}
		(135.0, 306.0) node (8){$[2, 3, 4, 5, 1, 6]$}
		(99.0, 378.0) node (9){$[3, 2, 4, 5, 1, 6]$}
		(99.0, 450.0) node (10){$[3, 4, 2, 5, 1, 6]$}
		(27.0, 522.0) node (11){$[4, 3, 2, 5, 1, 6]$}
		(99.0, 522.0) node (12){$[3, 4, 5, 2, 1, 6]$}
		(27.0, 594.0) node (13){$[4, 3, 5, 2, 1, 6]$}
		(27.0, 666.0) node (14){$[4, 5, 3, 2, 1, 6]$}
		(27.0, 738.0) node (15){$[5, 4, 3, 2, 1, 6]$}
		(171.0, 378.0) node (16){$[2, 3, 4, 5, 6, 1]$}
		(171.0, 450.0) node (17){$[3, 2, 4, 5, 6, 1]$}
		(171.0, 522.0) node (18){$[3, 4, 2, 5, 6, 1]$}
		(99.0, 594.0) node (19){$[4, 3, 2, 5, 6, 1]$}
		(171.0, 594.0) node (20){$[3, 4, 5, 2, 6, 1]$}
		(99.0, 666.0) node (21){$[4, 3, 5, 2, 6, 1]$}
		(99.0, 738.0) node (22){$[4, 5, 3, 2, 6, 1]$}
		(63.0, 810.0) node (23){$[5, 4, 3, 2, 6, 1]$}
		(171.0, 666.0) node (24){$[3, 4, 5, 6, 2, 1]$}
		(171.0, 738.0) node (25){$[4, 3, 5, 6, 2, 1]$}
		(135.0, 810.0) node (26){$[4, 5, 3, 6, 2, 1]$}
		(63.0, 882.0) node (27){$[5, 4, 3, 6, 2, 1]$}
		(135.0, 882.0) node (28){$[4, 5, 6, 3, 2, 1]$}
		(99.0, 954.0) node (29){$[5, 4, 6, 3, 2, 1]$}
		(99.0, 1026.0) node (30){$[5, 6, 4, 3, 2, 1]$}
		(99.0, 1098.0) node (31){$[6, 5, 4, 3, 2, 1]$};
		\begin{scope}[-]
			\draw[dashed] (1) to (0);
			\draw (2) to (1);
			\draw[dashed] (3) to (2);
			\draw (4) to (2);
			\draw (5) to (3);
			\draw[dashed] (5) to (4);
			\draw[dashed] (6) to (5);
			\draw (7) to (6);
			\draw[dashed] (8) to (4);
			\draw[dashed] (9) to (5);
			\draw[dashed] (9) to (8);
			\draw[dashed] (10) to (6);
			\draw[dashed] (10) to (9);
			\draw[dashed] (11) to (7);
			\draw (11) to (10);
			\draw (12) to (10);
			\draw (13) to (11);
			\draw (13) to (12);
			\draw[dashed] (14) to (13);
			\draw[dashed] (15) to (14);
			\draw (16) to (8);
			\draw (17) to (9);
			\draw[dashed] (17) to (16);
			\draw (18) to (10);
			\draw[dashed] (18) to (17);
			\draw (19) to (11);
			\draw (19) to (18);
			\draw (20) to (12);
			\draw (20) to (18);
			\draw (21) to (13);
			\draw (21) to (19);
			\draw (21) to (20);
			\draw (22) to (14);
			\draw[dashed] (22) to (21);
			\draw (23) to (15);
			\draw[dashed] (23) to (22);
			\draw[dashed] (24) to (20);
			\draw[dashed] (25) to (21);
			\draw (25) to (24);
			\draw[dashed] (26) to (22);
			\draw[dashed] (26) to (25);
			\draw[dashed] (27) to (23);
			\draw[dashed] (27) to (26);
			\draw (28) to (26);
			\draw (29) to (27);
			\draw[dashed] (29) to (28);
			\draw (30) to (29);
			\draw[dashed] (31) to (30);
		\end{scope}
	\end{tikzpicture}
	\caption{The subset $\Xi_6 \subset S_6$. Edges are drawn between adjacent permutations. The dashed lines indicate where $\eta(\tau(k)) \neq \eta(\tau(k+1))$ for the $\eta$-function corresponding to $\HeisUqn$ (cf. \cref{exmp:heisenberg_primes}). No mutation occurs at these edges (cf. \cref{thm:y_prime_swapped_cgl}). Finally, note that the graph is connected. Thus, every element of $\Xi_6$ can be built out of a chain of adjacent permutations starting from the identity. We will show later on that this holds in general for $\Xi_N$ (cf. \cref{lem:xi_n_characterization}).}
	\label{fig:xi_6_graph}
\end{figure}

\section{Formulating a precise statement}\label{sec:formulating_theorem}

Our goal is now to be able to formulate a precise statement on the cluster algebra
structure of symmetric CGL extensions. At the moment, there are three issues preventing
the results of \cref{thm:almost_cluster_mutation,thm:y_prime_swapped_cgl} to be used as
a cluster mutation statement.

\begin{enumerate}
	\item In order for $y'_1, \dots, y'_N$ to be a mutated cluster of $y_1, \dots, y_N$, we would
	      need $y'_j = y_j$ for all $j \neq k$. However, in \cref{eq:y_prime_in_swapped_cgl} we
	      see that $y'_j = \lambda_{k+1,k}y_j$ if $j = s^l(k+1)$ for some $l \in \bbZ_{\geq 0}$.
	\item In the setting of \cref{thm:y_prime_swapped_cgl}, the indexing of the $y'$-elements is
	      different from the indexing of the $y$-elements, i.e., we have $y'_j = y_{(k,k+1)j}$
	      when $\eta(k) \neq \eta(k+1)$. For a cluster mutation, the indices should remain
	      consistent.
	\item The factor $\kappa \in \bbK^\times$ appearing in \cref{thm:almost_cluster_mutation}. At
	      the moment we have no control over this factor. After reformulating the conclusion of
	      \cref{thm:almost_cluster_mutation} in terms of toric frames, the corresponding factor
	      should equal one.
\end{enumerate}

We will now resolve the first of the three issues, by a normalization of the
homogeneous prime elements, $y_1, \dots, y_N$. The last issue will be resolved by a
normalization of the variables $x_1, \dots, x_N$, while the second issue will be
addressed by a permutation of the cluster variables. After settling these three
problems, we will finally be ready to state the main theorem precisely and in full
generality.

\subsection{Normalization of the cluster variables}

The first step in addressing the three problems is to translate the results from
\cref{sec:cgl_introduction} to the language of toric frames. In addition to being
needed for the definition of a quantum cluster algebra, doing so will allow rescaling
and reindexing of the cluster variables more easily. We will now show that an
appropriate normalization resolves the first issue.

\medskip

For the toric frames we need to move over to the based quantum torus which requires a
matrix $\bbr$ such that $\bbr^{\cdot 2} = \bbq$. This puts an extra condition on the
base field. We need to be able to take square roots of the scalars $\lambda_{lj}$ for
all $l,j \in [1, N]$. If this is not possible in $\bbK$, one can consider the field
extension $\bbK[\sqrt{\lambda_{lj}} \mid j < l \in [1, N]]$, and consider the CGL
extension over this bigger field instead (the extension of scalars preserves the
structure of the CGL extension). In what follows we will hence assume the following
condition.

\begin{condition}\label{cond:square_roots}
	$R$ is a CGL extension where $\sqrt{\lambda_{lj}} \in \bbK$ for all
	$l, j \in [1, N]$, and a choice of
	\begin{equation*}
		\nu_{lj} \in \bbK \text{ such that } \nu^2_{lj} = \lambda_{lj}\text{ for all } l < j \in [1,N],
	\end{equation*}
	has been fixed.
\end{condition}

Define $\nu_{ll} \defeq 1$ and $\nu_{jl} \defeq \nu_{lj}\inv$ for $l < j \in [1, N]$.
Then $\bbn \defeq (\nu_{ij}) \in M_N(\bbK^\times)$\index{nu@$\bbn$} is multiplicatively
skew-symmetric, and $\bbn^{\cdot 2} = \boldsymbol{\lambda}$. Then analogous to the
definition of $\bbq$, we define
\begin{equation*}
	r_{lj} \defeq \Omega_{\bbn}(\oe_l, \oe_j) = \prod_{m=0}^{O_{-}(l)}\prod_{n=0}^{O_{-}(j)}\nu_{p^m(l), p^n(j)}.
\end{equation*}
%
Thus, the matrix $\bbr \defeq (r_{lj}) \in M_N(\bbK^\times)$\index{r@$\bbr$} is
multiplicatively skew-symmetric, and $\bbr^{\cdot 2} = \bbq$.

From \cref{thm:homogeneous_primes} it follows that the leading term of $y_k$ is given
by
\begin{equation*}
	x_k x_{p(k)} \cdots x_{p^{O_{-}(k)}} = x^{\oe_k}.
\end{equation*}
%
Furthermore,
\begin{equation*}
	x^{\oe_k}x^{\oe_j} = \Omega_{\bbl}(\oe_k, \oe_j)x^{\oe_j}x^{\oe_k} = q_{kj}x^{\oe_j}x^{\oe_k}.
\end{equation*}
%
In the based quantum torus we would consider the normalized variables $x^{(\oe_k)} =
	\mcS_{\bbn}(\oe_k)x^{\oe_k}$ instead. Since the $y_k$ quasi-commute in the same way as
their leading terms, it makes sense to normalize them in the same way:
\begin{equation}\label{eq:normalization_y}
	\oy_j \defeq \mcS_{\bbn}(\oe_j) y_j = \left(\prod_{0 \leq n < m \leq O_{-}(j)}\nu\inv_{p^m(j),p^n(j)}\right) y_j.
\end{equation}
\index{y k overline@$\oy_k$}%%

Using \cref{prop:y_quantum_torus} we then obtain a toric frame $M \colon \bbZ^N \to
	\Fract(R)$ with matrix $\bbr$ and such that
\begin{equation*}
	M(e_j) = \oy_j\quad \text{for all}\quad j \in [1, N].
\end{equation*}

\begin{example}\label{exmp:heisenberg_y_normalization}

	Suppose that $\sqrt{q} \in \bbK$ for the algebra $\HeisUqn$\index{Heis@$\HeisUqn$}. We
	now compute the $\oy_i, i\in [1,6]$. Since $\oe_1 = e_1$ and $\oe_2 = e_2$, it follows
	that $\oy_1 = y_1$ and $\oy_2 = y_2$. Then, from $\oe_3 = e_3 + e_1$, we obtain $\oy_3
		= \nu_{13}\inv y_3 = q^{\frac{1}{2}}y_3$. For $\oy_4$ we have $\oe_4 = e_4 + e_3 + e_1$
	and
	\begin{equation*}
		\oy_4 = \nu_{31}\nu_{41}\nu_{43}y_4 = q^{\frac{1}{2}}q^{-\frac{1}{2}}q y_4 = qy_4.
	\end{equation*}
	%
	Finally, $\oy_5 = \nu_{52}y_5 = q y_5$ and
	\begin{equation*}
		\oy_6 = (\nu_{31}\nu_{41}\nu_{43})\nu_{61}\nu_{63}\nu_{64} y_6 = q qq^{-\frac{1}{2}}q^{\frac{1}{2}}y_6 = q^2 y_6.
	\end{equation*}
\end{example}

For a second CGL presentation as in \cref{eq:swapped_cgl_presentation}, we define
$\bbn', \bbr'$ and $M'$ in the same way, i.e., $M'(e_j) = \oy'_j$ for all $j \in [1,
		N]$. Note that the vectors $\oe_k \in \bbZ^N$ should be computed with respect to the
predecessor function corresponding to this presentation instead. Since $\lambda'_{lj} =
	\lambda_{(k, k+1)l, (k, k+1)j}$, we may assume that the square roots have been chosen
such that
\begin{equation*}
	\bbn' = (k, k+1)\bbn (k, k+1) \in M_N(\bbK^\times).
\end{equation*}
%
In the setting of the main theorem this will be forced by \cref{cond:no_order_two}.

In the next theorem we describe $\bbr'$ in terms of $\bbr$ and show that the
normalization has the desired effect.

\begin{theorem}\label{thm:almost_mutation_toric_frame}

	Assume the setting of \cref{thm:y_prime_swapped_cgl} and that \cref{cond:square_roots}
	is satisfied.
	\begin{enumerate}[(a)]
		\item If $\eta(k) \neq \eta(k+1)$, then $\bbr' = (k, k+1)\bbr (k, k+1)$ and $\oy'_j =
			      \oy_{(k, k+1)j}$, for all $j \in [1, N]$. Hence, $M' = M(k, k+1)$.
		\item If $\eta(k) = \eta(k+1)$, then $M'(e_j) = M(e_j)$ for all $j \neq k$, and
		      \begin{equation}\label{eq:M'_of_ek}
			      M'(e_k) = M(-e_k + e_{p(k)} + e_{k+1}) + \zeta M\left(-e_k + \sum_{i \in P(k-1), i\neq p(k)}m_ie_i\right)
		      \end{equation}
		      %
		      for some $\zeta \in \bbK^\times$. Furthermore,
		      \begin{equation*}
			      \bbr' = \prescript{(E_{+}^\circ)^T}{}{\bbr}^{E^\circ_{+}},
		      \end{equation*}
		      where $E^\circ_{+}\in M_N(\bbZ)$\index{E circ plus@$E^\circ_{+}$} is the matrix with entries
		      \begin{equation*}
			      (E^\circ_{+})_{lj} = \begin{dcases*}
				      \delta_{lj} & if $j \neq k$                               \\
				      -1          & if $l = j = k$                              \\
				      1           & if $j=k$, and $l= p(k)$ or $k+1$            \\
				      0           & if $j = k$, and $l \neq p(k), k,$ or $k+1$.
			      \end{dcases*}
		      \end{equation*}
	\end{enumerate}
\end{theorem}
\begin{proof}

	If $\eta(k) \neq \eta(k+1)$, then \cref{thm:y_prime_swapped_cgl} gives that $y'_j =
		y_{(k,k+1)j}$ for all $j \in [1, N]$. In this case, we have $p'(j) = (k, k+1)p(j)(k,
		k+1)$ for all $j\in [1,N]$. Indeed,
	\begin{align*}
		(k, k+1) p'(j) & = (k, k+1)\max\{i \in [1, j-1] \mid \eta'(i) = \eta'(j)\}                \\
		               & = (k, k+1)\max\{i \in [1, j-1] \mid \eta((k, k+1) i) = \eta((k, k+1)j)\} \\
		               & = \max\{ i \in [1, (k, k+1)j-1] \mid \eta(i) = \eta((k, k+1)j)\}         \\
		               & = p((k, k+1)j),
	\end{align*}
	%
	where we take the maximum to be $-\infty$ if the set is empty, and we crucially use the
	fact that $\eta(k) \neq \eta(k+1)$. Hence,
	\begin{align*}
		\mcS_{\bbn'}(\oe_j) & = \prod_{0 \leq n < m \leq O'_{-}(j)}(\nu'_{(p')^m (j), (p')^n (j)})\inv                \\
		                    & = \prod_{0 \leq n < m \leq O'_{-}(j)}\nu\inv_{(k, k+1)(p')^m (j), (k, k+1)(p')^n (j)}   \\
		                    & = \prod_{0 \leq n < m \leq O'_{-}(j)}\nu\inv_{p^m ((k, k+1)j), p^n ((k, k+1)j)}         \\
		                    & = \prod_{0 \leq n < m \leq O_{-}((k, k+1)j)}\nu\inv_{p^m ((k, k+1) j), p^n ((k, k+1)j)} \\
		                    & = \mcS_{\bbn}(\oe_{(k, k+1)j}),
	\end{align*}
	%
	such that $\oy'_j = \oy_{(k, k+1)j}$ for all $j \in [1, N]$, which also immediately
	implies that $\bbr' = (k, k+1)\bbr (k, k +1)$.

	If $\eta(k) = \eta(k+1)$, we can still apply the same reasoning as above to show that
	$\mcS_{\bbn'}(\oe_j) = \mcS_{\bbn}(\oe_j)$ in the case that $j < k$ or $j > k+1$ and $j
		\neq s^l(k+1)$ for all $l \in \bbZ_{\geq 0}$. If $j = s^l (k+1)$ for some $l \in
		\bbZ_{\geq 0}$, then the difference between $\mcS_{\bbn'}(\oe_j)$ and
	$\mcS_{\bbn}(\oe_j)$ is that $\mcS_{\bbn'}(\oe_j)$ will contain a term $\nu_{k+1,
			k}\inv$ instead of $\nu_{k, k+1}\inv$. Hence,
	\begin{align*}
		\mcS_{\bbn'}(\oe_j) & = \nu_{k+1, k}\inv \nu_{k, k+1} \mcS_{\bbn'}(\oe_j) \\
		                    & = \nu_{k, k+1}^2 \mcS_{\bbn'}(\oe_j)                \\
		                    & = \lambda_{k, k+1} \mcS_{\bbn'}(\oe_j).
	\end{align*}
	It now follows from \cref{eq:y_prime_in_swapped_cgl} that $\oy'_j = \oy_j$ for all $j\neq k$. To prove the expression for $M'(e_k) = \oy'_k$, we start with the observation that $q_{kp(k)} = \alpha_{kp(k)}$. Indeed,
	\begin{align*}
		q_{kp(k)} & = \prod_{m=0}^{O_{-}(k)}\prod_{l=0}^{O_{-}(p(k))} \lambda_{p^m(k),p^l(p(k))}                                                                            \\
		          & = \left(\prod_{l = 0}^{O_{-}(p(k))}\lambda_{k, p^l(p(k))}\right)\left(\prod_{m=1}^{O_{-}(k)}\prod_{l=0}^{O_{-}(p(k))} \lambda_{p^m(k),p^l(p(k))}\right) \\
		          & = \alpha_{kp(k)}\left(\prod_{m=1}^{O_{-}(k)}\prod_{l=1}^{O_{-}(k)} \lambda_{p^m(k),p^l(k)}\right)                                                       \\
		          & = \alpha_{kp(k)}.
	\end{align*}
	Thus,
	\begin{equation*}
		\alpha_{kp(k)}y\inv_k y_{p(k)}y_{k+1} = y_{p(k)}y_k\inv y_{k+1}.
	\end{equation*}
	%
	So, by \cref{thm:almost_cluster_mutation}, we have that \cref{eq:M'_of_ek} holds, as
	long as the coefficients agree. Since we may choose $\zeta$, it suffices to compare the
	coefficients of $M'(e_k)$ and $M(-e_k + e_{p(k)} + e_{k+1})$, i.e., to verify that
	\begin{equation*}
		\mcS_{\bbn'}(\oe_k) = \mcS_{\bbr}(-e_k + e_{p(k)} + e_{k+1})\mcS_{\bbn}(\oe_{p(k)})\mcS_{\bbn}(\oe_k)\inv \mcS_{\bbn}(\oe_{k+1}).
	\end{equation*}
	%
	This follows from
	\begin{align*}
		\mcS_{\bbr}(-e_k + e_{p(k)} + e_{k+1})
		 & = r_{p(k),k}r_{k,k+1}r_{p(k), k+1}\inv                                                                 \\
		 & = \Omega_{\bbn}(\oe_{p(k)}, \oe_k)\Omega_{\bbn}(\oe_k, \oe_{k+1})\Omega_{\bbn}(-\oe_{p(k)}, \oe_{k+1}) \\
		 & = \Omega_{\bbn}(\oe_{p(k)}, \oe_k)\Omega_{\bbn}(e_k, \oe_{k+1})                                        \\
		 & = \Omega_{\bbn}(\oe_{p(k)}, \oe_k)\Omega_{\bbn}(e_k, \oe_{k})\Omega_{\bbn}(e_k, e_{k+1})               \\
		 & = \Omega_{\bbn}(\oe_{k}, \oe_k)\Omega_{\bbn}(e_k, e_{k+1})                                             \\
		 & = \Omega_{\bbn}(e_k, e_{k+1})                                                                          \\
		 & = \nu_{k, k+1},
	\end{align*}
	and
	\begin{align*}
		\mcS_{\bbn}(\oe_{p(k)})\mcS_{\bbn}(\oe_k)\inv \mcS_{\bbn}(\oe_{k+1})
		 & = \mcS_{\bbn}(\oe_{p(k)})\prod \{\nu_{i, k+1}\inv \mid i = p^{O_{-}(k)}(k), \dots, p(k), k\}        \\
		 & = \nu_{k, k+1}\inv  \prod \{\nu_{i, j}\inv \mid i,j = p^{O_{i}(k)}(k), \dots, p(k), k+1; \; i < j\} \\
		 & = \nu_{k, k+1}\inv\mcS_{\bbn'}(\oe_k).
	\end{align*}
	%
	It remains to show the expression for $\bbr'$. We have
	\begin{equation*}
		\Omega_{\bbr'}(e_l, e_j) = \Omega_{\bbn'}(\oe_l, \oe_j) = \Omega_{\bbn}((k, k+1)\oe_l, (k, k+1)\oe_j), \quad \text{ for all } l,j \in [1, N].
	\end{equation*}
	%
	In particular,
	\begin{equation*}
		\Omega_{\bbr'}(e_l, e_j) = \Omega_{\bbn}(\oe_l, \oe_j) = \Omega_{\bbr}(e_l, e_j)
	\end{equation*}
	for all $l, j \neq k$, and
	\begin{equation*}
		\Omega_{\bbr'}(e_k, e_j) = \Omega_{\bbn}(\oe_{p(k)} + e_{k+1}, e_j) = \Omega_{\bbn}(\oe_{p(k)} + \oe_{k+1} - \oe_k, e_j) = \Omega_{\bbr}(e_{p(k)} + e_{k+1} - e_k , e_j),
	\end{equation*}
	for all $j \neq k$.
\end{proof}

\subsection{Addressing the indexing issue}

We now proceed by addressing the indexing issue of the $y$ and $y'$ elements. To do
this we first describe everything in terms of the original presentation and the
elements $\tau \in \Xi_N$. Then, by choosing a canonical ordering for the level set of
the function $\eta$, we will ensure that the indices align.

So, let $R$ be a symmetric CGL extension, and $\tau \in \Xi_n$. Recall that each such
$\tau$ gives rise to a CGL extension presentation of the form
\begin{equation*}
	R = \bbK[x_{\tau(1)}][x_{\tau(2)}; \sigma_{\tau(2)}'', \delta_{\tau(2)}''] \cdots [x_{\tau(N)}; \sigma_{\tau(N)}'', \delta_{\tau(N)}''],
\end{equation*}
%
where
\begin{itemize}
	\item $\sigma''_{\tau(k)} = \sigma_{\tau(k)}, \delta_{\tau(k)}'' = \delta_{\tau(k)}$
	      and $h_{\tau(k)}' = h_{\tau(k)}$ if $\tau(k) = \max(\tau([1,k-1])) + 1$.
	\item $\sigma''_{\tau(k)} = \sigma^*_{\tau(k)}, \delta_{\tau(k)}'' = \delta^*_{\tau(k)}$ and
	      $h_{\tau(k)}'' = h_{\tau(k)}^*$ if $\tau(k) = \min(\tau([1,k-1])) - 1$.
\end{itemize}

We now want to define a toric frame $M_\tau$ corresponding to this new presentation in
such a way that the indexing issue gets resolved.

As before, this presentation has $\bbl$-matrix given by $\bbl_\tau = \tau\inv \bbl
	\tau$\index{lambda tau@$\bbl_\tau$}. We then define $\bbn_\tau = \tau\inv \bbn
	\tau$\index{nu tau@$\bbn_\tau$}, and $\widehat{\bbr}_\tau$\index{r tau
	hat@$\wh{r}_\tau$} the corresponding skew-symmetric matrix with entries
\begin{equation*}
	\widehat{r}_{\tau, lj} = \Omega_{\bbn_\tau}(\oe_{\tau, l}, \oe_{\tau, j}),
\end{equation*}
%
for all $l, j \in [1, N]$.	Write $\oy_{\tau, 1}, \dots, \oy_{\tau, N}$\index{y k
	overline tau@$\oy_{\tau, k}$} for the sequence of normalized homogeneous prime elements
of this presentation, and $\widehat{M}_\tau$\index{M hat tau@$\wh{M}_\tau$} as the
toric frame with matrix $\widehat{\bbr}_\tau$ and such that
\begin{equation*}
	\widehat{M}_\tau (e_k) =
	\oy_{\tau, k} \quad \text{for all}\quad k \in [1, N].
\end{equation*}

We now need to address indexing issue by permuting the order of the cluster variables.
Consider $\eta : [1, N] \to \bbZ$ satisfying the conditions of
\cref{thm:homogeneous_primes} for the \emph{original} CGL presentation of $R$. For
every element $m$ in the image of $\eta$, write
\begin{equation*}
	\eta\inv(m) = \{\tau(k_1), \dots, \tau(k_{|\eta\inv(m)|})\}
\end{equation*}
for $k_1 < \cdots < k_{|\eta\inv(m)|}$. Sort the elements of $\eta\inv(m)$ in increasing order:
\begin{equation*}
	\tau(k_{i_1}) < \cdots < \tau(k_{i_{|\eta\inv(m)|}}).
\end{equation*}
We then set $\tau_\bullet(\tau(k_j)) = \tau(k_{i_j})$\index{tau bullet@$\tau_\bullet$}, i.e., the $j$-th element in the sorted list. So, $\tau_\bullet$ sorts the elements in the level sets of $\eta$, effectively ``unscrambling'' the permutation $\tau$.

We can then finally define the toric frame $M_\tau$ as
\begin{equation}\label{eq:M_tau}
	M_\tau = \widehat{M}_\tau (\tau_\bullet \tau)\inv \colon \bbZ^N \to \Fract(R),
\end{equation}
\index{M tau@$M_\tau$}%%
which has corresponding matrix
\begin{equation}\label{eq:r_tau}
	\bbr_\tau = (\tau_\bullet \tau)\widehat{\bbr}_\tau(\tau_\bullet \tau)\inv.
\end{equation}
\index{r tau@$\bbr_\tau$}%%

This definition of $\tau_\bullet$ calls for some examples. At the same time, the
examples will demonstrate how the toric frame $M_\tau$ fixes the problem with the order
of the cluster variables.

\begin{example}
	Let us first consider $\eta \colon [1, 6] \to \bbZ$ defined as
	\begin{equation*}
		\eta(1) = \eta(4) = \eta(6) = 1, \quad \eta(2) = \eta(5) = 2, \quad \eta(3) = 3.
	\end{equation*}
	We will look at the two permutations
	\begin{align*}
		\tau  & = [3,4,2,5,1,6]  \\
		\tau' & = [3,4,2,1,5,6],
	\end{align*}
	%
	and compute $\tau_\bullet$ and $\tau'_\bullet$. We have
	\begin{align*}
		\eta\inv(1) & = \{1, 4, 6\}                          \\
		            & = \{\tau(5), \tau(2), \tau(6)\}        \\
		            & = \{\tau(k_2), \tau(k_1), \tau(k_3)\},
	\end{align*}
	from which we obtain
	\begin{align*}
		\tau_\bullet(4) & = \tau_\bullet(\tau(2)) = 1, \\
		\tau_\bullet(1) & = \tau_\bullet(\tau(5)) = 4, \\
		\tau_\bullet(6) & = \tau_\bullet(\tau(6)) = 6.
	\end{align*}
	From
	\begin{equation*}
		\eta\inv(2) = \{2, 5\} = \{\tau(3), \tau(4)\}
	\end{equation*}
	%
	we obtain $\tau_\bullet(2) = 2$ and $\tau_\bullet(5) = 5$. Since $\eta\inv(3) = \{3\}$,
	we automatically have $\tau_\bullet(3) = 3$. For $\tau'$ we find
	\begin{align*}
		\eta\inv(1) & = \{1, 4, 6\}                             \\
		            & = \{\tau'(4), \tau'(2), \tau'(6)\}        \\
		            & = \{\tau'(k_2), \tau'(k_1), \tau'(k_3)\},
	\end{align*}
	such that
	\begin{align*}
		\tau'_\bullet(4) & = \tau'_\bullet(\tau'(2)) = 1, \\
		\tau'_\bullet(1) & = \tau'_\bullet(\tau'(4)) = 4, \\
		\tau'_\bullet(6) & = \tau'_\bullet(\tau'(6)) = 6.
	\end{align*}
	%
	Similarly, one finds $\tau'_\bullet(2) = 2, \tau'_\bullet(5) = 5$ and $\tau'_\bullet(3)
		= 3$. Hence,
	\begin{equation*}
		\tau_\bullet = \tau'_\bullet = [4,2,3,1,5,6].
	\end{equation*}

	Now, remark that $\tau, \tau' \in \Xi_6$ and that $\tau' = \tau (4, 5) = (1,5) \tau$.
	Hence, if $\eta$ was the function satisfying the conditions of
	\cref{thm:homogeneous_primes} for some CGL extension of length 6, then the
	presentations corresponding to $\tau$ and $\tau'$ would satisfy the setting of
	\cref{thm:y_prime_swapped_cgl}. Since $\eta(1) = 1 \neq 2 = \eta(5)$, the conclusion of
	\cref{thm:y_prime_swapped_cgl} would be that $y_{\tau, j} = y_{\tau', (4,5)j}$ for all
	$j \in [1, N]$. Since no mutation occurs in this case, we should find that $M_\tau
		(e_j) = M_{\tau'}(e_j)$ for all $j \in [1, N]$. Indeed,
	\begin{align*}
		M_{\tau}(e_j)
		 & = \oy_{\tau, (\tau_\bullet \tau)\inv (j)}        \\
		 & = \oy_{\tau', (4,5)(\tau_\bullet \tau)\inv (j)}  \\
		 & = \oy_{\tau', (\tau_\bullet \tau (4,5))\inv (j)} \\
		 & = \oy_{\tau', (\tau_\bullet \tau')\inv (j)}      \\
		 & = M_{\tau'}(e_j).
	\end{align*}
\end{example}
\begin{example}
	We now look at $\eta \colon [1,6] \to \bbZ$ defined by
	\begin{equation*}
		\eta(1) = \eta(3) = \eta(4) = \eta(6) = 1, \quad \eta(2) = \eta(5) = 2,
	\end{equation*}
	and the two permutations $\tau, \tau' \in \Xi_6$ given by
	\begin{align*}
		\tau  & = [2,3,4,1,6,5]  \\
		\tau' & = [2,3,1,4,6,5].
	\end{align*}
	In this case $\tau_\bullet \neq \tau'_\bullet$, but
	\begin{align*}
		\tau_\bullet  & = [4,2,1,3,5,6]  \\
		\tau'_\bullet & = [3,2,1,4,5,6],
	\end{align*}
	%
	such that $\tau_\bullet \tau = \tau'_\bullet \tau'$. As $\tau' = \tau (3,4)$, we are
	again in the setting of \cref{thm:y_prime_swapped_cgl}, but now in the second case, as
	$\eta(3) = 1 = \eta(4)$. In this case, the conclusion of
	\cref{thm:almost_mutation_toric_frame} gives that we should have $M_\tau (e_j) =
		M_{\tau'}(e_j)$ for all $j \neq 3$. That is precisely why we need to permute
	$\widehat{M}_\tau$ with $\tau_\bullet$ as well.
\end{example}

The following lemma, which we will need later on, justifies the observations made in
the examples. Write $\ex = \{j \in [1, N] \mid s(j) \neq + \infty\}$.

\begin{lemma}\label{lem:tau_bullet}
	\leavevmode
	\begin{enumerate}[(a)]
		\item Take $\tau,\tau' \in \Xi_N$ such that $\tau' = \tau(k, k +1)$ for some $k \in [1,
				      N-1]$. If $\eta(\tau(k)) = \eta(\tau(k+1))$, then $\tau_\bullet'\tau' =
			      \tau_\bullet\tau$.
		\item Take $\tau,\tau' \in \Xi_N$ such that $\tau' = \tau(k, k +1)$ for some $k \in [1,
				      N-1]$. If $\eta(\tau(k)) \neq \eta(\tau(k+1))$, then $\tau'_\bullet\tau' =
			      \tau_\bullet\tau (k, k +1)$.
	\end{enumerate}
\end{lemma}
\begin{proof}\leavevmode
	\begin{enumerate}[(a)]
		\item Because $\eta(\tau(k)) = \eta(\tau(k+1)) = \eta(\tau'(k)) = \eta(\tau'(k+1))$, and
		      $\tau(j) = \tau'(j)$ for all $j\neq k, k+1$ we have $\tau\inv(L) = (\tau')\inv(L)$ for
		      all level sets, $L$, of $\eta$. Hence, $\tau_\bullet\tau = (\tau')_\bullet(\tau')$.
		\item Suppose
		      \begin{equation*}
			      \eta\inv(a) = \{\tau(k_1), \dots, \tau(k_n) \mid k_1 < \dots < k_n\}
		      \end{equation*}
		      %
		      is the level set of some $a\in \bbZ$ in the image of $\eta$. If $k, k+1 \neq k_i$ for
		      all $i \in [1, n]$, then $\tau(k_i) = \tau'(k_i)$ for all $i\in [1, n]$ and it follows
		      that $\tau_\bullet (\tau(k_i)) = (\tau')_\bullet (\tau'(k_i))$ for all $i\in [1, n]$.
		      If $k = k_j$ for some $j \in [1, n]$, then it follows that $k+1 \neq k_i$ for all $i\in
			      [1, n]$, because $\eta(\tau(k)) \neq \eta(\tau(k+1))$. Furthermore, $\tau'(k+1) =
			      \tau(k)$ implies that
		      \begin{equation*}
			      \eta\inv(a) = \{\tau'(k'_1), \dots, \tau'(k'_n)
			      \mid k'_1 < \cdots < k'_n\}	,
		      \end{equation*}
		      %
		      where $k'_i = k_i$ for all $i \neq j$ and $k'_j = k+1$. So, we see that $\tau_\bullet$
		      and $(\tau')_\bullet$ agree on this level set as well. The case where $k+1 = k_j$ for
		      some $j\in [1, n]$ is analogous.
	\end{enumerate}
\end{proof}

\subsection{Normalization of the generators}

The last issue to resolve is that of the factor $\zeta$ in
\cref{thm:almost_mutation_toric_frame}. One approach could be to try to figure out a
different normalization for the $y$-elements directly. It turns out to be easier to
rescale them indirectly through a normalization of the generators. For now we only
describe the normalization needed, but leave the technical proof that it works for
\cref{sec:normalizing_generators}.

\medskip

The key insight, is that we can find back all the variables $\oy_{\tau}$ (up to a
scalar multiple) by considering just the homogeneous prime elements of the subalgebras
$R_{[j, k]}$ of the original CGL extension presentation.

\begin{theorem}[\protect{\cite[Theorem 5.1]{GoodearlYakimov2017QCA}}]\label{thm:y_square_brackets}

	Let $R$ be a symmetric CGL extension of length $N$. For $i\in [1, N]$ and $m \in
		\bbZ_{\geq 0}$ such that $s^m(i) \neq + \infty$, there exists a unique homogeneous
	prime element $y_{[i, s^m(i)]}$\index{y i smi@$y_{[i, s^m(i)]}$} of $R_{[i, s^m(i)]}$
	with leading term $x_i x_{s(i)} \cdots x_{s^m(i)}$ such that $y_{[i, s^m(i)]} \notin
		R_{[i, s^m(i) - 1]}$ and $y_{[i, s^m(i)]} \notin R_{[i+1, s^m(i)]}$. In particular,
	$y_{[i, i]} = x_i$.
\end{theorem}

A priori, the $y_{[i, s^m(i)]}$ would only be cluster variables of the subalgebras
$R_{[i, s^m(i)]}$. We will show later that they are all actually cluster variables of
$R$ (cf. \cref{cor:cluster_variables}).

\begin{example}\label{exmp:heisenberg_y_brackets}

	We compute the $y_{[i, s^m(i)]}$ for the algebra $R = \HeisUqn$\index{Heis@$\HeisUqn$}.
	Recall that the $\eta(1) = \eta(3) = \eta(4) = \eta(6)$ and $\eta(2) = \eta(5)$. For $i
		= 1$ we just have
	\begin{equation*}
		y_{[1,1]} = y_1, \quad y_{[1, 3]} = y_3, \quad y_{[1, 4]} = y_4, \quad y_{[1, 6]} = y_6,
	\end{equation*}
	since $R_{[1, j]} = R_j$ for all $j \in [1, 6]$.  For $i = 2$, the uniqueness of \cref{thm:y_square_brackets} implies $y_{[2,5]} = y_5$. The other cases require some actual calculations. Note that \cref{prop:eta_invariance} ensures that we can calculate the predecessors and successors in the subalgebras $R_{[i, s^m(i)]}$ as in $R$.

	For $y_{[3, 4]}$ we have $\delta_4(E_1) = 1$ and hence $c_{[3,4]} = - \frac{1}{1-q^2}$
	so that
	\begin{equation*}
		y_{[3, 4]} = E_1 F_1 - \frac{1}{1-q^2}.
	\end{equation*}
	%
	Then, because $\delta_6(y_{[3,4]}) = \delta_6(E_1 F_1) = q\inv E_1 F_{12}$, we find
	\begin{equation*}
		y_{[3,6]} = y_{[3,4]} F_2 - q\inv q \frac{1}{q^{-2} - 1} q\inv E_1 F_{12}  = y_{[3,4]} F_2 - \frac{q}{1-q^2}E_1 F_{12}.
	\end{equation*}
	%
	Finally, from $\delta_6(F_1) = F_{12}$ we obtain
	\begin{equation*}
		y_{[4,6]} = F_1 F_2 - q\inv \frac{1}{q^{-2} - 1} F_{12} = F_1 F_2 - \frac{q}{1- q^2} F_{12}.
	\end{equation*}
\end{example}

We now introduce some new notation. For $i \in [1, N]$ and $m \in \bbZ$ such that
$s^m(i)\in [1, N]$, i.e., $s^m(i) \neq + \infty$, we define
\begin{equation*}
	e_{[i, s^m(i)]} \defeq e_i + e_{s(i)} + \cdots + e_{s^m(i)}.
\end{equation*}
\index{e i smi@$e_{[i, s^m(i)]}$}%%

In particular, $\oe_k = e_{[p^{O_{-}(k)}, k]}$, for all $k \in [1, N]$. By convention
$y_{\emptyset} = 1$ and $e_{\emptyset} = 0$. By applying
\cref{thm:y_prime_swapped_cgl,thm:almost_cluster_mutation} in this setting to the
permutations
\begin{equation*}
	[i+1, i+2, \dotsc, s^m(i)-1,i,s^{m}(i), s^m(i)+1, \dotsc, N, i-1, \dotsc,1] \in \Xi_N
\end{equation*}
and
\begin{equation*}
	[i+1, i+2, \dotsc, s^m(i)-1,s^m(i),i,s^m(i)+1,\dotsc, N,i-1,\dotsc,1] \in \Xi_N,
\end{equation*}
one can obtain the following result.
\begin{proposition}[\protect{\cite[Corollary 5.11]{GoodearlYakimov2017QCA}}]\label{prop:def_u_brackets}

	Let $R$ be a symmetric CGL extension of length $N$. Then, for $i\in [1, N]$ and $m \in
		\bbZ_{> 0}$ such that $s^m(i) \neq + \infty$, the element
	\begin{align*}
		u_{[i, s^m(i)]} & \defeq y_{[i, s^{m-1}(i)]}y_{[s(i), s^m(i)]} - \Omega_{\bbl}(e_i, e_{[s(i), s^{m-1}(i)]})y_{[s(i), s^{m-1}(i)]}y_{[i, s^m(i)]}        \\
		                & = y_{[i, s^{m-1}(i)]}y_{[s(i), s^m(i)]} - \Omega_{\bbl}(e_{s^m(i)}, e_{[s(i), s^{m-1}(i)]})\inv y_{[i, s^m(i)]}y_{[s(i), s^{m-1}(i)]}
	\end{align*}
	\index{u i smi@$u_{[i, s^m(i)]}$}%
	%
	is a nonzero homogeneous normal element of $R_{[i+1, s^m(i) - 1]}$ which is not a
	multiple of $y_{[s(i), s^{m-1}(i)]}$ if $m \geq 2$. It normalizes the elements of
	$R_{[i+1, s^m(i) - 1]}$ in exactly the same way as $y_{[s(i),
						s^{m-1}(i)]}y_{[i,s^m(i)]}$ does. Moreover,
	\begin{equation*}
		u_{[i, s^m(i)]} = \psi \prod_{k \in P} y^{m_k}_{[p^{O_{-}^{i+1}(k)}, k]}
	\end{equation*}
	where $\psi \in \bbK^\times, O^{i+1}_{-}(k) = \max\{n \in \bbZ_{\geq 0} \mid p^n(k) \geq i + 1\}$,
	\begin{equation*}
		P = P_{[i,s^m (i)]} = \{k \in [i, s^m(i)]\setminus \{i, s(i), \dots, s^m(i)\} \mid s(k) > s^m(i)\},
	\end{equation*}
	%
	and the integers $m_k$ are those from \cref{thm:almost_cluster_mutation}. Thus, the
	leading term of $u_{[i, s^m(i)]}$ has the form
	\begin{equation*}
		\lt (u_{[i, s^m(i)]}) = \pi_{[i, s^m(i)]} x^{f_{[i, s^m(i)]}}
	\end{equation*}
	\index{pi i smi@$\pi_{[i, s^m(i)]}$}\index{f i smi@$f_{[i, s^m(i)]}$}%
	%
	for some $\pi_{[i, s^m(i)]} \in \bbK^\times$ and $f_{[i, s^m(i)]} = n_{i+1}e_{i+1} +
		\cdots + n_{s^m(i) -1}e_{s^m(i)-1} \in \bbZ_{\geq 0}^N$ such that $n_{s(i)} = \cdots =
		n_{s^{m-1}(i)} = 0$ and $n_j = n_l$ for all $i+1 \leq j \leq l \leq s^m(i)-1$ with
	$\eta(j) = \eta(l)$.
\end{proposition}

The proposition does not apply for $m = 0$, so in this case we simply set
\begin{equation*}
	u_{[i, i]} = 1,
\end{equation*}
and hence $\pi_{[i,i]} = 1, f_{[i,i]} = 0$.

\begin{example}\label{exmp:heisenberg_u_bracket}

	We compute the elements $u_{[i, s(i)]}$ for $R = \HeisUqn$\index{Heis@$\HeisUqn$}. Note
	that in this special case
	\begin{equation*}
		u_{[i, s(i)]} = y_{[i, i]}y_{[s(i), s(i)]} - y_{[i, s(i)]} = x_i x_{s(i)} - y_{[i, s(i)]}.
	\end{equation*}
	Using \cref{exmp:heisenberg_y_brackets}, we find
	\begin{align*}
		 & u_{[1,3]} = E_2 E_1 - y_3 = \frac{1}{1-q^{-2}}E_{12},        \\
		 & u_{[2,5]} = E_{12}F_{12} - y_5 = (q - q\inv)E_1F_1 - q^{-1}, \\
		 & u_{[3,4]} = E_1 F_1 - y_{[3,4]} = \frac{1}{1-q^2},           \\
		 & u_{[4,6]} = F_1 F_2 - y_{[4,6]} = \frac{q}{1-q^2}F_{12}.
	\end{align*}
\end{example}

We now have the necessary definitions to describe the normalization of the
$x$-elements. For each $\bbg = (\gamma_1, \dots, \gamma_N) \in (\bbK^\times)^N$, one
can rescale the generators $x_1, \dots, x_N$ of $R$ by replacing them by $\gamma_1 x_1,
	\dots, \gamma_N x_N$. These still generate the same CGL extension, with the same
$\mcH$-action and matrix $\bbl$. Furthermore, for $i \in [1, N]$ and $m \in \bbZ_{\geq
		0}$ such that $s^m(i) \neq + \infty$, the subalgebra $R_{[i, s^m(i)]}$ is the same.
Since $y_{[i, s^m(i)]}$ is the \emph{unique} homogeneous prime element of $R_{[i,
					s^m(i)]}$ with a leading term $x_i x_{s(i)} \cdots x_{s^m(i)}$, we find that $y_{[i,
					s^m(i)]}$ gets replaced by $(\gamma_i \gamma_{s(i)} \cdots \gamma_{s^{m(i)}})y_{[i,
					s^m(i)]}$ after the rescaling. The definition of $u_{[i, s^m(i)]}$ then implies that
they get rescaled by
\begin{equation*}
	u_{[i, s^m(i)]} \mapsto \bbg^{e_{[i, s^m(i)]} + e_{[s(i), s^{m-1}(i)]} }u_{[i, s^m(i)]} =  (\gamma_i \gamma_{s(i)}^2 \cdots \gamma_{s^m(i)}^2 \gamma_{s^m(i)})u_{[i, s^m(i)]}.
\end{equation*}
%
Now one has to be careful to not conclude that $\pi_{[i, s^m(i)]}$ gets scaled by
exactly the same factor as $u_{[i, s^m(i)]}$. Indeed, the definition of $\pi_{[i,
				s^m(i)]}$ is as the coefficient of $x^{f_{[i, s^m(i)]}}$ which gets rescaled as well.
Hence, the scalar $\pi_{[i, s^m(i)]}$ get rescaled by the rule
\begin{equation*}
	\pi_{[i, s^m(i)]} \mapsto \bbg^{e_{[i, s^m(i)]}+e_{[s(i), s^{m-1}(i)]} - f_{[i, s^m(i)]}}\pi_{[i, s^m(i)]}.
\end{equation*}
%
The normalization that we need is described by the following proposition.
\begin{proposition}

	Let $R$ be a symmetric CGL extension of length $N$ satisfying \cref{cond:square_roots}.
	Then there exist $\bbg \in (\bbK^\times)^N$ such that after applying the normalization
	$x_j \mapsto \gamma_j x_j$ for all $j \in [1, N]$ we have
	\begin{equation}\label{eq:rescaling_conditions_for_pi}
		\pi_{[i, s(i)]} = \mcS_{\bbn}(-e_i + f_{[i, s(i)]})
	\end{equation}
	%
	for all $i \in [1, N]$ such that $s(i) \neq + \infty$. Every such $\bbg \in
		(\bbK^\times)^N$ is recursively determined by
	\begin{equation*}
		\gamma_i \text{ is arbitrary if } p(i) = -\infty
	\end{equation*}
	and
	\begin{equation*}
		\gamma_i \defeq \gamma_{p(i)}\inv \bbg^{f_{[p(i),i]}}\pi\inv_{[p(i), i]}\mcS_{\bbn}(-e_{p(i)} + f_{[p(i), i]})
	\end{equation*}
	if $p(i) \neq -\infty$. The scalars $\pi_{[p(i), i]}$ in the right-hand side are taken with respect to the original generators of $R$.
\end{proposition}
\begin{proof}

	Note that for each $i \in [1, N]$ such that $s(i) \neq -\infty$,
	\cref{eq:rescaling_conditions_for_pi} holds if and only if
	\begin{equation*}
		\gamma_i \gamma_{s(i)} \gamma^{-f_{[i, s(i)]}}\pi_{[i, s(i)]} = \mcS_{\bbn}(-e_i + f_{[i, s(i)]})
	\end{equation*}
	%
	This last equation is of course equivalent to
	\begin{equation*}
		\gamma_{s(i)} =  \gamma_{i}\inv \gamma^{f_{[i, s(i)]}}\pi_{[i, s(i)]}\inv \mcS_{\bbn}(-e_i + f_{[i, s(i)]}) \text{ for all } i \in [1, N] \text{ such that } s(i) \neq -\infty,
	\end{equation*}
	which is precisely the claim of the proposition.
\end{proof}

\begin{example}\label{exmp:heisenberg_rescaling}

	We compute $\bbg$ such that \cref{eq:rescaling_conditions_for_pi} is satisfied after
	the rescaling $x_i \mapsto \gamma_i x_i$ for $R = \HeisUqn$\index{Heis@$\HeisUqn$}.
	Since $p(1) = p(2) = -\infty$, we can take $\gamma_1 = \gamma_2 = 1$. We now determine
	$\gamma_3$. From \cref{exmp:heisenberg_u_bracket} we find $\pi_{[1, 3]} =
		\frac{1}{1-q^{-2}}$ and $f_{[1, 3]} = e_2$. Thus,
	\begin{equation*}
		\gamma_3 = \gamma_1\inv \bbg^{f_{[1,3]}}\pi_{[1,3]}\inv \mcS_{\bbn}(-e_1 + f_{[1,3]}) = (1-q^{-2})q^{\frac{1}{2}}.
	\end{equation*}
	%
	For $\gamma_4$, \cref{exmp:heisenberg_u_bracket} gives $\pi_{[3,4]} = \frac{1}{1-q^2}$
	and $f_{[3,4]} = 0$, so that
	\begin{equation*}
		\gamma_4 = \gamma_3\inv \bbg^{f_{[3,4]}}\pi_{[3,4]}\inv \mcS_{\bbn}(-e_3 + f_{[3,4]}) = q^{-\frac{1}{2}}\frac{1-q^2}{1-q^{-2}} = q^{\frac{3}{2}} \frac{1-q^2}{q^2 - 1} = -q^{\frac{3}{2}}.
	\end{equation*}
	%
	Continuing on, $\pi_{[2,5]} = (q - q\inv)$ and $f_{[2,5]} = e_3 + e_4$, from which
	\begin{align*}
		\gamma_5
		 & = \gamma_2\inv \bbg^{f_{[2,5]}}\pi_{[2,5]}\inv \mcS_{\bbn}(-e_2 + f_{[2,5]}) \\
		 & = (1-q^{-2})(-q^2)(q-q\inv)\inv \nu_{32}\inv\nu_{42}\inv\nu_{43}             \\
		 & = -q q^{\frac{1}{2}} q^{-\frac{1}{2}}q                                       \\
		 & = -q^2.
	\end{align*}
	%
	Finally, $\pi_{[4,6]} = \frac{q}{1-q^2}$ and $f_{[4,6]} = e_5$, so that
	\begin{equation*}
		\gamma_6
		= \gamma_4\inv \bbg^{f_{[4,6]}}\pi_{[4,6]}\inv \mcS_{\bbn}(-e_4 + e_5)
		= -q^{-\frac{3}{2}} (-q^2) q^{-1}(1-q^2)\nu_{54}\inv
		= (1-q^2).
	\end{equation*}

	For later convenience, we now determine the sequence of normalized homogeneous primes
	of $R = \HeisUqn$ if the normalization $x_i \mapsto \gamma_i x_i$ has been applied.
	Denote the original sequence of homogeneous primes with $y'_1, \dots, y'_6$ (cf.
	\cref{eq:heisenberg_hom_primes}). Note that the normalization of the generators does
	not change the subalgebras $R_1, \dots, R_3$, and hence \cref{thm:homogeneous_primes}
	guarantees that $\oy_1, \dots, \oy_N$ will be scalar multiples of $y'_1, \dots, y'_N$
	respectively. Furthermore, the matrix $\bbl$ remains the same, so the normalization
	constants $\mcS_{\bbn}(\oe_i)$ remain unchanged, and we can re-use the work from
	\cref{exmp:heisenberg_y_normalization}.

	Let us write $\wt{E}_2, \wt{E}_{12}, \wt{E}_1, \wt{F}_1, \wt{F}_{12}, \wt{F}_2$ for the
	normalized generators. Because $\gamma_1 = 1 = \gamma_2$, we have $\oy_1 = \oy'_1 =
		y'_1$ and $\oy_2 = \oy'_2 = y'_2$. For $\oy_3$ we have $\gamma_3 = q^{\frac{1}{2}}(1 -
		q^{-2})$. Then
	\begin{equation*}
		q^{\frac{1}{2}}(1-q^{-2})y'_3 = E_2 q^{\frac{1}{2}}(1-q^{-2})E_1 - E_{12} = \wt{E}_2\wt{E}_1 - \wt{E}_{12},
	\end{equation*}
	so that $y_3 = q^{\frac{1}{2}}(1-q^{-2})y'_3$ and $\oy_3 = q(1 -q^{-2})y'_3$. Similarly, because $\gamma_4 = -q^{\frac{3}{2}}$ we find
	\begin{equation*}
		y_4 = (1-q^2)y'_4 = q^{\frac{1}{2}}(1-q^{-2})y'_3 (-q^{\frac{3}{2}}F_1) - E_2 = y_3 \wt{F}_1 - \wt{E}_2,
	\end{equation*}
	and $\oy_4 = q y_4 = q(1-q^2)y'_4$. From $\gamma_5 = -q^2$ we find
	\begin{equation*}
		y_5 = (-q^{2})y'_5 = y_2\wt{F}_{12} -q \wt{E}_1\wt{F}_{1} + q,
	\end{equation*}
	and $\oy_5 = q y_5 = -q^{3} y'_5$. Finally, $\gamma_6 = (1-q^2)$ implies
	\begin{align*}
		y_6 & = (1-q^2)^2 y'_6                                                                         \\
		    & = (1-q^2)y'_4 ((1-q^2)F_2) - q^{\frac{1}{2}}q^{\frac{1}{2}}(1-q^{-2})y'_3(-q^2F_{12}) +1 \\
		    & = y_4\wt{F}_2 - q^{\frac{1}{2}}y_3\wt{F}_{12} + 1,
	\end{align*}
	and $\oy_6 = q^2 y_6 = q^2(1-q^2)^2 y'_6$.

	It is clear that the normalization simplifies the constants appearing in the
	expressions for the homogeneous prime elements.
\end{example}

\subsection{The precise statement}

We now finally state the main result. Afterwards we work out an example in detail, to
understand the precise statement. In addition to \cref{cond:square_roots}, the result
requires three extra conditions that we have not yet mentioned. The first condition
will be used to ensure uniqueness of square roots of certain scalars.
\begin{condition}\label{cond:no_order_two}
	The subgroup of $\bbK^\times$ generated by $\{\nu_{lj} \mid 1 \leq j < l \leq N\}$ does not contain elements of order two.
\end{condition}
%
Now, let $R$ be a symmetric CGL extension of length $N$, and define
\begin{equation}\label{eq:ex}
	\ex \defeq [1 ,N] \setminus P(N) = \{k \in [1, N] \mid s(k) \neq +\infty\}
\end{equation}
\index{ex@$\ex$}%%
%
where $s$ is the predecessor function as in \cref{thm:homogeneous_primes}. Note that by
\cref{thm:homogeneous_primes}, the elements $\{y_i \mid i \in P(N)\}$ are homogeneous
prime elements with respect to \emph{any} possible ordering of the generators. The
elements of $P(N)$ are therefore taken to be frozen.

The second condition is used to ensure that the principal part of the matrix $\tB_\tau$
in the statement is skew-symmetrizable (cf.
\cref{lem:principal_part_skew_symmetrizable}).
\begin{condition}\label{cond:lambda_star_to_the_d}
	There exist positive integers $d_i \in \bbZ_{>0}$ for $i$ in the image of $\eta$ such that
	\begin{equation*}
		(\lambda^*_l)^{d_{\eta(j)}} = (\lambda^*_j)^{d_{\eta(l)}}, \quad \forall j, l \in \ex.
	\end{equation*}
\end{condition}

Finally, the last condition is the normalization from the previous section. This is
needed to ensure that $\zeta = 1$ in \cref{eq:M'_of_ek}.
\begin{condition}\label{cond:normalization_generators}
	$R$ is a symmetric CGL extension such that \cref{eq:rescaling_conditions_for_pi} is satisfied.
\end{condition}

The main result can now be formulated.
\begin{theorem}[\protect{\cite[Theorem 8.2]{GoodearlYakimov2017QCA}}]\label{thm:gy_main_result}

	Let $R$ be a symmetric CGL extension of length $N$, and write $\ex$ as in \cref{eq:ex}.
	Assume that
	\cref{cond:square_roots,cond:normalization_generators,cond:no_order_two,cond:lambda_star_to_the_d}
	are satisfied. Then the following hold:
	\begin{enumerate}[(a)]
		\item For all $\tau \in \Xi_N$ and $l \in \ex$, there exists a unique vector $b^l_{\tau}\in
			      \bbZ^N$ such that $\chi_{M_\tau (b^l_\tau)} = 1$ and
		      \begin{equation*}
			      \Omega_{\bbr_\tau}(b^l_\tau, e_j) = 1, \quad \forall j\in [1, N],\,j\neq l \quad \text{and} \quad \Omega_{\bbr_\tau}(b^l_{\tau}, e_l)^2 = \lambda_l^*,
		      \end{equation*}
		      recall \cref{eq:M_tau,eq:r_tau}.
		      %
		      Denote by $\tB_\tau \in M_{N \times |\ex|}(\bbZ)$ the matrix with columns $b^l_\tau$
		      for all $l \in \ex$. Write $\tB = \tB_{\id}$.
		\item For all $\tau \in \Xi_N$, the pair $(M_\tau, \tB_\tau)$ is a quantum seed for
		      $\Fract(R)$. The principal part of $\tB_\tau$ is skew-symmetrizable by the integers
		      $d_{\eta(k)}$ for $k \in \ex$.
		\item All such quantum seeds are mutation-equivalent to each other. More precisely, they are
		      linked by the following one-step mutations. Let $\tau, \tau' \in \Xi_N$ be such that
		      \begin{equation*}
			      \tau' = (\tau(k), \tau(k+1))\tau = \tau (k, k+1)
		      \end{equation*}
		      for some $k\in [1, N-1]$. If $\eta(\tau(k)) \neq \eta(\tau(k+1))$, then $M_{\tau'} = M_\tau$. Otherwise, if $\eta(\tau(k)) = \eta(\tau(k+1))$, then $M_{\tau'} = \mu_{k_\bullet}(M_\tau)$, where $k_\bullet = \tau_\bullet \tau(k)$.
		\item We have equality between the CGL extension $R$, the quantum cluster algebra and the
		      upper cluster algebra associated to $M$ and $\tB$:
		      \begin{equation*}
			      R = \mcA(M, \tB, \emptyset)_\bbK = \mcU(M, \tB, \emptyset)_\bbK.
		      \end{equation*}
		\item Finally, let $\binv$ be any subset of the frozen variables $\frz \defeq P(N)$. Then
		      \begin{equation*}
			      R[y_k\inv \mid k \in \binv] = \mcA(M, \tB, \binv)_{\bbK} = \mcU(M, \tB, \binv)_{\bbK}.
		      \end{equation*}
	\end{enumerate}
\end{theorem}

\begin{example}

	We now apply the main theorem to $R = \HeisUqn$\index{Heis@$\HeisUqn$}. We have $\ex =
		[1,4]$. Assume that there exists $\sqrt{q} \in \bbK$. Then the subgroup of
	$\bbK^\times$ generated by the elements of $\bbn$ only contains half-integer powers of
	$q$. Since $q$ is not a root of unity, none of these have order 2. Since $\lambda_l^* =
		q^2$ for all $l \in [1, 6]$ it suffices to pick $d_{\eta(j)} = 1$ for all $j \in [1,
			6]$. Let us now calculate the mutation matrix $\tB = \tB_{\id}$.

	From \cref{table:sigma_delta_heisenberg} we obtain
	\begin{equation*}
		\bbl = \begin{pmatrix*}[l]
			1     & q     & q\inv & q      & q\inv  & q^{-2} \\
			q\inv & 1     & q     & q\inv  & q^{-2} & q\inv  \\
			q     & q\inv & 1     & q^{-2} & q\inv  & q      \\
			q\inv & q     & q^2   & 1      & q      & q\inv  \\
			q     & q^2   & q     & q\inv  & 1      & q      \\
			q^2   & q     & q\inv & q      & q\inv  & 1
		\end{pmatrix*}.
	\end{equation*}
	Thus,
	\begin{equation*}
		\boldsymbol{\alpha} = \begin{pmatrix*}[l]
			1     & q     & q\inv & 1      & 1      & q^{-2} \\
			q\inv & 1     & 1     & q\inv  & q^{-2} & q^{-2} \\
			q     & q\inv & q     & q^{-1} & q^{-2} & 1      \\
			q\inv & q     & q     & q      & q^2    & 1      \\
			q     & q^2   & q^2   & q      & q^2    & q^2    \\
			q^2   & q     & q     & q^2    & 1      & q^2
		\end{pmatrix*}
		\quad \text{and}\quad \bbq = \begin{pmatrix*}[l]
			1     & q   & q\inv & 1      & 1      & q^{-2} \\
			q\inv & 1   & 1     & q\inv  & q^{-2} & q^{-2} \\
			q     & 1   & 1     & q^{-1} & q^{-2} & q^{-2} \\
			1     & q   & q     & 1      & 1      & q^{-2} \\
			1     & q^2 & q^2   & 1      & 1      & 1      \\
			q^2   & q^2 & q^2   & q^2    & 1      & 1
		\end{pmatrix*}.
	\end{equation*}
	To find $b^1 \in \bbZ^6$ we need to solve the system of equations\footnote{Technically we also have the additional condition $\chi_{M(b^1)} = 1$, but it turns out to be superfluous in this case.} given by
	\begin{equation*}
		\Omega_\bbr(b^1, e_j) = 1, \quad \forall j \in [2, 6] \quad \text{and}\quad \Omega_\bbr(b^1, e_1)^2 = q^2.
	\end{equation*}
	Since $\bbq = \bbr^{\cdot 2}$, and $q$ is not a root of unity, this is equivalent to solving
	\begin{equation*}
		\Omega_\bbq(b^1, e_j) = 1, \quad \forall j \in [2, 6] \quad \text{and}\quad \Omega_\bbq(b^1, e_1) = q^2.
	\end{equation*}
	%
	Writing $\bbq = (q^{\Lambda_{ij}})$ with
	\begin{equation*}
		\Lambda = \begin{pmatrix*}[r]
			0  & 1 & -1 & 0  & 0  & -2 \\
			-1 & 0 & 0  & -1 & -2 & -2 \\
			1  & 0 & 0  & -1 & -2 & -2 \\
			0  & 1 & 1  & 0  & 0  & -2 \\
			0  & 2 & 2  & 0  & 0  & 0  \\
			2  & 2 & 2  & 2  & 0  & 0
		\end{pmatrix*},
	\end{equation*}
	the above equations reduce to the linear system of equations
	\begin{equation*}
		\Lambda^T b^1 = (2,0,0,0,0,0)^T.
	\end{equation*}
	Since $\bbq$ is multiplicatively skew-symmetric, $\Lambda$ is skew-symmetric and hence $\Lambda^T = - \Lambda$. One obtains an analogous linear system for the other columns. Together, this can be written compactly as
	\begin{equation*}
		\tB = -\Lambda{\inv}D_{\lambda^*},
	\end{equation*}
	where
	\begin{equation*}
		D_{\lambda^*} =
		\begin{pmatrix}
			2 & 0 & 0 & 0 \\
			0 & 2 & 0 & 0 \\
			0 & 0 & 2 & 0 \\
			0 & 0 & 0 & 2 \\
			0 & 0 & 0 & 0 \\
			0 & 0 & 0 & 0
		\end{pmatrix}.
	\end{equation*}
	Solving the linear system gives
	\begin{equation*}
		\tB = \begin{pmatrix*}[r]
			0  & 1  & -1 & 0  \\
			-1 & 0  & 0  & 1  \\
			1  & 0  & 0  & -1 \\
			0  & -1 & 1  & 0  \\
			0  & 1  & 0  & -1 \\
			0  & 0  & 0  & 1
		\end{pmatrix*},
	\end{equation*}
	%
	which corresponds to the ice quiver
	\begin{equation*}
		\tQ =
		\begin{tikzcd}
			1 \rar & 2 \dar & \lar \boxed{5} \\
			3 \uar & 4 \lar \urar & \lar \boxed{6}
		\end{tikzcd}
		.
	\end{equation*}

	Let us now compute $\tB_{\tau}$ where $\tau = [2,3,4,1,5,6] \in \Xi_6$. Then
	$\tau_{\bullet} = [4, 2, 1, 3, 5, 6]$ and $\tau_\bullet\tau = [2, 1, 3, 4, 5, 6]$. The
	procedure to compute $\tB_{\tau}$ is analogous to the one above. We start with the
	matrix $\bbl_\tau = \tau\inv \bbl \tau$. From $\bbl_\tau$ we construct the matrix
	$\wh{\bbq}_\tau$ using the predecessor function $p_\tau$ as in \cref{eq:q_from_lambda}.
	Explicitly,
	\begin{equation}\label{eq:heisenberg_q_hat_tau}
		\bbl_\tau = \begin{pmatrix*}[l]
			1     & q     & q\inv  & q\inv & q^{-2} & q\inv  \\
			q\inv & 1     & q^{-2} & q     & q\inv  & q      \\
			q     & q^{2} & 1      & q\inv & q      & q\inv  \\
			q     & q\inv & q      & 1     & q\inv  & q^{-2} \\
			q^{2} & q     & q\inv  & q     & 1      & q      \\
			q     & q\inv & q      & q^{2} & q\inv  & 1
		\end{pmatrix*}
		, \quad
		\wh{\bbq}_\tau = \begin{pmatrix*}[l]
			1     & q     & 1      & q\inv & q^{-2} & q^{-2} \\
			q\inv & 1     & q^{-2} & q\inv & q^{-2} & 1      \\
			1     & q^{2} & 1      & 1     & 1      & 1      \\
			q     & q     & 1      & 1     & 1      & q^{-2} \\
			q^{2} & q^{2} & 1      & 1     & 1      & 1      \\
			q^{2} & 1     & 1      & q^{2} & 1      & 1
		\end{pmatrix*}.
	\end{equation}
	%
	Then, recalling \cref{eq:r_tau}, we find $\bbq_\tau = (\tau_\bullet \tau)
		\wh{\bbq}_\tau (\tau_\bullet \tau)\inv$, from which we obtain the matrix $\Lambda_\tau
		\in M_6(\bbZ)$:
	\begin{equation}\label{eq:heisenberg_q_tau}
		\bbq_\tau = \begin{pmatrix*}[l]
			1     & {q^{-1}} & {q^{-2}} & {q^{-1}} & {q^{-2}} & 1        \\
			q     & 1        & 1        & {q^{-1}} & {q^{-2}} & {q^{-2}} \\
			q^{2} & 1        & 1        & 1        & 1        & 1        \\
			q     & q        & 1        & 1        & 1        & {q^{-2}} \\
			q^{2} & q^{2}    & 1        & 1        & 1        & 1        \\
			1     & q^{2}    & 1        & q^{2}    & 1        & 1
		\end{pmatrix*}
		,\quad
		\Lambda_\tau = \begin{pmatrix*}[r]
			0 & -1 & -2 & -1 & -2 & 0  \\
			1 & 0  & 0  & -1 & -2 & -2 \\
			2 & 0  & 0  & 0  & 0  & 0  \\
			1 & 1  & 0  & 0  & 0  & -2 \\
			2 & 2  & 0  & 0  & 0  & 0  \\
			0 & 2  & 0  & 2  & 0  & 0
		\end{pmatrix*}.
	\end{equation}
	Finally,
	\begin{align*}
		\tB_\tau = -\Lambda_\tau \inv D_{\lambda^*} = \begin{pmatrix*}[r]
			                                              0 & 0 & -1 & 0\\
			                                              0 & 0 & 1 & 0\\
			                                              1 & -1 & 0 & 1\\
			                                              0 & 0 & -1 & 0\\
			                                              0 & 1 & 0 & -1\\
			                                              0 & 0 & 0 & 1
		                                              \end{pmatrix*},
	\end{align*}
	%
	which corresponds to the ice quiver
	\begin{equation*}
		\tQ_{\tau} =
		\begin{tikzcd}
			1 & 2 \dlar & \boxed{5} \lar \\
			3 \uar \rar & 4 \urar & \boxed{6} \lar
		\end{tikzcd}
		.
	\end{equation*}
	%
	Note that the principal part of $\tQ_\tau$ is an orientation of the Dynkin diagram of
	type $D_4$. Recall also that the exchange graph for the quantum cluster algebra may be
	identified with the exchange of the classical cluster algebra in the uniparameter case.
	It follows that the quantum cluster algebra associated to $\HeisUqn$ is cluster-finite.
	Moreover, the seeds may be identified with tagged triangulations of a once-punctured
	square (cf. \cref{exmp:punctured_polygon1,thm:clusters_and_triangulations}). Only a
	small part of this exchange graph consists of the seeds are of the form $(M_\sigma,
		\tB_\sigma)$ for some $\sigma \in \Xi_6$. These are illustrated in
	\cref{fig:xi_6_graph}. An interesting question is whether the other seeds have any
	ring-theoretic meaning. Note that these other seeds are in some sense redundant.
	Indeed, the (extended) cluster variables from the seeds $(M_\sigma, \tB_\sigma)$
	already generate the whole algebra, as we will see later in (\cref{thm:intersections}
	(b)).

	We now take a closer look at the seed mutations. \Cref{thm:gy_main_result} (c) says
	that mutation will happen between adjacent permutations, i.e., ones which differ by an
	elementary transposition\index{elementary transposition}. Recall that an
	\emph{elementary transposition} is a transposition of the form $(i, i+1)$. We now
	decompose $\tau$ as a sequence of permutations in $\Xi_6$ each of which differs by an
	elementary transposition. Such decompositions will play an important role in the proof
	of \cref{thm:gy_main_result} (cf. \cref{lem:xi_n_characterization}). Write $\tau' =
		[2,3,1,4,5,6]$. Then $\tau = \tau(3,4)$. For $\tau'' = [2,1,3,4,5,6]$, we have $\tau''
		= \tau(2,3)$, and $\tau'' = \id (1,2)$. One can compute that $\tau'_{\bullet} =
			[3,2,1,4,5,6],\, \tau'_\bullet \tau' = [2,1,3,4,5,6]$ and
	\begin{equation*}
		\Lambda_{\tau'} = \begin{pmatrix*}[r]
			0 & -1 & 1 & -1 & -2 & 0\\
			1 & 0 & 0 & -1 & -2 & -2\\
			-1 & 0 & 0 & -1 & -2 & -2\\
			1 & 1 & 1 & 0 & 0 & -2\\
			2 & 2 & 2 & 0 & 0 & 0\\
			0 & 2 & 2 & 2 & 0 & 0
		\end{pmatrix*},
	\end{equation*}
	from which one obtains
	\begin{equation*}
		\tB_{\tau'}
		\begin{pmatrix*}[r]
			0 & -1 & 1 & 0\\
			1 & 0 & -1 & 1\\
			-1 & 1 & 0 & -1\\
			0 & -1 & 1 & 0\\
			0 & 1 & 0 & -1\\
			0 & 0 & 0 & 1
		\end{pmatrix*},
		\quad \tQ_{\tau'} =
		\begin{tikzcd}
			1 \dar & 2 \lar \dar & \boxed{5} \lar \\
			3 \urar & 4 \lar \urar & \boxed{6} \lar
		\end{tikzcd}
		.
	\end{equation*}
	%
	Because $\eta(1) \neq \eta(2)$, we do not obtain a mutation between $\tB$ and
	$\tB_{\tau''}$. Instead, $\tB = \tB_{\tau''}$. Now, since $\tau' = \tau''(2,3)$ and
	$\eta(\tau''(2)) = \eta(\tau''(3)) = 1$, \cref{thm:gy_main_result} (c) gives that
	$\tB_{\tau'} = \mu_{k_\bullet}(\tB_{\tau''}) = \mu_{k_\bullet}(\tB)$ where $k_\bullet =
		\tau''_\bullet(\tau''(2)) = \tau'_\bullet(\tau'(2)) = 1$. Indeed, the ice quiver
	$\tQ_{\tau'}$ is obtained from $\tQ$ by a mutation at vertex 1. In the same way, from
	$\tau = \tau'(3,4)$ and $\tau_\bullet(\tau(3)) = 3$, it follows that $\tB_\tau =
		\mu_{3}(\tB_{\tau'})$ which can again be verified most easily by looking at the
	corresponding ice quivers.

	To finish the example, we look at the sequences of homogeneous prime elements
	corresponding to the permutations $\tau$ and $\tau'$. First remark that $\tau$ and
	$\tau'$ are precisely the permutations from \cref{exmp:heisenberg_two_presentations}.
	There we had found
	\begin{equation}\label{eq:heisenber_almost_mutation}
		y'_{\tau, 3}y'_{\tau', 3} = q^2 y'_{\tau, 2}y'_{\tau, 4} - \frac{q}{(1-q^2)^2}y'_{\tau, 1},
	\end{equation}
	%
	where the primes indicate that the normalization of the generators and the
	normalization \cref{eq:normalization_y} has not been applied. The goal is now to
	compare this to the mutation statement
	\begin{align*}
		M_{\tau'}(e_3)
		 & = M_{\tau}(-e_3 + [b^3_{\tau}]_{+}) + M_\tau(-e_3 - [b^3_{\tau}]_{-}) \\
		 & = M_{\tau}(-e_3 + e_2) + M_{\tau}(-e_3 + e_1 + e_4).
	\end{align*}
	Recall that $\tau_\bullet\tau = [2,1,3,4,5,6] = (1,2)$ and \cref{eq:heisenberg_q_hat_tau,eq:heisenberg_q_tau}. Expanding the right-hand side gives
	\begin{align*}
		M_{\tau}(e_2 - e_3) + M_{\tau}(e_1 - e_3 + e_4)
		 & = \mcS_{\bbr_\tau}(e_2 - e_3)\oy_{\tau, 1}(\oy_{\tau, 3})\inv + \mcS_{\bbr_\tau}(e_1 -e_3 + e_4)\oy_{\tau, 2}(\oy_{\tau, 3})\inv \oy_{\tau, 4} \\
		 & = r_{\tau, 23}\oy_{\tau, 1}(\oy_{\tau, 3})\inv + r_{\tau, 13}r_{\tau, 14}\inv r_{\tau, 34}\oy_{\tau, 2}(\oy_{\tau, 3})\inv \oy_{\tau, 4}       \\
		 & = \oy_{\tau, 1}(\oy_{\tau, 3})\inv + q\inv q^{\frac{1}{2}} \oy_{\tau, 2}(\oy_{\tau, 3})\inv \oy_{\tau, 4}                                      \\
		 & = \wh{q}_{\tau, 31}(\oy_{\tau, 3})\inv\oy_{\tau, 1} + \wh{q}_{\tau, 32}q^{-\frac{1}{2}}(\oy_{\tau, 3})\inv \oy_{\tau, 2}\oy_{\tau, 4}          \\
		 & = (\oy_{\tau, 3})\inv\oy_{\tau, 1} + q^{\frac{3}{2}}(\oy_{\tau, 3})\inv \oy_{\tau, 2}\oy_{\tau, 4},
	\end{align*}
	and hence
	\begin{equation}\label{eq:heisenberg_real_mutation}
		\oy_{\tau, 3}\oy_{\tau',3} = \oy_{\tau, 1} + q^{\frac{3}{2}}\oy_{\tau, 2}\oy_{\tau, 4}.
	\end{equation}

	We now need to determine $\oy_{\tau, i}$ and $\oy_{\tau',i}$ for $i \in [1,4]$. From
	\cref{exmp:heisenberg_rescaling} we know that $\gamma_1 = 1 = \gamma_2, \gamma_3 = 1
		-q^{-2}$ and $\gamma_4 = -q^2$. Since $y'_{\tau, 1} = y'_{\tau',1} = y'_2$, it follows
	that $\oy_{\tau, 1} = \oy_{\tau',1} = \oy_2$. Now,
	\begin{equation*}
		y'_{\tau, 2} = y'_{\tau', 2} = E_1
	\end{equation*}
	gives
	\begin{equation*}
		\oy_{\tau, 2} = \oy_{\tau', 2} = y_{\tau, 2} = y_{\tau', 2} =  q^{\frac{1}{2}}(1-q^{-2})y'_{\tau, 2}.
	\end{equation*}
	Next we determine $\oy_{\tau, 3}$ and $\oy_{\tau', 3}$. Note that we need to use the predecessor functions $p_\tau$ and $p_{\tau'}$ to determine the normalization factors for $\oy_{\tau, 3}$ and $\oy_{\tau', 3}$. From
	\begin{equation*}
		y'_{\tau, 3} = y'_{\tau, 2}F_1 - \frac{1}{1-q^2},
	\end{equation*}
	it follows that
	\begin{equation*}
		y_{\tau, 3} = -q^2 (1-q^{-2})y'_{\tau, 3} = y_{\tau, 2}(-q^{\frac{3}{2}}F_1) - 1,
	\end{equation*}
	and
	\begin{equation*}
		\oy_{\tau, 3} = \nu_{\tau, 23}\inv y_{\tau, 3} = \nu_{34}\inv y_{\tau, 3} = q y_{\tau, 3} = -q^3(1-q^{-2})y'_{\tau, 3}.
	\end{equation*}
	On the other hand, from
	\begin{equation*}
		y'_{\tau', 3} = y'_{\tau', 2}E_2 - \frac{q}{q^2 - 1}E_{12},
	\end{equation*}
	we obtain
	\begin{equation*}
		y_{\tau', 3} = q^{\frac{1}{2}}(1-q^{-2})y'_{\tau', 3} = y_{\tau, 2}E_2 - q^{\frac{1}{2}} E_{12},
	\end{equation*}
	and
	\begin{equation*}
		\oy_{\tau', 3} = \nu_{\tau', 23}\inv y_{\tau', 3} = \nu_{31}\inv y_{\tau', 3} = q^{-\frac{1}{2}}y_{\tau', 3} = (1-q^{-2})y_{\tau',3}.
	\end{equation*}

	To see that we are on the right track, note that we should have $\oy_{\tau', 2} =
		M_{\tau'}(e_1)$. The latter is determined by the mutation in direction 1 of $M$, as we
	already saw. We indeed find
	\begin{align*}
		M_{\tau'}(e_1)
		 & = M(-e_1 + e_3) + M(-e_1 + e_2)                                                                                                        \\
		 & = \mcS_{\bbr}(-e_1 + e_3)(\oy_1)\inv \oy_3 + \mcS_{\bbr}(-e_1 + e_2)(\oy_1)\inv \oy_2                                                  \\
		 & = r_{13} E_2\inv q^{\frac{1}{2}}(E_2 q^{\frac{1}{2}}(1-q^{-2})E_1 - q^{\frac{1}{2}}E_{12}) + r_{12} E_2\inv E_{12}                     \\
		 & = q^{-\frac{1}{2}} q^{\frac{1}{2}} E_2\inv (E_2 q^{\frac{1}{2}}(1-q^{-2})E_1 - q^{\frac{1}{2}}E_{12}) + q^{\frac{1}{2}} E_2\inv E_{12} \\
		 & = q^{\frac{1}{2}}(1-q^{-2})E_1                                                                                                         \\
		 & = \oy_{\tau', 2}.
	\end{align*}

	It remains to determine $\oy_{\tau, 4}$.
	\begin{equation*}
		y'_{\tau, 4} = y'_{\tau,3}E_2 -\frac{1}{1-q^2}E_{12}F_1,
	\end{equation*}
	gives
	\begin{equation*}
		y_{\tau, 4} = -q^2 (1-q^{-2}) y'_{\tau, 4} = y_{\tau, 3} E_2 - q^{\frac{1}{2}}E_{12}(-q^{\frac{3}{2}}F_1),
	\end{equation*}
	and
	\begin{equation*}
		\oy_{\tau, 4} = \nu_{\tau, 23}\inv \nu_{\tau, 24}\inv \nu_{\tau, 34}\inv y_{\tau, 4} = \nu_{34}\inv \nu_{31}\inv \nu_{41}\inv y_{\tau, 4} = q q^{-\frac{1}{2}}q^{\frac{1}{2}} y_{\tau, 4} = qy_{\tau, 4} = -q^3(1-q^{-2})y'_{\tau, 4}.
	\end{equation*}

	We can now compare the cluster mutation statement to
	\cref{eq:heisenber_almost_mutation}. \Cref{eq:heisenberg_real_mutation} gives
	\begin{align*}
		y'_{\tau, 3}y'_{\tau', 3}
		 & = -q^{-3}(1-q^{-2})\inv \oy_{\tau, 3} (1-q^{-2})\inv \oy_{\tau', 3}                                         \\
		 & = -q^{-3}(1-q^{-2})^{-2}\bigl( \oy_{\tau, 1} + q^{\frac{3}{2}}\oy_{\tau, 2}\oy_{\tau, 4}             \bigr) \\
		 & = -q^{-3}(1-q^{-2})^{-2}\bigl(y'_{\tau, 1} + q^{2}(1-q^{-2})y'_{\tau, 2}(-q^3)(1-q^{-2})y'_{\tau, 4}\bigr)  \\
		 & = -q (1-q^2)^{-2} y'_{\tau, 1} + q^2 y'_{\tau, 2}y'_{\tau, 4},
	\end{align*}
	%
	which is precisely \cref{eq:heisenber_almost_mutation}. We see that the normalization
	had the desired effect.

\end{example}

\section{Normalizing the generators}\label{sec:normalizing_generators}

The goal of this chapter is to show that \cref{cond:normalization_generators} had the
desired effect. This is by far the most technical part of the proof of
\cref{thm:gy_main_result}. We begin by characterizing the subset $\Xi_N \subseteq S_N$
differently. From this we obtain a description of the $\eta$-functions of the
presentations corresponding to the different permutations $\tau \in \Xi_N$. Finally, we
derive two important results which form the backbone of the proof of
\cref{thm:gy_main_result}. The first, \cref{prop:y_tau_is_y_bracket}, provides an
alternate description of the cluster variables $\oy_{\tau, k}$ in terms of the
homogeneous prime elements of the subalgebras $R_{[j, k]}$. The second,
\cref{prop:mutation_adjacent_permutations}, essentially proves mutation between
adjacent presentations.

\subsection{The subset \texorpdfstring{$\Xi_N \subseteq S_N$}{Xi\_ N of S\_ N}}

We begin by studying more closely the subset $\Xi_N \subseteq S_N$. Recall that an
element $\tau \in \Xi_N$ has the property that $\tau([1, j])$ is an interval for all $j
	\in [1, N]$. In particular, this means that $\tau([1, N-1]) = [1, N-1]$ or $\tau([1,
		N-1]) = [2, N]$. Reformulating this in terms of an element $\tau' \in \Xi_{N-1}$ we
obtain the following lemma.
\begin{lemma}
	For each $\tau \in \Xi_N$, there exists $\tau' \in \Xi_{N-1}$ such that either
	\begin{equation*}
		\tau(i) = \tau'(i), \text{ for all } i \in [1, N-1] \quad \text{and} \quad \tau(N) = N
	\end{equation*}
	or
	\begin{equation*}
		\tau(i) = \tau'(i) + 1, \text{ for all } i \in [1, N-1] \quad \text{and} \quad \tau(N) = 1.
	\end{equation*}
	%
	Conversely, any element $\tau' \in \Xi_{N-1}$ defines an element $\tau \in \Xi_N$ this
	way.
\end{lemma}

From this we obtain an alternative description of $\Xi_N$. Namely, for $k\in [1, N]$
and $k \leq j_k \leq \cdots \leq j_1 \leq N$, define
\begin{equation*}
	\tau_{(j_k, \dots, j_1)} \defeq (k,k+1, \cdots, j_k)\cdots (2,3, \cdots, j_2)(1,2,\cdots, j_1)\in S_N,
\end{equation*}
\index{tau jk j one@$\tau_{(j_k, \dots, j_1)}$}%%
%
where the right-hand side is a composition of cycles.
\begin{lemma}\label{lem:xi_n_characterization}

	We have the following characterization for $\Xi_N$:
	\begin{equation*}
		\Xi_N = \{\tau_{(j_k, \dots, j_1)} \mid k \leq j_k \leq \cdots \leq j_1 \leq N,\, k\in [1, N]\}.
	\end{equation*}
	%
	Moreover, for each $\tau \in \Xi_N$, there exists a sequence $\tau_0 = \id, \tau_1,
		\dots, \tau_n = \tau$ in $\Xi_N$ and $k_i\in[1, N-1]$ for $i\in[1,n]$, such that for
	all $l \in [1, n]$,
	\begin{equation*}
		\tau_l = (\tau_{l-1}(k_l), \tau_{l-1}(k_l + 1))\tau_{l-1} = \tau_{l-1}(k_l, k_l + 1)
	\end{equation*}
	%
	and $\tau_{l-1}(k_l) < \tau_{l-1}(k_l + 1)$.
\end{lemma}
\begin{proof}
	We first show that each element of $\Xi_N$ can be written as an element $\tau_{(j_k, \dots, j_1)}$.

	By induction on $N$. For $N = 1$, we have $\Xi_N = \{\id\}$, and $\tau_{(1)} = \id$.
	Now assume the lemma holds for $\Xi_{N-1}$, and take $\tau \in \Xi_N$. There are two
	cases
	\begin{enumerate}
		\item There exists $\tau' \in \Xi_{N-1}$ such that $\tau(i) = \tau'(i)$ for all $i\in [1,
				      N-1]$ and $\tau(N) = N$. Write $\tau' = \tau_{(j_k, \dots, j_1)} \in S_{N-1}$ using the
		      induction hypothesis. Then $\tau = \tau_{(j_k, \dots, j_1)}$ but now viewed as an
		      element of $S_N$ (since $\tau$ fixes $N$ and equals $\tau'$ on $[1, N-1]$).
		\item Otherwise, there exists $\tau' \in \Xi_{N-1}$ such that $\tau(i) = \tau'(i)$ for all
		      $i\in [1, N-1]$ and $\tau(N) = 1$. The induction hypothesis gives that we can write
		      $\tau' = \tau_{(j'_k, \dots, j'_1)}$ for some $k \in [1, N - 1]$ and $k \leq j'_k \leq
			      \cdots \leq j'_1 \leq N - 1$. Write $j_{i+1} = j'_i + 1$ for $1 \leq i \leq k$ and
		      define $j_1 = N$. Then
		      \begin{equation*}
			      \tau = \tau_{(j_k, \dots, j_1)} = (k+1, \cdots, j'_k + 1) \cdots (2, 3, \cdots ,j'_1 + 1)(1,2, \cdots, N) \in S_N.
		      \end{equation*}
		      Indeed, $\tau_{(j_k, \dots, j_1)}(N) = 1$, and for $i \in [1, N-1]$,
		      \begin{align*}
			      \tau_{(j_k, \dots, j_1)}(i)
			       & = (k+1, \cdots, j'_k + 1) \cdots (2, 3, \cdots, j'_1 + 1)(1,2, \cdots, N) i \\
			       & = (k+1, \cdots, j'_k + 1) \cdots (2, 3, \cdots, j'_1 + 1) (i+1)             \\
			       & = \tau'(i) + 1                                                              \\
			       & = \tau(i).
		      \end{align*}
	\end{enumerate}

	We prove the other inclusion, and the final statement together. More precisely, take $k
		\in [1, N]$ and $k \leq j_k \leq \dotsb \leq j_1 \leq N$. We will show that
	$\tau_{(j_k, \dotsc, j_1)} \in \Xi_N$, and that it can be decomposed as in the
	statement of the lemma.

	We can decompose the cycle $(1,2,\dots, j_1)$ as $(1, j_1)(1, j_1 - 1)\cdots (1, 2)$.
	For each $l \in [1, j_1 - 1]$, write
	\begin{equation*}
		\tau_l = (1,2,\cdots, l+1) = (1, l+1) (1, l) \cdots (1, 2).
	\end{equation*}
	Then
	\begin{equation*}
		\tau_l = (1, l+1)\tau_{l-1} = (\tau_{l-1}(l), \tau_{l-1}(l+1)) = \tau_{l-1}(l, l+1),
	\end{equation*}
	%
	and $\tau_l \in \Xi_N$, because $\tau_l ([1, i]) = [2, i+1]$ for $i \in [1, l]$ and
	$\tau_l ([1, i]) = [1, i]$ for $i \in [l+1, N]$.

	We now look at what happens when we add another cycle, $(2,3,\dots, j_2)$. Because we
	can apply the same type of decomposition in transpositions to the cycle $(2,3,\dots,
		j_2)$, it remains to show that $\tau_{(j_2, j_1)} \in \Xi_N$. For $i \in [1, j_2 - 2]$,
	we have
	\begin{equation*}
		\tau_{(j_2, j_1)}([1, i]) = (2,3, \dots, j_2)(1,2,\dots,j_1)[1, i]= (2,3,\dots,j_2)[2, i+1] = [3,\dots,i+2].
	\end{equation*}
	For $i \in [j_2 - 1, j_1 -1]$, we have
	\begin{equation*}
		\tau_{(j_2,j_1)}([1, i]) = (2,3,\dots, j_2)(1,2, \dots, j_1)[1, i] = (2,3,\dots,j_2)[2,i+1] = [2, i+1],
	\end{equation*}
	and finally, for $i \in [j_1, N]$ we have $\tau_{(j_2,j_1)}[1,i] = [1, i]$, which shows that $\tau_{(j_2, j_1)} \in \Xi_N$. The statement now follows by proceeding like this inductively.
\end{proof}

To illustrate the induction step in the proof of the previous lemma, we look at a small
example.
\begin{example}

	Suppose $N = 4$ and $\tau = [3,4,2,1] \in \Xi_4$. Then, since $\tau(N) = \tau(4) = 1$,
	we have $\tau' = [2,3,1] \in \Xi_{3}$. Similarly, we find $\tau'' = [1,2] \in \Xi_2$
	and $\tau''' = [1] \in \Xi_1$. The base case gives $\tau''' = \tau_{(1)} = (1) = \id
		\in S_1$. Then, since $\tau''(2) = 2$, the induction step gives $\tau'' = \tau_{(1)}$
	as well, but now viewed as an element of $S_2$. Now, because $\tau'(3) = 1$, the
	induction step now tells us that $\tau' = \tau_{(2,3)} = (2)(1,2,3) = (1,2,3) \in S_3$,
	which is indeed the case. Finally, as $\tau(4) = 1$ we must have
	\begin{equation*}
		\tau = \tau_{(3,4,4)} = (3)(2,3,4)(1,2,3,4) = (2,3,4)(1,2,3,4) \in S_4.
	\end{equation*}

	Note that we also have $\tau = \tau_{(4,4)}$ which shows that the representation is not
	unique.
\end{example}

The decomposition of \cref{lem:xi_n_characterization} has the following important
consequence, which we alluded to many times already.
\begin{proposition}\label{prop:eta_invariance}
	Let $R$ be a symmetric CGL extension of length $N$ and $\tau \in \Xi_N$.
	\begin{enumerate}[(a)]
		\item If $\eta : [1, N] \to \bbZ$ is a function satisfying the conditions of
		      \cref{thm:homogeneous_primes} for the original CGL extension presentation of $R$, then
		      \begin{equation*}
			      \eta_\tau = \eta \tau : [1, N] \to \bbZ
		      \end{equation*}
		      %
		      satisfies the conditions of \cref{thm:homogeneous_primes} for the presentation of $R$
		      corresponding to $\tau$.

		\item Furthermore, for all $1 \leq j \leq k \leq N$, the function $\eta_{[j, k]} \colon [1,
				      k-j+1] \to \bbZ$ given by
		      \begin{equation*}
			      \eta_{[j,k]}(l) = \eta(j+l-1)
		      \end{equation*}
		      %
		      satisfies the conditions of \cref{thm:homogeneous_primes} for the symmetric CGL
		      extension $R_{[j,k]}$.
	\end{enumerate}
\end{proposition}
\begin{proof}

	The first part follows from \cref{lem:xi_n_characterization}, by applying
	\cref{thm:y_prime_swapped_cgl} inductively. Indeed, assume that $\eta_{\tau_l}$
	satisfies the conditions of \cref{thm:homogeneous_primes} for the presentation
	corresponding to $\tau_l$. Then, because $\tau_{l+1} = \tau_l (k_{l+1}, k_{l+1} + 1)$,
	\cref{thm:y_prime_swapped_cgl} applied to the CGL presentations corresponding to
	$\tau_{l}$ and $\tau_{l+1}$ gives that we may take $\eta' = \eta_{\tau_l}(k_{l+1},
		k_{l+1}+1) = \eta_{\tau_{l+1}}$ for the $\eta$-function of the presentation
	corresponding to $\tau_{l+1}$.

	The second statement follows from the first by looking at
	\begin{equation*}
		\tau = [j, j+1, \dots, k, j-1,j-2, \dots , 1, k+1, k+2, \dots, N] \in \Xi_N.
	\end{equation*}
	%
	Due to the first part, we can take $\eta_\tau$ for the $\eta$-function of
	\cref{thm:homogeneous_primes} applied to the presentation corresponding to $\tau$.
	Furthermore, \cref{thm:homogeneous_primes} implies that the (restriction of the) same
	function can be used when looking at the subalgebra generated by the first $i$
	generators $x_{\tau(1)}, \dots, x_{\tau(i)}$ for all $i \in [1, N]$. Finally, remark
	that the subalgebra of $R$ generated by $\tau(1), \dots, \tau(k - j + 1)$ equals
	$R_{[j, k]}$, and that $\tau(l) = j + l - 1$ for all $l \in [1, k- j + 1]$.
\end{proof}

\subsection{An alternative description of the cluster variables}

Using the results from the previous subsection, we can now prove that all the cluster
variables coming from the seeds indexed by $\tau \in \Xi_N$ are actually obtained by
considering the cluster variables coming from the subalgebras $R_{[j,k]}$ of the
original CGL extension presentation. This result will be used in
\cref{prop:mutation_adjacent_permutations}, and later on in the proof of
\cref{thm:gy_main_result}.

\begin{lemma}\label{lem:y_tauk_y_brackets}
	Let $R$ be a symmetric CGL extension of length $N$. Take $\tau \in \Xi_N$ and $k \in [1, N]$.
	\begin{itemize}
		\item If $\tau(k) \geq \tau(1)$, then $y_{\tau,k}$ is a scalar multiple of $y_{[p^m(\tau(k)),
							      \tau(k)]}$, where
		      \begin{equation*}
			      m \defeq \max\{n \in \bbZ_{\geq 0} \mid p^n(\tau(k)) \in \tau([1,k])\}.
		      \end{equation*}
		\item If $\tau(k) \leq \tau(1)$, then $y_{\tau,k}$ is a scalar multiple of $y_{[\tau(k),s^m(
							      \tau(k))]}$, where
		      \begin{equation*}
			      m \defeq \max\{n \in \bbZ_{\geq 0} \mid s^n(\tau(k)) \in \tau([1,k])\}.
		      \end{equation*}
	\end{itemize}
	%
	In both cases the predecessor and successor functions are with respect to the original
	CGL extension presentation of $R$.
\end{lemma}
\begin{proof}

	For $k \in [1, N]$, denote by $R_{\tau, k}$, the subalgebra generated by $x_{\tau(1)},
		\dots, x_{\tau(k)}$. Let us first tackle the case where $\tau(k) \leq \tau(1)$. Because
	$\tau \in \Xi_N$, we have either $\tau(k) \geq \tau(j)$ for all $j\in [1, k - 1]$ or
	$\tau(k) \leq \tau(j)$ for all $j \in [1, k-1]$. The fact that $\tau(k) \leq \tau(1)$
	forces $\tau(k) \leq \tau(j)$ for all $j \in [1, k-1]$. We can hence write
	\begin{equation*}
		\tau([1, k]) = [\tau(k), \tau(i)] \quad \text{for some } i \in [1, k-1],
	\end{equation*}
	from which it follows that $R_{\tau, k} = R_{[\tau(k), \tau(i)]}$ and $R_{\tau, k-1} = R_{[\tau(k) + 1,\tau(i)]}$.
	%
	By assumption, we have $\tau(k) \leq s^m(\tau(k)) \leq \tau(i)$ and $s (s^m(\tau(k))) >
		\tau(i)$. The element $y_{[\tau(k), s^m(\tau(k))]}$ is a homogeneous prime element of
	$R_{[\tau(k), s^m(\tau(k))]}$ by assumption. \Cref{thm:homogeneous_primes} applied to
	this subalgebra shows that $y_{[\tau(k), s^m(\tau(k))]}$ must be a scalar multiple of
	one of the $y$-elements for $R_{[\tau(k), s^m(\tau(k))]}$, and hence also a homogeneous
	prime element of $R_{[\tau(k), \tau(i)]} = R_{\tau, k}$, by
	\cref{prop:eta_invariance,thm:homogeneous_primes} as $s(s^m(\tau(k))) > \tau(i)$.
	Because its leading term contains $x_{\tau(k)}$ by \cref{thm:y_square_brackets}, it
	does not belong to $R_{[\tau(k) + 1, \tau(i)]} = R_{\tau, k-1}$. But then
	\cref{thm:homogeneous_primes} implies that it must be a scalar multiple of $y_{\tau,
				k}$ as a homogeneous prime element of $R_{\tau, k}$ which does not lie in $R_{\tau,
				k-1}$.

	The other case, where $\tau(k) \geq \tau(1)$, follows by a symmetry argument. Namely,
	consider $\sigma \in \Xi_N$ given by reversing the order, i.e., $\sigma(i) = N- i + 1$
	for all $i \in [1, N]$. By \cref{prop:eta_invariance} we can take $\eta \sigma$ for the
	$\eta$-function with the presentation of $R$ corresponding to $\sigma$. Then note that
	$p_\sigma (i) = \sigma (s(\sigma(i)))$ and $s_\sigma (i) = \sigma(p(\sigma(i)))$ for
	all $i\in [1, n]$, where we define $\sigma(+\infty) = -\infty$ and $\sigma(-\infty) =
		+\infty$. Indeed,
	\begin{align*}
		\sigma(s(\sigma(i))) & = \sigma\left(\min \{k \in [i+1, N]\mid \eta(k) = \eta(\sigma(i))\}\right) \\
		                     & = \max\{k \in [1, i-1] \mid \eta(\sigma(k)) = \eta(\sigma(i))\}            \\
		                     & = p_\sigma(i).
	\end{align*}
	%
	The result is that we can apply \cref{thm:homogeneous_primes} ``in reverse'', which
	allows us to use an analogous argument to the first case.
\end{proof}

In the setting of \cref{thm:gy_main_result} we can improve this result. We first prove
a small lemma which we will need in the inductive step.
\begin{lemma}\label{lem:symmetrization_of_sum}

	Let $\bbr \in M_N(\bbK^\times)$ be a multiplicatively skew-symmetric matrix. Then, for
	all $j \in [2, N]$ and $f = m_1 e_1 + \dots + m_j e_j, g = m_{j+1} e_{j+1} + \dots +
		m_{N} e_N \in \bbZ^N$,
	\begin{equation*}
		\mcS_\bbr(f+g) = \Omega_{\bbr}(f,g)\inv \mcS_{\bbr}(f)\mcS_{\bbr}(g).
	\end{equation*}
\end{lemma}
\begin{proof}
	This is a straightforward calculation from the definitions.
	\begin{align*}
		\mcS_{\bbr}(f+g)
		 & = \prod_{k < l}r_{kl}^{-m_k m_l}                                                                                 \\
		 & = \prod_{k < l \leq j}r_{kl}^{-m_k m_l} \prod_{k \leq j < l}r_{kl}^{-m_k m_l} \prod_{j < k < l}r_{kl}^{-m_k m_l} \\
		 & = \prod_{k < l \leq j}r_{kl}^{-f_k f_l} \prod_{k \leq j < l}r_{kl}^{-f_k g_l} \prod_{j < k < l}r_{kl}^{-g_k g_l} \\
		 & = \mcS_{\bbr}(f) \prod_{k \leq j < l}r_{kl}^{-f_k g_l} \mcS_{\bbr}(g)                                            \\
		 & = \mcS_{\bbr}(f) \prod_{k, l}r_{kl}^{-f_k g_l} \mcS_{\bbr}(g)                                                    \\
		 & = \Omega_{\bbr}(f,g)\inv \mcS_{\bbr}(f) \mcS_{\bbr}(g).
	\end{align*}
\end{proof}
\begin{proposition}\label{prop:y_tau_is_y_bracket}
	Assume the setting of \cref{thm:gy_main_result}. Let $\tau \in \Xi_N$ and $k \in [1, N]$. Write, for $i \in [1, N]$ and $m \in \bbZ_{\geq 0}$ such that $s^m(i) \neq +\infty$,
	\begin{equation*}
		\oy_{[i, s^m(i)]} \defeq \mcS_{\bbn}(e_{[i, s^m(i)]})y_{[i, s^m(i)]},
	\end{equation*}
	%
	as in \cref{eq:normalization_y}. Thus, the normalization happens in the subalgebra
	$R_{[i, s^m(i)]}$. Then,
	\begin{itemize}
		\item If $\tau(k) \geq \tau(1)$, then $\oy_{\tau,k} = \oy_{[p^m(\tau(k)), \tau(k)]}$, where
		      \begin{equation*}
			      m \defeq \max\{n \in \bbZ_{\geq 0} \mid p^n(\tau(k)) \in \tau([1,k])\}.
		      \end{equation*}
		\item If $\tau(k) \leq \tau(1)$, then $\oy_{\tau,k} = \oy_{[\tau(k),s^m( \tau(k))]}$, where
		      \begin{equation*}
			      m \defeq \max\{n \in \bbZ_{\geq 0} \mid s^n(\tau(k)) \in \tau([1,k])\}.
		      \end{equation*}
	\end{itemize}
	In both cases the predecessor and successor functions are with respect to the original
	CGL extension presentation of $R$.
\end{proposition}
\begin{proof}
	We prove the proposition by induction on $k$. Because $\tau$ does not necessarily preserve the ordering, we need to do induction on both cases at the same time. If $k=1$, then $\oy_{\tau, 1} = y_{\tau, 1} = x_{\tau(1)} = \oy_{[\tau(1), \tau(1)]}$, so both cases are fine. Assume now that $k > 1$, and that $\tau(k) < \tau(1)$. The other case is analogous.

	By the previous lemma, $\oy_{\tau, k} = \xi \oy_{[\tau(k), s^m(\tau(k))]}$ for some
	$\xi \in \bbK^\times$. It is hence sufficient to prove that the leading terms are
	equal. As in the proof of the previous lemma, we find from $\tau(k) < \tau(1)$ that
	$\tau([1, k]) = [\tau(k), \tau(i)]$ for some $i \in [1, k]$. Thus, $R_{[\tau(k),
						\tau(i)]} = R_{\tau, k}$ and $R_{\tau, k-1} = R_{[\tau(k) + 1, \tau(i)]}$.

	In what follows, all leading terms will be computed with respect to the standard
	presentation of $R_{[\tau(k), \tau(i)]}$ where the generators are adjoined in the order
	$x_{\tau(k)}, x_{\tau(k) + 1}, \dots, x_{\tau(i)}$. By
	\cref{thm:homogeneous_primes,prop:eta_invariance},
	\begin{equation*}
		y_{\tau, k} = y_{\tau, p_{\tau}(k)}x_{\tau(k)} - c_{\tau, k-1}
	\end{equation*}
	%
	for some $c_{\tau, k-1} \in R_{\tau, k-1}$, where, like before, $p_\tau$ is the
	predecessor function corresponding to $\eta_\tau = \eta \tau \colon [1, N] \to \bbZ$.
	If $p_\tau(k) = -\infty$, then $\oy_{\tau, k} = x_{\tau(k)} = \oy_{[\tau(k),
					s^m(\tau(k))]}$, because $m = 0$ in this case. Indeed, if $m>0$, then $s(\tau(k)) =
		\tau(j)$ for some $j \in [1, k-1]$. Hence, $\eta_\tau(j) = \eta(\tau(j)) =
		\eta(\tau(k))$, which implies $p_\tau(k) \geq j$, a contradiction with $p_\tau(k) =
		-\infty$.

	We now apply induction on $p_\tau(k)$. If $\tau(p_\tau(k)) \leq \tau(1)$, then
	$\tau([1, p_\tau(k)]) = [\tau(p_\tau(k)), \tau(i')]$ for some $i' \in [1, p_\tau(k)]$
	by the same reasoning as we used to show that $\tau([1, k]) = [\tau(k), \tau(1)]$. We
	now claim that $\tau(p_\tau(k)) = s(\tau(k))$. First note that from $\eta_\tau (k) =
		\eta_\tau(p_{\tau}(k))$ we get
	\begin{equation*}
		\eta(\tau(p_\tau(k))) = \eta(\tau(k)) = \eta(s(\tau(k))),
	\end{equation*}
	%
	which shows that they belong to the same level set. Since $p_\tau(k) \in [1, k-1]$, we
	find that $\tau(p_\tau(k)) > \tau(k)$. Now, take $\tau(j) \in [\tau(k) + 1,
			\tau(p_\tau(k))]$ such that $\eta(\tau(j)) = \eta(\tau(k))$. We need to show that $j =
		p_\tau(k)$. By definition of $p_\tau(k)$ we have $j \notin [p_\tau(k) + 1, k-1]$. Since
	$\tau([1, p_\tau(k)]) = [\tau(p_\tau(k)), \tau(i')]$, we also have $j \not [1,
			p_\tau(k) - 1]$. If $j = p_\tau(k)$, then we are done. If not, then $j > k$, and hence
	$\tau(j) \notin [\tau(k), \tau(i)]$. By assumption, $\tau(j) \geq \tau(k) + 1$, so we
	must have
	\begin{equation*}
		\tau(j) > \tau(i) \geq \tau(1) \geq \tau(p_\tau(k)),
	\end{equation*}
	a contradiction to $\tau(j) \in [\tau(k) + 1, \tau(p_\tau(k))]$. So, the claim holds, and we must have
	\begin{equation*}
		\max\{n \in \bbZ_{\geq 0} \mid s^n(\tau(p_\tau(k))) \in \tau([1, p\tau(k)])\} = m-1.
	\end{equation*}
	%
	Since $p_\tau(k) < k$, we can apply the induction hypothesis to conclude that
	$\oy_{\tau, p_\tau(k)} = \oy_{[s(\tau(k)), s^m(\tau(k))]}$.

	If $\tau(p_\tau(k)) \geq \tau(1)$, then we claim that $\tau(p_\tau(k)) = s^m(\tau(k))$,
	which will then also imply $\oy_{\tau, p_\tau(k)} = \oy_{[s(\tau(k)), s^m(\tau(k))]}$
	using the induction hypothesis. So, assume that $\tau(j) \in [p_\tau(k), N]$ and
	$\eta(\tau(j)) = \eta(\tau(k))$. We want to show $j=k$ or $j = p_\tau(k)$ or $\tau(j)
		\in \tau([1, k])$. Then $j \notin [1, p_\tau(k) - 1]$, because $\tau([1, p_\tau(k)]) =
		[\tau(i'), \tau(p\tau(k))]$ for some $i \in [1, p_\tau(k)]$. By definition of
	$p\tau(k)$ we also have $j \notin [p_\tau(k) + 1, k -1]$. So, either $j = p_\tau(k)$,
	or $j = k$ or $j > k$ in which case $\tau(j) \in \tau([1, k])$, proving the claim.

	So, in both case we found $\oy_{\tau, p_\tau(k)} = \oy_{[s(\tau(k)), s^m(\tau(k))]}$.
	From \cref{lem:symmetrization_of_sum}, we obtain
	\begin{align*}
		\mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), k]})
		 & = \Omega_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), p_\tau(k)]}, e_k)\inv \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), p_\tau(k)]})\mcS_{\bbn_\tau}(e_k) \\
		 & = \Omega_{\bbn}(e_{[s(\tau(k)), s^m(\tau(k))]}, e_{\tau(k)})\inv \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), p_\tau(k)]}),
	\end{align*}
	%
	where $e^\tau_{[p^m_\tau(k), p^l_\tau(k)]} = e_{p^m _\tau(k)} + e_{p^{m-1}_\tau(k)} +
		\cdots + e_{p^l_\tau(k)}$ for $m \geq l \geq 0$. Hence,
	\begin{align*}
		\lt(\oy_{\tau, k})
		 & = \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), k]}) \lt(y_{\tau, k})                                                                                                                                              \\
		 & = \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), k]}) \lt(y_{\tau, p_\tau(k)}x_{\tau(k)})                                                                                                                           \\
		 & = \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), k]}) \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), p_\tau(k)]})\inv \lt(\oy_{\tau, p_\tau(k)}x_{\tau(k)})                                                                 \\
		 & = \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), k]}) \mcS_{\bbn_\tau}(e^\tau_{[p^m_\tau(k), p_\tau(k)]})\inv \Omega_{\bbn}(e_{\tau(k)}, e_{[s(\tau(k)), s^m(\tau(k))]})^{-2} x_{\tau(k)}\lt(\oy_{\tau, p_\tau(k)}) \\
		 & = \Omega_{\bbn}(e_{\tau(k)}, e_{[s(\tau(k)), s^m(\tau(k))]})\inv x_{\tau(k)}\lt(\oy_{\tau, p_\tau(k)})                                                                                                      \\
		 & = \lt(\oy_{[\tau(k), s^m(\tau(k))]}),
	\end{align*}
	%
	which concludes the proof of the proposition.
\end{proof}

We now introduce a subset of $\Xi_N$ which will play a crucial role in the proof of
\cref{thm:gy_main_result}. Denote with $w_\circ \defeq [N, N-1, \dots, 1]$\index{w
	circ@$w_\circ$} the longest element of $S_N$. Then, for $1 \leq i \leq j \leq N$ we
define the following elements of $\Xi_N$:
\begin{equation*}
	\tau_{i,j} \defeq [i+1, i+2, \dots, j, i ,j+1, j+2, \dots, N, i-1,i-2, \dots, 1] \in \Xi_N.
\end{equation*}
\index{tau i j@$\tau_{i,j}$}%%
%
We have $\tau_{1,1} = \id$,
\begin{equation*}
	\tau_{i, N} = [i+1, i+2, \dots, N, i, i-1, 1] = \tau_{i+1, i+1}
\end{equation*}
%
for $i \in [1, N-1]$ and finally $\tau_{N, N} = w_\circ$. We then define $\Gamma_N
	\subseteq \Xi_N$\index{Gamma N@$\Gamma_N$} as the subset consisting of all the
$\tau_{i,j}$ for $1 \leq i \leq j \leq N$. Looking only at CGL extension presentations
obtained from elements of $\Gamma_N$ turns out to be enough. This is already
illustrated by the following corollary.
\begin{corollary}\label{cor:cluster_variables}

	Assume the setting of \cref{thm:gy_main_result}. Then the following sets of cluster
	variables are equal:
	\begin{align*}
		\{M_\tau(e_k) \mid \tau \in \Xi_N,\, k \in [1, N]\}
		 & = \{M_\tau(e_k) \mid \tau \in \Gamma_N,\, k \in [1, N]\}             \\
		 & = \{\oy_{[i,j]} \mid 1 \leq i \leq j \leq N, \, \eta(i) = \eta(j)\}.
	\end{align*}
\end{corollary}
\begin{proof}
	Because $\Gamma_N \subseteq \Xi_N$, we have
	\begin{equation*}
		\{M_\tau(e_k) \mid \tau \in \Gamma_N,\, k \in [1, N]\}
		\subseteq \{M_\tau(e_k) \mid \tau \in \Xi,\, k \in [1, N]\}.
	\end{equation*}
	%
	By \cref{prop:y_tau_is_y_bracket},
	\begin{equation*}
		\{M_\tau(e_k) \mid \tau \in \Xi_N,\, k \in [1, N]\} \subseteq
		\{\oy_{[i,j]} \mid 1 \leq i \leq j \leq N, \, \eta(i) = \eta(j)\}.
	\end{equation*}
	It remains to show
	\begin{equation*}
		\{\oy_{[i,j]} \mid 1 \leq i \leq j \leq N, \, \eta(i) = \eta(j)\} \subseteq
		\{M_\tau(e_k) \mid \tau \in \Gamma_N,\, k \in [1, N]\}.
	\end{equation*}
	%
	Take $1 \leq i \leq j \leq N$ with $\eta(i) = \eta(j)$. Then $i = p^m(j)$, where
	\begin{equation*}
		m = \max \{n \in \bbZ_{\geq 0} \mid p^n(j) \in [i, j]\}.
	\end{equation*}
	For $k' = j - i + 1$, and
	\begin{equation*}
		\tau = \begin{dcases*}
			\id = \tau_{1,1}                                                & if $i=1$    \\
			\tau_{i-1,j} = [i, \dots, j, i-1, j+1, \dots, N, i-2, \dots, 1] & if $i > 1$,
		\end{dcases*}
	\end{equation*}
	%
	we have $\tau(1) = i \leq j = \tau(j - i + 1) = \tau(k')$ and $\tau([1, k']) = [i, j]$.
	Hence,
	\begin{equation*}
		m = \max\{n \in \bbZ_{\geq 0} \mid p^n(\tau(k')) \in \tau([1, k'])\},
	\end{equation*}
	such that \cref{prop:y_tau_is_y_bracket} gives
	\begin{equation*}
		\oy_{\tau, k'} = \oy_{[p^m(\tau(k')), \tau(k')]} = \oy_{[i, j]}.
	\end{equation*}
	%
	Write $k = \tau_\bullet(\tau(k'))$. Then, $M_\tau(e_k) = \oy_{\tau,
			(\tau_\bullet\tau)\inv(k)} = \oy_{[i,j]}$, as we wanted.
\end{proof}

\subsection{Mutation between adjacent presentations}

We now want to prove that $\zeta = 1$ in \cref{thm:almost_mutation_toric_frame}, under
the assumptions of \cref{thm:gy_main_result}. This will be done in
\cref{prop:mutation_adjacent_permutations}. In doing so, we will derive the conditions
of \cref{thm:gy_main_result} (a) for the column which gets mutated. In the next section
these conditions will be used to inductively build the matrix $\tB_\tau$.

\medskip

Recall from \cref{thm:almost_cluster_mutation,thm:almost_mutation_toric_frame} that the
mutation in direction $k$ is determined by the vector
\begin{equation*}
	e_{p(k)} + e_{k+1} - \sum_{i \in P(k-1),\,i\neq p(k)} m_i e_i \in \bbZ^N.
\end{equation*}
%
In order to construct the full mutation matrix, it will be necessary to figure out what
restrictions this vector has. This is established in the next theorem.
\begin{theorem}

	Assume the setting of \cref{thm:almost_cluster_mutation} and \cref{cond:square_roots}.
	Let $h'_{k+1} \in \mcH$ be such $\sigma'_{k+1} = (h'_{k+1}\cdot)$ as in
	\cref{def:cgl_extension}. Then
	\begin{equation}  \label{eq:Omega_r_squared_one}
		\Omega_{\bbr}\left(e_{p(k)} + e_{k+1} - \sum_{i \in P(k-1), i\neq p(k)} m_i e_i, e_j\right)^2  = 1, \quad \forall j \neq k
	\end{equation}
	and
	\begin{equation}\label{eq:Omega_r_squared_ek}
		\begin{aligned}
			\Omega_{\bbr}\left(e_{p(k)} + e_{k+1} - \sum_{i \in P(k-1), i\neq p(k)}m_i e_i, e_k\right)^2 & = \chi_{x_{k+1}}(h_{k+1})\inv \\
			                                                                                             & = \chi_{x_k}(h'_{k+1})
		\end{aligned}
	\end{equation}
	%
	for the collection of nonnegative integers $\{m_i \mid i \in P(k-1), i\neq p(k)\}$ from
	\cref{thm:almost_cluster_mutation,thm:almost_mutation_toric_frame}.

\end{theorem}
\begin{proof}

	Denote for brevity the elements
	\begin{align}
		g            & = \sum_{i \in P(k-1), i\neq p(k)} m_i e_i            \\
		\overline{g} & = \sum_{i \in P(k-1), i\neq p(k)} m_i \overline{e}_i
	\end{align}
	%
	in $\bbZ^N$. By construction of the toric frames $M$ and $M'$, the element
	$\overline{y}_j$ belongs to the image of both $M$ and $M'$ for each $j \neq k$. Recall
	also that
	\begin{equation*}
		M(f)M(f') = \Omega_{\bbr}(f, f')^2 M(f')M(f)
	\end{equation*}
	%
	for any two vectors $f,f' \in \bbZ^N$. Using this together with
	\cref{eq:y_quasi_commute} and \cref{thm:almost_mutation_toric_frame}, we find
	\begin{align*}
		\xi_{kj}\oy_j \oy'_k & = \oy'_k \oy_j                                                                                                                            \\
		                     & = (M(-e_k + e_{p(k)} + e_{k+1}) + \zeta M(-e_k + g))\oy_j                                                                                 \\
		                     & = \oy_j (\Omega_{\bbr}(-e_k + e_{p(k)} + e_{k+1}, e_j)^2 M(-e_k + e_{p(k)} + e_{k+1}) + \zeta\Omega_{\bbr}(-e_k + g, e_j)^2 M(-e_k + g)),
	\end{align*}
	for some $\xi_{kj} \in \bbK$. So,
	\begin{equation*}
		\Omega_{\bbr}(-e_k + e_{p(k)} + e_{k+1}, e_j)^2 = \xi_{kj} = \Omega_{\bbr}(-e_k + g, e_j)^2
	\end{equation*}
	from which it follows that
	\begin{equation*}
		\Omega_{\bbr}(e_{p(k)} + e_{k+1} - g, e_j)^2 = 1,
	\end{equation*}
	%
	due to \cref{eq:Omega_of_sum}. This proves \cref{eq:Omega_r_squared_one}. Now,
	\begin{align*}
		\Omega_{\bbr}(e_{p(k)} + e_{k+1} -g, e_k)^2
		\overset{\eqref{eq:Omega_r_squared_one}} & {=} \Omega_{\bbr}(e_{p(k)} + e_{k+1}-g,e_k - e_{k+1})^2                     \\
		                                         & = \Omega_{\bbn}(\oe_{p(k)} + \oe_{k+1} - \overline{g}, \oe_k - \oe_{k+1})^2 \\
		                                         & = \Omega_{\bbn}(\oe_{p(k)} + \oe_{k+1} - \overline{g}, e_{k+1})^{-2}        \\
		                                         & = \Omega_{\bbn}(\oe_{p(k)} + \oe_k - \overline{g}, e_{k+1})^{-2},
	\end{align*}
	%
	where we used that $\Omega_{\bbn}(e_{k+1}, e_{k+1}) = 1$ in the last step. Since
	$\oy'_k$ is homogeneous, we must have
	\begin{equation*}
		\chi_{M(-e_k + e_{p(k)} + e_{k+1})} = \chi_{M(-e_k + g)},
	\end{equation*}
	%
	from which we obtain $\chi_{M(e_{p(k)} + e_{k+1} - g)} = 1$. Since $y_{k+1} = y_k
		x_{k+1} - c_{k+1}$ by \cref{thm:homogeneous_primes} we also have
	\begin{equation*}
		\chi_{M(e_{p(k)} + e_{l+1} -g)} = \chi_{M(e_{p(k)} + e_k - g)}\chi_{x_{k+1}},
	\end{equation*}
	and hence
	\begin{equation*}
		\chi_{M(e_{p(k)} + e_k - g)} = \chi_{x_{k+1}}\inv.
	\end{equation*}
	%
	Because $h_{k+1} \cdot x_j = \lambda_{k+1, k} x_j = \nu_{k, k+1}^{-2}x_j$ for all $j
		\in [1, N]$, we find
	\begin{equation*}
		\Omega_{\bbn}(\oe_{p(k)}+\oe_k - \overline{g}, e_{k+1})^{-2} = \chi_{M(e_{p(k)} + e_k - g)}(h_{k+1}) = \chi_{x_{k+1}}(h_{k+1})\inv,
	\end{equation*}
	proving the first equality of \cref{eq:Omega_r_squared_ek}.

	It now remains to show that $\chi_{x_{k+1}}(h_{k+1})\inv = \chi_{x_k}(h'_{k+1})$. By
	the first equality of \cref{eq:Omega_r_squared_ek},
	\begin{equation*}
		M(e_{p(k)} + e_{k+1} - g)\oy_k = \chi_{x_{k+1}}(h_{k+1})\inv \oy_k M(e_{p(k)} + e_{k+1} - g).
	\end{equation*}
	%
	If we now apply the same reasoning, but swap the roles of the two CGL presentations, we
	find that
	\begin{equation*}
		M'(e_{p(k)} + e_{k+1} - g)\oy'_k = \chi_{x_k}(h'_{k+1})\inv \oy'_k M'(e_{p(k)} + e_{k+1} - g).
	\end{equation*}
	%
	On the other hand, \cref{thm:almost_mutation_toric_frame} implies that $M'(e_{p(k)} +
		e_{k+1} - g)$ is a scalar multiple of $M(e_{p(k)} + e_{k+1} - g)$, so that we find
	\begin{equation*}
		M(e_{p(k)} + e_{k+1} - g)\oy'_k = \chi_{x_k}(h'_{k+1})\inv \oy'_k M(e_{p(k)} + e_{k+1} - g).
	\end{equation*}
	%
	From \cref{eq:Omega_r_squared_one} we obtain that $M(e_{p(k)} + e_{k+1} - g)$ commutes
	with $M(e_j)$ for all $j \neq k$. In particular, it commutes with $M(e_{p(k)} +
		e_{k+1})$ and $M(g)$, which implies that it commutes with $\oy_k \oy'_k$, using
	\cref{thm:almost_mutation_toric_frame}. Hence,
	$\chi_{x_{k+1}}(h_{k+1})\chi_{x_k}(h'_{k+1}) = 1$, which is what we needed to show.

\end{proof}

For \cref{thm:gy_main_result} (a) we want to rewrite \cref{eq:Omega_r_squared_ek}
slightly. To do so, we make the following observation. Consider the two adjacent
permutations $\tau_{i,j} \in \Gamma_N$ and $\tau_{i, j+1} \in \Gamma_N$ for some $1
	\leq i \leq j < N$. The corresponding CGL extension presentations have the forms
\begin{multline}
	R = \bbK[x_{i+1}]\cdots[x_j;\sigma_j,\delta_j][x_i;\sigma^*_i,\delta^*_i][x_{j+1}; \sigma_{j+1}, \delta_{j+1}][x_{j+2}; \sigma_{j+2}, \delta_{j+2}]\cdots \\
	[x_N;\sigma_{N}, \delta_{N}][x_{i-1}; \sigma_{i-1}^*, \delta^*_{i-1}]\cdots[x_1; \sigma_1^*, \delta^*_1],
\end{multline}
and
\begin{multline}
	R = \bbK[x_{i+1}]\cdots[x_j;\sigma_j,\delta_j][x_{j+1}; \sigma_{j+1}, \delta_{j+1}][x_i;\sigma^*_i,\delta^*_i][x_{j+2}; \sigma_{j+2}, \delta_{j+2}]\cdots \\
	[x_N;\sigma_{N}, \delta_{N}][x_{i-1}; \sigma_{i-1}^*, \delta^*_{i-1}]\cdots[x_1; \sigma_1^*, \delta^*_1].
\end{multline}
%
By \cref{prop:eta_invariance}, we can take $\eta\tau_{i,j}$ as the $\eta$-function of
\cref{thm:homogeneous_primes} for the CGL extension presentation corresponding to
$\tau_{i,j}$. In particular, $\eta_{\tau_{i,j}}(j-i+1) = i$ and
$\eta_{\tau_{i,j}}(j-i+2) = \eta(j+1)$. So, if $\eta(i) = \eta(j+1)$, then
\cref{eq:Omega_r_squared_ek} of the previous theorem implies
\begin{equation*}
	1 = \chi_{x_{j+1}}(h_{j+1})\chi_{x_i}(h^*_i) = \lambda_{j+1}\lambda_i^*.
\end{equation*}
%
Since $1 \leq i \leq j < N$ were arbitrary we find $\lambda_{k}^* = \lambda_{l}\inv$
for any $k < l$ such that $\eta(k) = \eta(l)$. This gives the following proposition.
\begin{proposition}\label{prop:lambda*_of_successor}
	Let $R$ be a symmetric CGL extension of length $N$ and $a \in \bbZ$ in the image of $\eta$. Write $\eta\inv(a) = \{l, s(l), \dots, s^m(l)\}$, where $l\in [1, N]$ and $m = O_{+}(l)$. Then
	\begin{equation*}
		\lambda_l^* = \lambda_{s(l)}^* = \cdots = \lambda_{s^{m-1}(l)}^* = \lambda\inv_{s(l)}=\lambda\inv_{s^2(l)} = \cdots = \lambda\inv_{s^m(l)}.
	\end{equation*}
\end{proposition}

\medskip

In order to prove that $\zeta = 1$ in \cref{thm:almost_mutation_toric_frame} under the
assumptions of \cref{cond:square_roots,cond:no_order_two,cond:normalization_generators}
we need to keep track precisely of all the coefficients. It turns out that this is best
done by looking at the elements $y_{[i, s^m(i)]}$ instead of the elements $y_{\tau,
			k}$. To do so, we introduce some new notation.

Fix $i \in [1, N]$ and $m\in \bbZ_{>0}$ such that $s^m(i) \neq +\infty$. We consider
the CGL extension presentation of $R_{[i, s^m(i)]}$ with the following order of the
generators:
\begin{equation*}
	x_{i+1}, x_{i+2}, \dots, x_{s^m(i) - 1}, x_i, x_{s^m(i)}.
\end{equation*}
%
Write $t = s^m(i)-i +1$. We then identify $\bbZ^t \cong \bbZ e_i + \cdots + \bbZ
	e_{s^m(i)}$ and index the rows and columns of matrices in $M_t(\bbZ)$ by $i, \cdots,
	s^m(i)$. Recall from \cref{prop:def_u_brackets} that we write
\begin{equation*}
	O_{-}^j(k) \defeq \max \{n \in \bbZ_{\geq 0} \mid p^n(k) \geq j\},
\end{equation*}
\index{O j minus k@$O_{-}^j(k)$}%%
%
and then define, for $k \in [i, s^m(i)]$,
\begin{equation*}
	e'_k \defeq \begin{dcases*}
		e_{[p^{O^{i+1}_{-}(k)}, k]}, & if $k \in [i+1, s^m(i) - 1]$ \\
		e_{[i, s^{m-1}(i)]},         & if $k=i$                     \\
		e_{[i, s^m(i)]},             & if $k = s^m(i)$.
	\end{dcases*}
\end{equation*}
%
This then gives rise to the toric frame $M_{[i, s^m(i)]}\colon \bbZ^t \to \Fract(R_{[i,
				s^m(i)]})$, with matrix
\begin{equation*}
	\bbr_{[i, s^m (i)]} \defeq (\Omega_{\bbn}(e'_k,e'_j)),
\end{equation*}
such that
\begin{equation*}
	M_{[i, s^m(i)]}(e_k) \defeq \begin{dcases*}
		\oy_{[p^{O^{i+1}_{-}(k)}, k]}, & if $k \in [i+1, s^m(i) - 1]$ \\
		\oy_{[i, s^{m-1}(i)]},         & if $k=i$                     \\
		\oy_{[i, s^m(i)]},             & if $k = s^m(i)$.
	\end{dcases*}
\end{equation*}
\index{M i smi@$M_{[i, s^m(i)]}$}%%

Finally, \cref{prop:def_u_brackets} implies that
\begin{equation*}
	f_{[i, s^m(i)]} = \sum\{m_k e_{[p^{O^{i+1}_{-}}(k), k]} \mid k \in P_{[i, s^m(i)]}\},
\end{equation*}
for the integers $m_k$ of \cref{thm:almost_cluster_mutation}, and we define
\begin{equation*}
	g_{[i, s^m(i)]} \defeq \sum\{m_k e_k \mid k \in P_{[i, s^m(i)]}\}.
\end{equation*}
%
In this setting one can obtain the following version of a mutation statement. We omit
the long and technical proof.

\begin{theorem}[\protect{\cite[Theorem 6.6]{GoodearlYakimov2017QCA}}]\label{thm:mutation_for_bracket_frames}
	Let $R$ be a symmetric CGL extension such that \cref{cond:square_roots,cond:no_order_two,cond:normalization_generators} are satisfied. Then, for all $i \in [1, N]$ and $m \in \bbZ_{> 0}$ such that $s^m(i) \in [1, N]$,
	\begin{equation*}
		\oy_{[s(i), s^m(i)]} = \begin{dcases*}
			M_{[i, s(i)]}(e_{s(i)} - e_i) + M_{[i, s(i)]}(g_{[i, s(i)]} - e_i),                         & if $m=1$    \\
			M_{[i, s^m(i)]}(e_{s^{m-1}(i)} + e_{s^m(i)} -e_i) + M_{[i, s^m(i)]}(g_{[i, s^m(i)]} - e_i), & if $m > 1$.
		\end{dcases*}
	\end{equation*}
\end{theorem}

The main task for the proof of \cref{prop:mutation_adjacent_permutations} will be to
convert the result of \cref{thm:mutation_for_bracket_frames} back to the setting of
\cref{thm:gy_main_result}. This relies heavily on \cref{prop:y_tau_is_y_bracket}.

Write, for $g = g_1e_1 + \dots g_N e_N \in \bbZ^N$,
\begin{equation*}
	\supp(g) \defeq \{j \in [1, N] \mid g_j \neq 0\}.
\end{equation*}
\index{supp g@$\supp(g)$}%%
We can now finally prove mutation between adjacent presentations.

\begin{proposition}\label{prop:mutation_adjacent_permutations}
	Let $R$ be a symmetric CGL extension such that \cref{cond:square_roots,cond:no_order_two,cond:normalization_generators} are satisfied. Let $\tau, \tau' \in \Xi_N$ be such that
	\begin{equation*}
		\tau' = (\tau(k), \tau(k+1))\tau = \tau(k, k+1)
	\end{equation*}
	for some $k \in [1, N-1]$.
	\begin{enumerate}[(a)]
		\item If $\eta(\tau(k)) \neq \eta(\tau(k + 1))$, then $M_{\tau'} = M_\tau$.
		\item If $\eta(\tau(k)) = \eta(\tau(k+1))$, set $k_\bullet = \tau_\bullet\tau(k)$. Then
		      $(\tau')_\bullet\tau'(k) = k_\bullet$ and,

		      \begin{equation*}
			      M_{\tau'}(e_j) = \begin{dcases*}
				      M_{\tau}(e_j),                                                                         & if $j \neq k_\bullet$ \\
				      M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet}) + M_\tau(g-e_{k_\bullet}), & if $j =k_\bullet$
			      \end{dcases*}
		      \end{equation*}
		      for some $g \in \bbZ^N_{\geq 0}$ such that $\supp(g)\cap \eta\inv(\eta(k_\bullet)) = \emptyset$ and $|\supp(g)\cap \eta \inv (a)| \leq 1$ for all $a \in \bbZ$. Furthermore, if $\tau(k) < \tau(k +1)$, then the vector $e_{p(k_\bullet)} + e_{s(k_\bullet)} - g \in \bbZ^N$ satisfies the identities
		      \begin{align*}
			       & \Omega_{\bbr_\tau}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g, e_j) = 1, \, \forall j \neq k_\bullet, \\
			       & \Omega_{\bbr_\tau}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g, e_k)^2 = \lambda^*_k,                  \\
			      \shortintertext{and}
			       & \chi_{M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g)} = 1.
		      \end{align*}
		      %
		      If $\tau(k) > \tau(k+1)$, the identities are instead satisfied by the vector
		      $-(e_{p(k_\bullet)} + e_{s(k_\bullet)} -g) \in \bbZ^N$.
	\end{enumerate}
\end{proposition}
\begin{proof}

	We will first prove the proposition for the case $\tau(k) < \tau(k+1)$. The case
	$\tau(k) > \tau(k+1)$ will then follow from this.

	If $\eta(\tau(k)) \neq \eta(\tau(k+1))$, then \cref{lem:tau_bullet} (b) shows that
	$\tau_\bullet \tau (k, k+1) = (\tau')_\bullet \tau'$, and part (a) of the theorem now
	follows from \cref{thm:almost_mutation_toric_frame} (a).

	We now consider the case where $\eta(\tau(k)) = \eta(\tau(k+1))$ which requires
	significantly more work. Because $\tau([1, k])$ and $\tau([1, k+1])$ are intervals,
	$\tau(k+1)$ must lie on one of the endpoints of the interval $\tau([1, k+1])$. The
	assumption $\tau(k) < \tau(k+1)$ forces
	\begin{equation*}
		\tau'([1, k+1]) = \tau([1, k+1]) = [\tau(i), \tau(k+1)] \quad \text{and}\quad \tau([1, k]) = [\tau(i), \tau(k+1) - 1]
	\end{equation*}
	for some $i\in [1, k]$. But then,
	\begin{equation*}
		\tau'([1, k]) = \tau'([1, k+1])\setminus\{\tau'(k+1)\} = [\tau(i), \tau(k+1)] \setminus \{\tau(k)\},
	\end{equation*}
	%
	forces $\tau(k) = \tau(i)$ as $\tau'([1, k])$ must also be an interval. Hence,
	\begin{align*}
		\tau'([1, k+1]) & = \tau([1, k+1]) = [\tau(k), \tau(k+1)], \\
		\tau([1, k])    & = [\tau(k), \tau(k+1) - 1],              \\
		\shortintertext{and}
		\tau'([1, k])   & = [\tau(k) + 1, \tau(k+1)].
	\end{align*}
	%
	Because $\eta(\tau(k)) = \eta(\tau(k+1))$ and $\tau(k) < \tau(k+1)$, we must have
	\begin{equation*}
		\tau(k+1) = s^m(\tau(k)) \text{ for some } m \in \bbZ_{\geq 0}.
	\end{equation*}
	%
	This then implies
	\begin{equation}\label{eq:level_set_tau_k}
		\begin{aligned}
			\eta\inv(\eta(\tau(k))) \cap \tau([1, k+1])
			 & = \{j \in [\tau(k), s^m(\tau(k))] \mid \eta(j) = \eta(\tau(k))\} \\
			 & = \{\tau(k), s(\tau(k)), \dots, \tau(k+1) = s^m(\tau(k))\}.
		\end{aligned}
	\end{equation}
	%
	Then, since $\tau_\bullet \tau = (\tau')_\bullet \tau'$, by \cref{lem:tau_bullet}, we
	obtain using \cref{thm:almost_mutation_toric_frame} that $M_\tau(e_j) = M_{\tau'(e_j)}$
	for all $j \neq k_\bullet$.

	Now, from $\tau([1, k]) = [\tau(k), \tau(k+1) - 1] = [\tau(k), s^m(\tau(k)) - 1]$ it
	follows that
	\begin{equation*}
		m - 1 = \max\{n \in \bbZ_{\geq 0} \mid s^m(\tau(k)) \in \tau([1, k])\}.
	\end{equation*}
	%
	By \cref{prop:y_tau_is_y_bracket}, and similar arguments for $k+1$ and $\tau'$,
	\begin{align*}
		\oy_{\tau, k+1} & = \oy_{[\tau(k), s^m(\tau(k))]},     \\
		\oy_{\tau, k}   & = \oy_{[\tau(k), s^{m-1}(\tau(k))]}, \\
		\oy_{\tau', k}  & = \oy_{[s(\tau(k)), s^m(\tau(k))]}.
	\end{align*}

	Our goal is now to apply \cref{thm:mutation_for_bracket_frames}. To do this, we will
	construct an isomorphism $\dot{w}$ from $\bbZ^{s^m(\tau(k)) -\tau(k) + 1} = \bbZ^{k+1}$
	to $\bbZ e_{\tau(k)} + \bbZ e_{\tau(k)+1} + \dotsb + \bbZ e_{s^m(\tau(k))}$ in such a
	way that the toric frames $\wh{M}_\tau$ and $M_{[\tau(k), s^m(\tau(k))]}\dot{w}$ agree
	on suitable $e_j$.

	Recall that
	\begin{equation*}
		P_{[\tau(k), s^m(\tau(k))]} = \{j \in [\tau(k), s^m(\tau(k)) -1] \mid s(j) > s^m(\tau(k))\}.
	\end{equation*}
	Hence, $\eta$ is injective on this set and
	\begin{equation*}
		Q = \{j \in [1, k-1] \mid \eta(\tau(j)) \neq \eta(\tau(l)),\, \forall l \in [j+1, k+1]\},
	\end{equation*}
	is in bijection with the set
	\begin{equation*}
		A = \eta(P_{[\tau(k), s^m(\tau(k))]}) = \eta(\tau([1, k+1])) \setminus \{\eta(\tau(k))\},
	\end{equation*}
	%
	through the restriction of $\eta \tau$. The injectivity of $\eta$ on $P_{[\tau(k),
						s^m(\tau(k))]}$ also implies
	\begin{equation*}
		|Q| = |A| = |P_{[\tau(k), s^m(\tau(k))]}|.
	\end{equation*}
	%
	By definition of $Q$, we have $\eta(t) \neq \eta(\tau(j))$ for $j \in Q$ and $t \in
		\tau([j+1, k +1])$. Hence,
	\begin{equation}\label{eq:tau_1j}
		\{t \in [\tau(k), s^m(\tau(k))] \mid \eta(t) = \eta(\tau(j))\} \subseteq \tau([1, j]), \forall j \in Q.
	\end{equation}
	%
	We now differentiate two cases for $j \in Q$.
	\begin{itemize}
		\item If $\tau(j) \geq \tau(1)$ then $\tau([1, j]) = [\tau(i_j), \tau(j)]$ for some $i_j \in
			      [1, j]$, and hence $\tau(j) \in P_{[\tau(k), s^m(\tau(k))]}$ by \cref{eq:tau_1j}.
		      Furthermore,
		      \begin{equation*}
			      m_j = O_{-}^{\tau(k) + 1}(\tau(j)) = \max\{n \in \bbZ_{\geq 0} \mid p^n (\tau(j)) \in \tau([1, j])\},
		      \end{equation*}
		      such that \cref{prop:y_tau_is_y_bracket} implies
		      \begin{equation*}
			      \oy_{\tau, j} = \oy_{[p^m_j(\tau(j), \tau(j))]} = M_{[\tau(k), s^m(\tau(k))]}(e_{\tau(j)}).
		      \end{equation*}
		\item If $\tau(j) < \tau(1)$, then $\tau([1, j]) = [\tau(j), \tau(i_j)]$ for some $i_j \in
			      [1, j-1]$. Let $m_j$ be the integer corresponding to $j$ in
		      \cref{prop:y_tau_is_y_bracket}, and write $s^{m_j}(\tau(j)) = \tau(j^{-})$. Then
		      $s(\tau(j^{-})) > s^m(\tau(k))$ and hence $\tau(j^{-}) \in P_{[\tau(k),
							      s^m(\tau(k))]}$. Furthermore, $m_j = O_{-}^{\tau(k) + 1}$ such that
		      \cref{prop:y_tau_is_y_bracket} gives
		      \begin{equation*}
			      \oy_{\tau, j} = \oy_{[p^{m_j}(\tau(j^{-})), \tau(j^{-})]} = M_{[\tau(k), s^m(\tau(k))]}(e_{\tau(j^{-})}).
		      \end{equation*}
	\end{itemize}

	If $m > 1$, then we need one more definition before defining $\dot{w}$. Set, recalling
	\cref{eq:level_set_tau_k},
	\begin{equation*}
		t = \max\{\tau\inv\{s(\tau(k)), \dots, s^{m-1}(\tau(k))\}\} = \max \{j \in [1, k-1] \mid \eta(\tau(j)) = \eta(\tau(k))\} = p_\tau(k).
	\end{equation*}
	%
	Then, because $\tau([1, t])$ is an interval, either $\tau(t) = s^{m-1}(\tau(k))$ or
	$\tau(t) = s(\tau(k))$. \Cref{prop:y_tau_is_y_bracket} now yields
	\begin{equation*}
		\oy_{\tau, t} = \oy_{[s(\tau(k)), s^{m-1}(\tau(k))]} = M_{[\tau(k), s^m(\tau(k))]}(e_{s^{m-1}(\tau(k))}).
	\end{equation*}

	Let $w \colon [1, k+1] \to [\tau(k), s^m(\tau(k))]$ be any bijection such that
	\begin{align*}
		w(k+1) & = s^m(\tau(k))                                                            \\
		w(k)   & = \tau(k)                                                                 \\
		w(t)   & = s^{m-1}(\tau(k)),\,\text{ if }m >1                                      \\
		w(j)   & = \tau(j), \,\text{ for all }j \in Q \text{ with } \tau(j) \geq \tau(1)   \\
		w(j)   & = \tau(j^{-}), \,\text{ for all }j \in Q \text{ with } \tau(j) < \tau(1).
	\end{align*}
	%
	Such a $w$ exists, because $t,k,k+1 \notin Q, w(j) \in P_{[\tau(k), s^m(\tau(k))]}
		\not\ni \tau(k), s^{m-1}(\tau(k)), s^m(\tau(k))$ and $\eta w(j) = \eta(\tau(j))$ for
	all $j \in Q$. Since $|Q| = |P_{[\tau(k), s^m(\tau(k))]}|$, it follows that
	\begin{equation}\label{eq:w_is_bijection}
		w|_Q \colon Q \to P_{[\tau(k), s^m(\tau(k))]}\quad \text{ is a bijection.}
	\end{equation}
	%
	Denote with $\dot{w}$ the isomorphism $\bbZ^{k+1} \to \bbZ e_{\tau(k)} + \cdots + \bbZ
		e_{s^m(\tau(k))}$ such that $\dot{w}(e_j) = e_{w(j)}$ for $j\in[1, k+1]$. Then, by
	construction, we have
	\begin{equation*}
		\wh{M}_\tau(e_j) = \oy_{\tau, j} = M_{[\tau(k), s^m(\tau(k))]}\dot{w}(e_j),
	\end{equation*}
	%
	for $j\in Q \cup \{t, k, k+1\}$ if $m>1$ and $j \in Q \cup \{k, k+1\}$ if $m=1$. The
	matrices of the toric frames also agree on the same sets, i.e.,
	\begin{equation*}
		(\bbr(\wh{M}_\tau |_{\bbZ^{k+1}}))_{lj} = ((\bbr_{[\tau(k), s^m(\tau(k))]})\dot{w})_{lj}
	\end{equation*}
	%
	for $l,j \in Q \cup \{t, k, k+1\}$ if $m>1$ and $l, j \in Q \cup \{k, k+1\}$ if $m=1$.

	We can now apply \cref{thm:mutation_for_bracket_frames}. Assume first that $m = 1$.
	Then,
	\begin{equation*}
		\wh{M}_\tau(f) = M_{[\tau(k), s(\tau(k))]}\dot{w}(f)
	\end{equation*}
	for all $f \in \bbZ^N$ such that $\supp(f) \subseteq Q \cup \{k, k+1\}$. Thus, because of \cref{eq:w_is_bijection}, we obtain from \cref{thm:y_square_brackets} that
	\begin{equation*}
		\oy_{\tau', k} = \oy_{[s(\tau(k)), s(\tau(k))]} = \wh{M}_\tau(e_{k+1} - e_k) + \wh{M}_{\tau}(g' - e_k),
	\end{equation*}
	%
	where $\supp(g') \subseteq \dot{w}\inv(P_{[\tau(k), s(\tau(k))]}) = Q$. By
	\cref{eq:level_set_tau_k}, we find that $\tau_\bullet\tau(k+1) = s(k_\bullet)$ and
	$p_{k\bullet} = -\infty$. Hence,
	\begin{equation*}
		M_{\tau'}(e_{k_\bullet}) = \wh{M}_{\tau'}(e_k) = \oy_{\tau', k} = M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet}) + M_\tau(\tau_\bullet \tau(g') - e_{k\bullet})
	\end{equation*}
	%
	which is what we needed to show.

	If $m > 1$, the reasoning is analogous. We first observe that
	\begin{equation*}
		\wh{M}_\tau(f) = M_{[\tau(k), s^m(\tau(k))]}\dot{w}(f)
	\end{equation*}
	for all $f \in \bbZ^N$ such that $\supp(f) \subseteq Q \cup \{t, k , k+1\}$. Thus, \cref{eq:w_is_bijection,thm:mutation_for_bracket_frames} give
	\begin{align*}
		\oy_{\tau', k} = \oy_{[s(\tau(k)), s^m(\tau(k))]} = \wh{M}_\tau(e_t + e_{k+1} - e_k) + \wh{M}_\tau(g' - e_k),
	\end{align*}
	where $\supp(g') \subseteq Q$. By \cref{eq:level_set_tau_k}, we find this time that
	\begin{equation*}
		\tau_\bullet\tau(t) = p(k_\bullet) \quad \text{and} \quad \tau_\bullet\tau(k+1) = s(k_\bullet),
	\end{equation*}
	from which we obtain
	\begin{equation*}
		M_{\tau'}(e_{k_\bullet}) = \wh{M}_{\tau'}(e_k) = \oy_{\tau', k} = M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet}) + M_\tau(\tau_\bullet \tau(g') - e_{k\bullet}),
	\end{equation*}
	again.

	We now resolve the remaining identities. Write $g = \tau_\bullet \tau(g')$. Note that
	the $p(k)$ appearing in \cref{eq:Omega_r_squared_ek,eq:Omega_r_squared_one} is with
	respect to the presentation corresponding to $\tau$, and is hence equal to $p_\tau(k) =
		t$ in the current setting. Consequently, \cref{eq:Omega_r_squared_one} gives
	\begin{equation*}
		\Omega_{\bbr_\tau}(e_{p(k_\bullet)} + e_{s(k_\bullet)} -g, e_j) = 1
	\end{equation*}
	for all $j\neq k_\bullet$, because of \cref{cond:no_order_two}. Now note that by definition of $k_\bullet$,
	we have $\eta(k_\bullet) = \eta(\tau(k))$. Furthermore, $s(k_\bullet) =
		\tau_\bullet\tau(k+1) \neq + \infty$ and $s(\tau(k)) \leq \tau(k+1) < + \infty$ so that
	we obtain $\chi_{x_{\tau(k)}}(h^*_{\tau(k)}) = \lambda^*_{\tau(k)} =
		\lambda^*_{k_\bullet}$ using \cref{prop:lambda*_of_successor}. Hence, \cref{eq:Omega_r_squared_ek} gives
	\begin{equation*}
		\Omega_{\bbr_\tau}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g, e_{k_\bullet})^2 = \lambda_{k_\bullet}^*.
	\end{equation*}

	Finally, since $\oy_{\tau, j}$ and $\oy_{\tau', j}$ are $\mcH$-eigenvectors for all
	$j\in [1, N]$, we must have
	\begin{equation*}
		\chi_{M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g)} = 1,
	\end{equation*}
	because
	\begin{equation*}
		M_{\tau'}(e_{k_\bullet}) =
		M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet}) + M_\tau(g-e_{k_\bullet}).
	\end{equation*}

	\medskip

	We now show how the case $\tau(k) > \tau(k+1)$ can be handled. Note that in this case
	\begin{equation*}
		\tau'(k) = \tau(k+1) < \tau(k) = \tau'(k+1).
	\end{equation*}
	%
	We can thus apply the part we already proved with the roles of $\tau$ and $\tau'$
	swapped. This immediately resolves case (a), since it is symmetric in $\tau$ and
	$\tau'$. It remains to show that the conclusions of (b) for $\tau$ also hold for
	$\tau'$. To do this, we must carefully compare $\bbr_\tau$ and $\bbr_{\tau'}$. We make
	extensive use of \cref{eq:Omega_of_sum,eq:Omega_skew_symmetric}.

	From \cref{thm:almost_mutation_toric_frame} we have
	\begin{align*}
		 & \Omega_{\wh{\bbr}_{\tau'}}(e_l, e_j) = \Omega_{\wh{\bbr}_\tau}(e_l, e_j), \, \forall l, j \neq k,                        \\
		 & \Omega_{\wh{\bbr}_{\tau'}}(e_k, e_j) = \Omega_{\wh{\bbr}_\tau}(e_{p_\tau(k)} + e_{k+1} - e_k, e_j), \, \forall j \neq k.
	\end{align*}
	%
	Thus, because $\tau_\bullet\tau = (\tau')_\bullet\tau'$ by \cref{lem:tau_bullet},
	\begin{align*}
		 & \Omega_{{\bbr}_{\tau'}}(e_l, e_j) = \Omega_{{\bbr}_\tau}(e_l, e_j), \, \forall l, j \neq {k_\bullet},                                                            \\
		 & \Omega_{{\bbr}_{\tau'}}(e_{k_\bullet}, e_j) = \Omega_{{\bbr}_\tau}(e_{p({k_\bullet})} + e_{s({k_\bullet})} - e_{k_\bullet}, e_j), \, \forall j \neq {k_\bullet}.
	\end{align*}
	%
	From this we obtain
	\begin{equation*}
		\Omega_{\bbr_{\tau'}}(-(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g), e_j) =
		\Omega_{\bbr_{\tau}}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g, e_j)\inv  = 1\inv = 1
	\end{equation*}
	for all $j \neq k_\bullet$, and
	\begin{align*}
		\Omega_{\bbr_{\tau'}}(-(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g), e_{k_\bullet})^2
		 & =\Omega_{\bbr_{\tau}}(-(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g), e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet})^2 \\
		 & =\Omega_{\bbr_{\tau}}(-(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g),- e_{k_\bullet})^2                                      \\
		 & =\Omega_{\bbr_{\tau}}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g,e_{k_\bullet})^2                                           \\
		 & =\lambda_{k_\bullet}^* .
	\end{align*}
	%
	Since $M_\tau (e_j) = M_{\tau'}(e_j)$ for all $j\neq k_\bullet$ we obtain that $M_\tau
		(f) = M_{\tau'}(f)$ for all $f\in \bbZ^N$ such that $k_\bullet \notin \supp(f)$. Thus,
	also
	\begin{equation*}
		\chi_{M_{\tau'}(-(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g))} =
		\chi_{M_{\tau'}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g)} =
		\chi_{M_{\tau}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g)} = 1.
	\end{equation*}
	%
	It remains to show
	\begin{equation*}
		M_{\tau}(e_{k_\bullet}) = M_{\tau'}(e_{p(k_\bullet)}+e_{s(k_\bullet)}-e_{k_\bullet}) + M_{\tau'}(g-e_{k_\bullet}).
	\end{equation*}
	%
	On the one hand we have
	\begin{equation*}
		M_\tau(g - e_{k_\bullet}) = \Omega_{\bbr_\tau}(-e_{k_\bullet}, g) M_\tau(g) M_\tau(e_{k_\bullet})\inv,
	\end{equation*}
	and
	\begin{align*}
		M_{\tau'}(e_{k_\bullet})\inv M_\tau(g)
		 & = M_{\tau'}(e_{k_\bullet})\inv M_{\tau'}(g)                                                                        \\
		 & =  \Omega_{\bbr_{\tau'}}(-e_{k_\bullet}, g)M_{\tau'}(g -e_{k_\bullet})                                             \\
		 & =  \Omega_{\bbr_{\tau}}(e_{p(k_\bullet)} + e_{s(k_\bullet)} -e_{k_\bullet}, g)\inv M_{\tau'}(g -e_{k_\bullet})     \\
		 & =  \Omega_{\bbr_{\tau}}(e_{p(k_\bullet)} + e_{s(k_\bullet)} - g -e_{k_\bullet}, g)\inv M_{\tau'}(g -e_{k_\bullet}) \\
		 & =  \Omega_{\bbr_{\tau}}(-e_{k_\bullet}, g)\inv M_{\tau'}(g -e_{k_\bullet}),
	\end{align*}
	such that
	\begin{equation*}
		M_{\tau'}(e_{k_\bullet})\inv M_\tau(g -e_{k_\bullet}) = M_{\tau'}(g - e_{k_\bullet})M_\tau (e_{k_\bullet})\inv.
	\end{equation*}
	%
	On the other hand we have
	\begin{equation*}
		M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)} - e_{k_\bullet}) = \Omega_{\bbr_\tau}( \ekbullet, \epsbullet)\inv  M_\tau(e_{p(k_\bullet)} + e_{s(k_\bullet)}) M_\tau (e_{k_\bullet})\inv,
	\end{equation*}
	and
	\begin{align*}
		M_{\tau'}(\ekbullet)\inv M_\tau(\epsbullet)
		 & = M_{\tau'}(\ekbullet)\inv M_{\tau'}(\epsbullet)                                               \\
		 & = \Omega_{\bbr_{\tau'}}(\ekbullet, \epsbullet)\inv M_{\tau'}(\epsbullet - \ekbullet)           \\
		 & = \Omega_{\bbr_{\tau}}(\epsbullet-\ekbullet, \epsbullet)\inv M_{\tau'}(\epsbullet - \ekbullet) \\
		 & = \Omega_{\bbr_{\tau}}(-\ekbullet, \epsbullet)\inv M_{\tau'}(\epsbullet - \ekbullet)           \\
		 & = \Omega_{\bbr_{\tau}}(\ekbullet, \epsbullet) M_{\tau'}(\epsbullet - \ekbullet),
	\end{align*}
	such that
	\begin{equation*}
		M_{\tau'}(\ekbullet)\inv M_\tau(\epsbullet - \ekbullet) = M_{\tau'}(\epsbullet - \ekbullet)M_\tau(\ekbullet)\inv.
	\end{equation*}
	%
	Thus, using that
	\begin{equation*}
		M_{\tau'}(e_{k_\bullet}) = M_{\tau}(e_{p(k_\bullet)}+e_{s(k_\bullet)}-e_{k_\bullet}) + M_{\tau}(g-e_{k_\bullet}),
	\end{equation*}
	we obtain
	\begin{equation*}
		M_{\tau}(e_{k_\bullet}) = M_{\tau'}(e_{p(k_\bullet)}+e_{s(k_\bullet)}-e_{k_\bullet}) + M_{\tau'}(g-e_{k_\bullet}),
	\end{equation*}
	as desired. This concludes the proof of the proposition.
\end{proof}

\section{Constructing quantum seeds}\label{sec:constructing_quantum_seeds}

We will now use the results of \cref{prop:mutation_adjacent_permutations} to prove
parts (a), (b) and (c) of \cref{thm:gy_main_result}. We begin with a short outline of
the proof.

From \cref{prop:mutation_adjacent_permutations} we obtain the column
$b^{k_\bullet}_{\tau} = \epsbullet - g$ of the matrix $\tB_\tau$, where $k_\bullet =
	\tau_\bullet(\tau(k))$, whenever we have a pair of adjacent permutations $\tau, \tau'$
such that $\tau(k) < \tau(k+1)$ and $\eta(\tau(k)) = \eta(\tau(k+1))$. This only gives
some columns. The other columns will be constructed inductively through mutation. This
is achieved for the most part in \cref{lem:inductive_columns}.

A priori, there might be some issues with this approach.
\Cref{lem:xi_n_characterization} gives a way to reach $\tau$ by a sequence of adjacent
permutations, but this sequence is not necessarily unique. It could be possible that
two different sequences would yield different columns. This is resolved by showing
uniqueness of vectors satisfying similar conditions to the vector $\epsbullet -g$ in
\cref{prop:mutation_adjacent_permutations}. This will be shown in \cref{lem:unique_b}.
Furthermore, we show that these conditions are preserved under mutation. This makes it
possible to keep those conditions on all the columns, and ensures uniqueness for the
whole matrix $\tB_\tau$.

\subsection{Recursive construction of the columns}

We start by showing uniqueness for vectors satisfying conditions similar to the vector
$\epsbullet - g$ in \cref{prop:mutation_adjacent_permutations}.

\begin{lemma}\label{lem:unique_b}
	Assume that $R$ is a symmetric CGL extension of length $N$ satisfying \cref{cond:square_roots}. Then, for all $\tau \in \Xi_N, \theta \in X(\mcH)$, and $\xi_1, \dots, \xi_N \in \bbK^\times$, there exists at most one vector $b\in \bbZ^N$ such that $\chi_{M_\tau(b)} = \theta$ and $\Omega_{\bbr_\tau}(b, e_j)^2 = \xi_j$ for all $j \in [1, N]$.
\end{lemma}
\begin{proof}
	Suppose that $b_1, b_2 \in \bbZ^N$ are such that $\chi_{M_\tau(b_1)} = \chi_{M_\tau(b_2)} = \theta$, and $\Omega_{\bbr_\tau}(b_1, e_j)^2 = \Omega_{\bbr_\tau}(b_2, e_j)^2 = \xi_j$ for all $j \in [1, N]$. From the first equality, we find
	\begin{equation*}
		\chi_{M_\tau(b_1)M_\tau(b_2)\inv} = 1.
	\end{equation*}
	%
	The second condition implies that $M_\tau(b_1)M_\tau(b_2)\inv$ commutes with
	$M_\tau(e_j)$ for all $j\in [1, N]$. Thus, by \cref{prop:y_quantum_torus}, it must lie
	in the center, $Z(\Fract(R))$. We now apply \cref{thm:H_rationality}, to conclude that
	$M_\tau(b_1)M_\tau(b_2)\inv \in \bbK$, which can only happen when $b_1 = b_2$.
\end{proof}

That these conditions are preserved under mutation will follow from the next lemma,
together with \cref{prop:mutation_preserves_good_things}.
\begin{lemma}\label{lem:equivariance_mutations}

	Let $\mcF$ be a division algebra and $\mcH$ a group acting on $\mcF$ by algebra
	automorphisms. Assume that $(M, \tB)$ is a quantum seed for $\mcF$ such that $M(f)$ is
	an $\mcH$-eigenvector for all $f \in \bbZ^N$, and that $\chi_{M(b^j)} = 1$ for all
	columns $b^j$ of $\tB$. Then all mutations of the seed $(M, \tB)$ share the same
	properties.
\end{lemma}
\begin{proof}
	Denote, for brevity, $M' = \mu_k(M)$ and $\tB' = \mu_k(\tB)$. Since $\chi_{M(b^k)} = 1$ and $b^k = [b^k]_{+} + [b^k]_{-}$, we find
	\begin{equation*}
		\chi_{M(-e_k + [b^k]_{+})} = \chi_{M(-e_k - [b^k]_{-})}.
	\end{equation*}
	%
	Thus, by \cref{prop:formula_for_mutation}, $M'(e_k)$ is an $\mcH$-eigenvector with
	$\mcH$-eigenvalue
	\begin{equation*}
		\chi_{M'(e_k)} = \chi_{M(-e_k + [b^k]_{+})} = \chi_{M(-e_k - [b^k]_{-})}.
	\end{equation*}
	Then, since $M'(e_j) = M(e_j)$ for all $j \neq k$, we find that $M'(f)$ is an $\mcH$-eigenvector for all $f \in \bbZ^N$. Furthermore, since $\bbr(M')_{ij} = \bbr(M)_{ij}$ for all $i,j \neq k$, we have $M'(f) = M(f)$ for all $f \in \bbZ^N$ such that $k \notin \supp(f)$.

	It remains to check the $\mcH$-eigenvalues of the columns $(b')^j$ of the matrix
	$\tB'$. Because the principal part of $\tB'$ is skew-symmetrizable, we have $k \notin
		\supp((b')^k)$ and $\chi_{M'((b')^k)} = \chi_{M((b')^k)} = \chi_{M(-b^k)} = 1$.
	Similarly, for $j \neq k$, if $b_{kj} = 0$ then $\chi_{M'((b')^j)} = \chi_{M(b^j)} =
		1$. If $b_{kj} \neq 0$, then
	\begin{equation*}
		(b')^j = b^j + \epsilon b_{kj}[b^k]_{\epsilon} - 2 b_{kj}e_k,
	\end{equation*}
	where $\epsilon = \sign(b_{kj})$. Thus,
	\begin{align*}
		\chi_{M'((b')^j)}
		 & = \chi_{M'(b^j + \epsilon b_{kj}[b^k]_\epsilon - 2b_{kj} e_k)}                                                  \\
		 & = \chi_{M'(b^j + \epsilon b_{kj}[b^k]_\epsilon - b_{kj} e_k)}\chi_{M'(-b_{kj}e_k)}                              \\
		 & = \chi_{M(b^j + \epsilon b_{kj}[b^k]_\epsilon - b_{kj} e_k)}\chi_{M(b_{kj}e_k - \epsilon b_{kj}[b^k]_\epsilon)} \\
		 & = \chi_{M(b^j)} = 1.
	\end{align*}
\end{proof}

In the next lemma we assume existence of the matrix $\tB_\tau$ or $\tB_{\tau'}$ and use
it to prove existence of the other through mutation. This will then be used to
construct the mutation matrices inductively in \cref{lem:inductive_columns}. Here we
will need for the first time \cref{cond:lambda_star_to_the_d} to show that the
principal parts of the matrices are skew-symmetrizable.

As before, we will index matrices of size $N \times |X|$ by the set $X$ for subsets $X
	\subseteq \ex$. The set of such matrices with integer entries will be denoted by $M_{N
			\times X}(\bbZ)$.
\begin{lemma}\label{lem:inductive_step_btautau}
	Assume the setting of \cref{thm:gy_main_result}. Suppose that $\tau, \tau' \in \Xi_N$ are such that
	\begin{equation*}
		\tau' = (\tau(k), \tau(k+1))\tau = \tau(k, k+1)
	\end{equation*}
	%
	for some $k \in [1, N-1]$ such that $\eta(\tau(k)) = \eta(\tau(k+1))$ and $\tau(k) <
		\tau(k+1)$. Write $k_\bullet = \tau_\bullet(\tau(k))$, and let $\wt{\ex} \subseteq \ex$
	be a subset such that $k_\bullet \in \wt{\ex}$. Then there exists a matrix $\tB_{\tau}
		\in M_{N \times \wt{\ex}}(\bbZ)$ whose columns, $b^l_{\tau} \in \bbZ^N$ for $l \in
		\wt{\ex}$ satisfy
	\begin{equation}\label{eq:conditions_for_bltautau'}
		\begin{aligned}
			\chi_{M_\tau(b^l_{\tau})}             & = 1,                                \\
			\Omega_{\bbr_\tau}(b^l_{\tau}, e_l)^2 & = \lambda^*_l,                      \\
			\Omega_{\bbr_\tau}(b^l_{\tau}, e_j)   & = 1, \forall j \in [1, N], j\neq l,
		\end{aligned}
	\end{equation}
	%
	for all $l \in \wt{\ex}$ if and only if there exists a matrix $\tB_{\tau'}$ whose
	columns $b^l_{\tau'} \in \bbZ^N,\,l\in \wt{\ex}$ satisfy
	\begin{equation*}
		\begin{aligned}
			\chi_{M_{\tau'}(b^l_{{\tau'}})}             & = 1,                                \\
			\Omega_{\bbr_{\tau'}}(b^l_{{\tau'}}, e_l)^2 & = \lambda^*_l,                      \\
			\Omega_{\bbr_{\tau'}}(b^l_{{\tau'}}, e_j)   & = 1, \forall j \in [1, N], j\neq l,
		\end{aligned}
	\end{equation*}
	%
	for all $l \in \wt{\ex}$.

	For both implications the principal parts of the matrices $\tB_{\tau}$ and
	$\tB_{\tau'}$ are skew-symmetrizable. Furthermore, $\tB_{\tau'} =
		\mu_{k_\bullet}(\tB_{\tau})$, $\bbr_{\tau'} = \mu_{k_\bullet}(\bbr_{\tau})$ and
	\begin{equation*}
		b^{k_\bullet}_{\tau} = - b^{k_\bullet}_{\tau'} = e_{p(k_\bullet)} + e_{s(k_\bullet)} - g,
	\end{equation*}
	%
	where $g\in \bbZ_{\geq 0}^N$ is the vector from
	\cref{prop:mutation_adjacent_permutations}.
\end{lemma}
\begin{proof}

	We start with the first implication. The conditions of
	\cref{eq:conditions_for_bltautau'} imply that $(\bbr_\tau, \tB_{\tau})$ is a compatible
	pair. Indeed, if we write $t_{lj} = \Omega_{\bbr_\tau}(b^l_{\tau}, e_j)$ for $j\in[1,
			N],\, l \in \wt{\ex}$, then we see that $t_{lj} = 1$ for all $l \neq j$ and that
	$t_{ll}$ is not a root of unity, as $t_{ll}^2 = \lambda_l^*$, which is not a root of
	unity. Furthermore,
	\begin{align*}
		t_{ll}^{d_{\eta(k)}}  = (\lambda^*_l)^{d_{\eta(k)}} = (\lambda^*_k)^{d_{\eta(l)}} = t_{kk}^{d_{\eta(l)}}
	\end{align*}
	%
	by \cref{cond:lambda_star_to_the_d}, which shows that the principal part of
	$\tB_{\tau}$ is skew-symmetrizable by \cref{lem:principal_part_skew_symmetrizable}.

	Now, \cref{eq:conditions_for_bltautau'} and \cref{prop:mutation_adjacent_permutations}
	(b) together with the uniqueness from \cref{lem:unique_b} give
	\begin{equation*}
		e_{p(k_\bullet)} + e_{s(k_\bullet)} - g = b^{k_\bullet}_{\tau}.
	\end{equation*}
	%
	Recalling \cref{prop:formula_for_mutation} and that $g \in \bbZ_{\geq 0}^N$, we find
	\begin{align*}
		\mu_{k_\bullet}(M_\tau)(e_{k_\bullet})
		 & = M_\tau(-e_{k_\bullet} + [b^{k_\bullet}_{\tau}]_{+}) + M_\tau(-e_{k_\bullet} - [b^{k_\bullet}_{\tau}]_{-})                                       \\
		 & = M_\tau(-e_{k_\bullet} + [e_{p(k_\bullet)} + e_{s(k_\bullet)} - g]_{+}) + M_\tau(-e_{k_\bullet} - [e_{p(k_\bullet)} + e_{s(k_\bullet)} - g]_{-}) \\
		 & = M_\tau(-e_{k_\bullet} + e_{p(k_\bullet)} + e_{s(k_\bullet)}) + M_\tau(-e_{k_\bullet} + g)                                                       \\
		 & = M_{\tau'}(e_{k_\bullet}),
	\end{align*}
	such that $\mu_{k_\bullet}(M_\tau)(e_l) = M_{\tau'}(e_l)$ for all $l \in [1, N]$. Hence,
	\begin{equation*}
		\Omega_{\bbr_{\tau'}}(e_t, e_l)^2 M_{\tau'}(e_l)M_{\tau'}(e_t) = M_{\tau'}(e_t)M_{\tau'}(e_l) = \Omega_{\mu_{k_\bullet}(\bbr_{\tau})}(e_t, e_l)^2 M_{\tau'}(e_l)M_{\tau'}(e_t),
	\end{equation*}
	%
	for all $t, l \in [1, N]$. Consequently, $\Omega_{\bbr_{\tau'}}(e_t, e_l)^2 =
		\Omega_{\mu_{k_\bullet}(\bbr_\tau)}(e_t, e_l)^2$ for all $t, l \in [1, N]$ which gives
	$\Omega_{\bbr_{\tau'}}(e_t, e_l) = \Omega_{\mu_{k_\bullet}(\bbr_\tau)}(e_t, e_l)$ due
	to \cref{cond:no_order_two}. Thus, $\bbr_{\tau'} = \mu_{k_\bullet}(\bbr_{\tau})$, with
	which we can now conclude $M_{\tau'} = \mu_{k_\bullet}(M_\tau)$.
	\Cref{prop:mutation_preserves_good_things,lem:equivariance_mutations} now imply
	\cref{eq:conditions_for_bltautau'} for $\tB_{\tau'} = \mu_{k_\bullet}(\tB_{\tau})$.

	The proof for the other implication is analogous. The difference is that we now have to
	consider the case $\tau(k) > \tau(k+1)$ in \cref{prop:mutation_adjacent_permutations}
	(b). In this case we obtain
	\begin{equation*}
		\epsbullet - g = - b^{k_\bullet}_{\tau'},
	\end{equation*}
	and
	\begin{align*}
		\mu_{k_\bullet}(M_{\tau'})(e_{k_\bullet})
		 & = M_{\tau'}(-e_{k_\bullet} + [b^{k_\bullet}_{\tau'}]_{+}) + M_{\tau'}(-e_{k_\bullet} - [b^{k_\bullet}_{\tau'}]_{-})                                       \\
		 & = M_{\tau'}(-e_{k_\bullet} + [-e_{p(k_\bullet)} - e_{s(k_\bullet)} + g]_{+}) + M_{\tau'}(-e_{k_\bullet} - [-e_{p(k_\bullet)} - e_{s(k_\bullet)} + g]_{-}) \\
		 & = M_{\tau'}(-e_{k_\bullet} + g) + M_{\tau'}(-e_{k_\bullet} + e_{p(k_\bullet)} + e_{s(k_\bullet)})                                                         \\
		 & = M_{\tau}(e_{k_\bullet}).
	\end{align*}
	%
	The rest of the proof can then be taken over literally from the first case, by swapping
	$\tau$ and $\tau'$.

\end{proof}

We will first construct the matrices $\tB_\tau$ only for the elements $\tau \in
	\Gamma_N$\index{Gamma N@$\Gamma_N$}. Recall that the subset $\Gamma_N$ of $\Xi_N$,
consists of permutations of the form
\begin{equation*}
	\tau_{i, j} = [i+1, i+2, \dots, j, i , j+1, j+2, \dots, N, i-1, i-2, \dots, 1]
\end{equation*}
%
for $1 \leq i \leq j \leq N$. To do the induction, we make use of the following total
order on $\Gamma_N$:
\begin{multline*}
	\Gamma_N = \{\tau_{1,1} = \id \prec \tau_{1,2} \prec \cdots \prec \tau_{1, N} = \tau_{2,2} \prec \tau_{2,3} \prec \cdots \prec \tau_{2,N} = \tau_{3,3} \prec \cdots\\ \cdots \prec \tau_{N-1, N-2} \prec \tau_{N-1, N-1} \tau_{N-1, N} = \tau_{N, N} = w_\circ \},
\end{multline*}
%
where $w_\circ = [N, N-1, \dots, 1]$. We will write $\sigma \preceq \tau$ for $\sigma,
	\tau \in \Gamma_N$ to say that either $\sigma = \tau$ or $\sigma \prec \tau$.

If $\tau \prec \tau'$ are consecutive elements in the total order, we can write
\begin{equation*}
	\tau = \tau_{i,j-1} \text{ and } \tau' = \tau_{i,j}
\end{equation*}
%
for some $1 \leq i < j \leq N$. Expanding the definitions, we have
\begin{align*}
	\tau_{i, j-1} & = [i+1, i+2, \dots, j - 1, i , j, j+1, j+2, \dots, N, i-1, i-2, \dots, 1] \\
	\tau_{i, j}   & = [i+1, i+2, \dots,j-1,  j, i , j+1, j+2, \dots, N, i-1, i-2, \dots, 1],
\end{align*}
%
from which we see that
\begin{equation*}
	\tau' = \tau_{i,j} = (i, j)\tau_{i, j-1} = (i, j)\tau = \tau(j-i, j-i+1).
\end{equation*}
%
Thus, consecutive elements in the linear order are adjacent permutations. We can hence
view the elements of $\Gamma_N$ as a special instance of
\cref{lem:xi_n_characterization} applied to $w_\circ$. In \cref{fig:xi_6_graph}, the
elements of $\Gamma_6$ form the path from $\id$ to $w_\circ$ consisting of the leftmost
nodes.

To each $\tau \in \Gamma_N$ we associate a subset $\ex_\tau \subseteq \ex$\index{ex
	tau@$\ex_\tau$} in such a way that
\begin{equation*}
	\ex_{\id} = \emptyset, \quad \ex_{w_\circ} = \ex \quad
\end{equation*}
%
and $\ex_\sigma \subseteq \ex_\tau$ for all $\sigma, \tau \in \Gamma_N$ with $\sigma
	\prec \tau$. The subsets $\ex_\tau$ are defined inductively, as follows. The base case
is $\ex_{\id} \defeq \emptyset$. Now, suppose that $\tau \prec \tau'$ are two
consecutive elements, and write
\begin{equation*}
	\tau' = \tau_{i,j} = (i, j)\tau_{i, j-1} = (i, j)\tau = \tau(j-i, j-i+1),
\end{equation*}
%
as above. From $\ex_\tau$ we then construct $\ex_{\tau'}$ as
\begin{equation*}
	\ex_{\tau'} \defeq \begin{dcases*}
		\ex_\tau \cup \{p(j)\}, & if $p(i) = -\infty$ and $\eta(i) = \eta(j)$ \\
		\ex_\tau,               & otherwise.
	\end{dcases*}
\end{equation*}
%
Recall that $\ex = \{j \in [1, N] \mid s(j) \neq + \infty \} = \{p(j) \mid j \in [1,
		N],\, p(j) \neq -\infty\}$. It follows that $\ex_{w_\circ} = \ex$, as $\sigma \preceq
	w_\circ$ for all $\sigma\in \Gamma_N$.

\begin{lemma}\label{lem:inductive_columns}
	Assume the setting of \cref{thm:gy_main_result} for some $\tau \in \Gamma_N$. For all $\sigma \in \Gamma_N$ such that $\sigma \preceq \tau$, there exists a unique matrix $\tB_{\sigma, \tau}\in M_{N \times \ex_\tau} (\bbZ)$ whose columns, $b^l_{\sigma, \tau} \in \bbZ^N$ for $l\in \ex_\tau$, satisfy
	\begin{equation}\label{eq:conditions_for_blsigmatau}
		\begin{aligned}
			\chi_{M_\sigma(b^l_{\sigma, \tau})}            & = 1,                                \\
			\Omega_{\bbr_\sigma}(b^l_{\sigma,\tau}, e_l)^2 & = \lambda^*_l,                      \\
			\Omega_{\bbr_\sigma}(b^l_{\sigma,\tau}, e_j)   & = 1, \forall j \in [1, N], j\neq l,
		\end{aligned}
	\end{equation}
	%
	for all $l \in \ex_\tau$. The principal part of the matrix $\tB_{\sigma, \tau}$ is
	skew-symmetrizable via the integers $\{d_{\eta(k)} \mid k \in \ex_\tau\}$.
\end{lemma}
\begin{proof}
	The uniqueness statement is handled by \cref{lem:unique_b}. The principal part of $\tB_{\sigma, \tau}$ is skew-symmetrizable by the same argument as in the proof of \cref{lem:inductive_step_btautau}.

	It now remains to prove the existence statement. For $\tau = \id$, we have $\ex_{\id} =
		\emptyset$, and there is nothing to prove. We will now proceed by induction on the
	total ordering of $\Gamma_N$.

	Let $\tau \prec \tau'$ be two consecutive elements of $\Gamma_N$, and assume that the
	existence statement holds for $\tau$. We will now show that it holds for $\tau'$ as
	well. Recall that we can write $\tau = \tau_{i, j-1}$ and $\tau' = \tau_{i, j}$ for
	some $1 \leq i < j \leq N$. Furthermore, $\tau' = (i, j)\tau = \tau(j-i, j-i+1)$ with
	$\tau(j-i) = i < j = \tau(j - i +1)$ such that
	\cref{prop:mutation_adjacent_permutations} is applicable with $k = j - i$.

	If $\eta(i) \neq \eta(j)$, then the existence follows easily. Indeed, $\ex_{\tau'} =
		\ex_\tau$ and, by \cref{prop:mutation_adjacent_permutations}, $M_{\tau'} = M_\tau$,
	such that also $\Omega_{\bbr_{\tau'}} = \Omega_{\bbr_\tau}$. So, we can take
	$\tB_{\sigma, \tau'} \defeq \tB_{\sigma, \tau}$ for $\sigma \preceq \tau$ and
	$\tB_{\tau', \tau'} \defeq \tB_{\tau, \tau}$.

	If $\eta(i) = \eta(j)$, there is more work. Since $i < j$, we can write $j = s^m(i)$
	for some $m \in \bbZ_{\geq 0}$. Then note that
	\begin{equation*}
		\tau([1, j-i]) \cap \eta\inv(\eta(i)) = \{i+1, \dots, j-1, i\} \cap \eta\inv(\eta(i))= \{i, s(i), \dots, s^{m- 1}(i)\},
	\end{equation*}
	%
	so that $\tau_\bullet(\tau(j-i))$ must be the $m$-th element of $\eta\inv(\eta(i))$
	when the elements are ordered from least to greatest. Thus,
	\begin{equation*}
		\tau_\bullet (\tau(j- i)) = s^{m-1}p^{O_{-}(i)}(i),
	\end{equation*}
	because $p^{O_{-}(i)}(i)$ is the smallest element of $\eta\inv(\eta(i))$, by definition of $O_{-}(i)$. Set, as in \cref{prop:mutation_adjacent_permutations}, $k_\bullet = \tau_\bullet(\tau(j-i)) = \tau_\bullet(\tau(k))$. We now have two subcases.

	First, assume that $p(i) \neq -\infty$. Then, $\ex_{\tau'} = \ex_{\tau}$, and we can
	take $\tB_{\sigma, \tau'} \defeq \tB_{\sigma, \tau}$ for $\sigma \in \Gamma_N$ such
	that $\sigma \preceq \tau$. By \cref{lem:inductive_step_btautau} we can take
	$\tB_{\tau', \tau'} \defeq \mu_{k_\bullet}(\tB_{\tau, \tau'})$.

	In the other subcase, where $p(i) = -\infty$, we have $\ex_{\tau'} = \ex_\tau \cup
		\{k_\bullet\}$, because
	\begin{equation*}
		k_\bullet = s^{m-1}p^{O_{-}(i)}(i) = s^{m-1}(i) = p(j).
	\end{equation*}
	%
	We now need to create a new column. We take $b^{k_\bullet}_{\tau, \tau'} \defeq
		e_{p(k_\bullet)} + e_{s(k_\bullet)} - g$, where $g \in \bbZ_{\geq 0}^N$ is again the
	vector from \cref{prop:mutation_adjacent_permutations}. This column satisfies
	\cref{eq:conditions_for_blsigmatau}, precisely because of
	\cref{prop:mutation_adjacent_permutations}. By the inductive hypothesis, the columns
	$b^l_{\tau, \tau}$ of $\tB_{\tau, \tau}$ satisfy \cref{eq:conditions_for_blsigmatau}.
	So, we can take $\tB_{\tau, \tau'}$ as the matrix with columns
	\begin{equation*}
		b^l_{\tau, \tau'} \defeq \begin{dcases*}
			b^l_{\tau, \tau},                        & if $l \neq k_\bullet$ \\
			e_{p(k_\bullet)} + e_{s(k_\bullet)} - g, & if $l = k_\bullet$.
		\end{dcases*}
	\end{equation*}
	%
	By \cref{lem:inductive_step_btautau}, we can then take $\tB_{\tau', \tau'} \defeq
		\mu_{k_\bullet}(\tB_{\tau, \tau'})$.

	So, it remains to construct $\tB_{\sigma, \tau'}$ for $\sigma \in \Gamma_N$ such that
	$\sigma \prec \tau$. To do this, we apply our induction in reverse. Take $\sigma \prec
		\sigma' \preceq \tau$ with $\sigma, \sigma' \in \Gamma_N$ two consecutive elements.
	Then, as before,
	\begin{equation*}
		\sigma = \tau_{i',j' -1} \text{ and } \sigma' = \tau_{i', j'}
	\end{equation*}
	for some $1 \leq i'< j' \leq N$. Write $k_\bullet' = \sigma_\bullet(\sigma(j' - i'))$. Now assume that there exists a matrix $\tB_{\sigma', \tau'} \in M_{N \times \ex_{\tau'}}(\bbZ)$ satisfying \cref{eq:conditions_for_blsigmatau}, and define
	\begin{equation*}
		\tB_{\sigma, \tau'} \defeq \begin{dcases*}
			\tB_{\sigma', \tau'},                   & if $\eta(i') \neq \eta(j')$ \\
			\mu_{k_\bullet'}(\tB_{\sigma', \tau'}), & if $\eta(i') = \eta(j')$.
		\end{dcases*}
	\end{equation*}
	%
	Applying \cref{lem:inductive_step_btautau} once more, we conclude that $\tB_{\sigma,
			\tau'}$ satisfies \cref{eq:conditions_for_blsigmatau}.

\end{proof}

\subsection{Proof of parts (a), (b) and (c) of the main result}

We now have everything in place for the proof of parts (a), (b) and (c). We first
remark that \cref{lem:inductive_columns} establishes parts (a) and (b) of
\cref{thm:gy_main_result} for $\tau \in \Gamma$. Indeed, it suffices to take $(\sigma,
	\tau) = (\tau, w_\circ)$ and set $\tB_\tau \defeq \tB_{\tau, w_\circ}$, because
$\ex_{w_\circ} = \ex$. In particular, because $\id \in \Gamma_N$, we have constructed
the mutation matrix $\tB = \tB_{\id}$ for the initial toric frame $M = M_{\id}$.

The proof of parts (a), (b) and (c) of \cref{thm:gy_main_result} are now just a matter
of putting everything together.
\begin{proof}[Proof of \cref{thm:gy_main_result} (a), (b) and (c)]
	We prove part (a) by induction. The uniqueness follows from \cref{lem:unique_b}. Fix $\tau \in \Xi_N$. By \cref{lem:xi_n_characterization}, we can find a sequence $\tau_0 = \id, \tau_1, \dots, \tau_n = \tau \in \Xi_N$ such that for all $l \in [1, n]$ we can write
	\begin{equation*}
		\tau_l = (\tau_{l-1}(k_l), \tau_{l-1}(k_l + 1))\tau_{l-1} = \tau_{l-1}(k_l, k_l + 1)
	\end{equation*}
	%
	for some $k_l \in [1, N-1]$ such that $\tau_{l-1}(k_l) < \tau_{l-1}(k_l + 1)$. As
	remarked above, the existence of $\tB_{\id}$ follows from \cref{lem:inductive_columns}.
	Then, for $l \in [1, n]$, if $\eta(\tau_{l-1}(k_l)) \neq \eta(\tau_l(k_l))$,
	\cref{prop:mutation_adjacent_permutations} (a) yields $M_{\tau_l} = M_{\tau_{l-1}}$,
	and we can choose $\tB_{\tau_l} = \tB_{\tau_{l-1}}$. Otherwise, if
	$\eta(\tau_{l-1}(k_l)) = \eta(\tau_l(k_l))$, we can apply
	\cref{lem:inductive_step_btautau} for $\tau_{l-1}$ and $\tau_{l}$. In this case
	$\tB_{\tau_l} = \mu_{(k_l)_\bullet}(\tB_{\tau_{l-1}})$, where $(k_l)_\bullet =
		(\tau_{k_l})_\bullet(\tau_{k_l}(k_l))$.

	Part (b) follows as in the proofs of
	\cref{lem:inductive_columns,lem:inductive_step_btautau} from
	\cref{lem:principal_part_skew_symmetrizable}.

	For part (c), the one-step mutation statement follows from
	\cref{prop:mutation_adjacent_permutations} (a) if $\eta(\tau(k)) \neq \eta(\tau(k +
			1))$. The other case, $\eta(\tau(k)) = \eta(\tau(k+1))$, is covered by
	\cref{lem:inductive_step_btautau}, swapping the roles of $\tau$ and $\tau'$ if needed.
	Finally, since mutation is involutive, every $\tau \in \Xi_N$ can be obtained by a
	sequence of one-step mutations from $\id\in \Xi_N$ due to
	\cref{lem:xi_n_characterization} (a), and the uniqueness of part (a), we obtain that
	all the quantum seeds associated to $\Xi_N$ are mutation-equivalent to each other.
\end{proof}

\section{The upper cluster algebra}\label{sec:upper_cluster_algebra}

The goal of this final section is to prove equality between the symmetric CGL extension
$R$, the quantum cluster algebra, and the upper quantum cluster algebra. Let $E_\tau$
be the multiplicative subset of $R$ generated by $\bbK^\times$ and $M_\tau(e_l)$ for $l
	\in \ex$. We will show that this is an Ore set. The idea is to construct the following
chain of inclusions:
\begin{equation*}
	R \subseteq \mcA(M, \tB, \emptyset)_\bbK \subseteq \mcU(M, \tB, \emptyset) \subseteq \bigcap_{\tau \in \Gamma_N} R[E_{\tau}\inv] \subseteq R.
\end{equation*}

The first inclusion will be shown by proving that for each $j \in [1, N]$, the
generator $x_j \in R$ is a cluster variable for some toric frame $M_\tau$. The second
inclusion is just the quantum Laurent phenomenon (cf. \cref{thm:quantum_laurent}). The
hardest inclusion is the last one. For this we will need to study the intersections of
the Ore localizations by the homogeneous prime elements more carefully. The first step
to proving this inclusion will be \cref{thm:minimal_denominators}. The inclusion is
then proven in \cref{thm:intersections} (d) using an inductive argument based on the
total order on $\Gamma_N$.

\subsection{Ore localizations of CGL extensions}\label{sec:ore_localizations}

We first focus on what happens to the intersection of the localizations of the two
sequences of prime elements in the setting of \cref{thm:y_prime_swapped_cgl}. The main
goal is to prove \cref{thm:minimal_denominators}. This will be done by a careful
analysis of the denominators that can appear.

\begin{lemma}\label{lem:ore_set_ore_extension}
	%
	Let $B[x;\sigma,\delta]$ be an Ore extension and $E$ a (left or right) Ore set in $B$.
	If $\sigma(\bbK^\times E) = \bbK^\times E$, then $E$ is a (left or right) Ore set in
	$B[x;\sigma, \delta]$.
\end{lemma}
\begin{proof}
	%
	We first show that the elements of $E$ are still regular in $B[x; \sigma, \delta]$.
	Indeed, take some $\sum_{i} b_i x^i \in B[x; \sigma, \delta]$ and $e \in E$. Then,
	since the elements $x^i$ form a basis, we have that $e \sum_i b_i x^i = 0$ if and only
	if $e b_i = 0$ for all $i$. Because $e$ is regular, it follows that $b_i = 0$ for all
	$i$, and hence $\sum_i b_i x^i = 0$.

	Take $e \in E$. We only prove the case where $E$ is a right Ore set, as the case for a
	left Ore set is completely analogous. We first show that there exist $e' \in E$ and $r
		\in R = B[x; \sigma, \delta]$ such that $er = x e'$. Because $E$ is a right Ore set of
	$B$, there exist $f\in E$ and $b \in B$ such that
	\begin{equation*}
		e b = \delta(\sigma\inv(e))f.
	\end{equation*}
	Because $\sigma\inv(e) \in \bbK^\times E$ by assumption, there exists some $\xi \in \bbK^\times$ such that $\xi \sigma\inv(e) \in E$.
	Define
	\begin{equation*}
		e' \defeq \xi \sigma\inv(e)f \in E.
	\end{equation*}
	Then
	\begin{align*}
		xe' & = x\xi\sigma\inv(e)f                                     \\
		    & = \xi (\sigma(\sigma\inv(e)f)x + \delta(\sigma\inv(e)f)) \\
		    & = \xi(e\sigma(f)x + e \delta(f) + e b)                   \\
		    & = e(\xi (\sigma(f)x + \delta(f) + b)) \in eR.
	\end{align*}

	Now, assume that $r,s \in R$ are such that $e R \cap r E \neq \emptyset$ and $e R \cap
		s E \neq \emptyset$ for all $e \in E$. Then, also $e R \cap rs E \neq \emptyset$ for
	all $e\in E$. Indeed, for $e \in E$ we can find $a \in R$ and $f \in E$ such that $ea =
		r f$, and $b \in R$ and $g \in E$ such that $f b = s g$, and then
	\begin{equation*}
		e a b = r f b = r s g \in rs E \cap e R.
	\end{equation*}

	The statement now follows by iteratively applying this fact on an element $\sum b_i x^i
		\in R$.
\end{proof}

We now apply this lemma to a CGL extension $R$. Let $y_1, \dots, y_N$ be the sequence
of homogeneous prime elements from \cref{thm:homogeneous_primes}. We now claim that for
each $j \in [1, K]$, the set $E_j \defeq \bbK^\times\{y_j^{m} \mid m \in \bbZ_{\geq
		0}\}$ is an Ore set in $R$. Indeed, first note that for any $m \in \bbZ_{\geq 0}$ and
$a \in R_j$, we have
\begin{equation*}
	y_j^k R_j \cap a E_j = R_j y_j^k \cap  a E_j \ni a y_j^k.
\end{equation*}
%
This shows that $E_j$ is an Ore set in $R_j$. Furthermore, $\sigma(\bbK^\times E_j) =
	\bbK^\times E_j$ because $y_j$ is homogeneous. Hence, by
\cref{lem:ore_set_ore_extension}, we find that $E_j$ is also an Ore set in $R_{j + 1}$.
By repeatedly applying \cref{lem:ore_set_ore_extension} we find that $E_j$ is an Ore
set in $R$. Now, take $I \subseteq [1, N]$ and define
\begin{equation*}
	E_I \defeq \bbK^\times \prod_{j \in I}\{y_j^m \mid m \in \bbZ_{\geq 0}\}.
\end{equation*}
\index{E I@$E_I$}%%
%
By \cref{eq:y_quasi_commute}, it is a multiplicative set. It is also an Ore set by a
similar argument as in the proof of \cref{lem:ore_set_ore_extension}. Indeed, if $e \in
	E$ and $f \in F$ for two Ore sets $E$ and $F$, then for every $x \in R$ the set $ef R
	\cap x E F$ is non-empty. Using that $E$ and $F$ are Ore sets, take $y, z \in R, e' \in
	E$ and $f' \in F$ such that $ey = xe'$ and $fz = yf'$. Then $xe'f' = eyf' = efz \in efR
	\cap xEF$.

We will use the shorthand $E = E_{[1,N]}$. Write $a \mid_l b$\index{divides
	left$\mid_l$} if $a$ divides $b$ on the left, i.e., $b = ar$ for some $r \in R$. Call
an element $y_1^{m_1}\cdots y_N^{m_N}$ a \emph{minimal denominator}\index{minimal
	denominator} of a nonzero element $v\in R[E\inv]$ if
\begin{equation*}
	v = y_1^{-m_1}\cdots y_N^{-m_N} s
\end{equation*}
%
for some $s \in R$ such that $y_j \nmid_l s$ for all $j\in [1,N]$ with $m_j > 0$.
Intuitively, this means that we can not cancel any terms.

In what follows, we assume the setting of
\cref{thm:y_prime_swapped_cgl}~\ref*{itm:eta_k_is_eta_k_plus_one}. We then define for
all $I \subseteq [1, N]$ the analogous Ore sets,
\begin{equation*}
	E'_{I} := \bbK^\times \prod_{j \in I}\{(y'_j)^m \mid m \in \bbZ_{\geq 0}\};
\end{equation*}
%
and write $E' = E'_{[1, N]}$. Because $y'_j$ is a scalar multiple of $y_j$ for all $j
	\neq k$, we have that $E'_I = E_I$ if $k \notin I'$. We now state the theorem that we
want to prove.

\begin{theorem}\label{thm:minimal_denominators}
	Assume the setting of \cref{thm:y_prime_swapped_cgl}~\ref*{itm:eta_k_is_eta_k_plus_one}. Let
	\begin{equation*}
		y_1^{m_1}\cdots y_N^{m_N} \quad \text{and} \quad y_1^{m'_1} \cdots y_{k-1}^{m'_{k-1}}(y'_k)^{m'_k}y_{k+1}^{m'_{k+1}} \cdots y_N^{m'_N}
	\end{equation*}
	%
	be two minimal denominators of a nonzero element $v \in R[E\inv] \cap R[(E')\inv]$
	(with respect to both $R[E\inv]$ and $R[(E')\inv]$). Then
	\begin{equation*}
		m_k = m'_k = 0 \quad \text{and} \quad m_j = m'_j,\quad \forall j \in [1, N], j \neq k.
	\end{equation*}
	In particular,
	\begin{equation*}
		R[(E_I)\inv] \cap R[(E'_{I'})\inv] = R[(E_I \cap E'_{I'})\inv] = R[(E_{(I \cap I')\setminus \{k\}})\inv]
	\end{equation*}
	for all $I,I' \subseteq [1, N]$.
\end{theorem}

Note that since $E_I \cap E'_{I'} \subseteq E_I, E'_{I'}$ we always have
\begin{equation*}
	R[(E_I)\inv] \cap R[(E'_{I'})\inv] \supseteq R[(E_I \cap E'_{I'})\inv].
\end{equation*}
%
The other inclusion follows from the first part of the theorem. The last equality of
the theorem follows from the following lemma.
\begin{lemma}
	For all $I, I' \subseteq [1, N]$,
	\begin{equation*}
		E_I \cap E'_I = E_{(I \cap I')\setminus \{k\}} = E'_{(I \cap I') \setminus \{k\}}.
	\end{equation*}
\end{lemma}
\begin{proof}
	%
	The inclusions $E_{(I \cap I')\setminus \{k\}}, E'_{(I \cap I') \setminus \{k\}}
		\subseteq E_I \cap E'_{I'}$ are immediate. Take $e \in E_I \cap E'_{I'}$, and write
	\begin{equation*}
		e = \beta \prod_{j=1}^N y_j^{m_j} = \beta' \prod_{j=1}^N (y'_j)^{m'_j}
	\end{equation*}
	%
	for some $\beta, \beta' \in \bbK^\times$ and $m_j, m'_j\in \bbZ_{\geq 0}$ such that
	$m_j = 0$ for $j \notin I$ and $m'_j = 0$ for $j \notin I'$. It now remains to show
	\begin{equation*}
		m_k = m'_k = 0 \quad \text{and}\quad m_j = m'_j, \quad \forall j \in [1, N], j\neq k.
	\end{equation*}
	%

	By \cref{thm:normal_in_UFD} we must have $m_N = m'_N$, as $y_N$ and $y'_N$ are prime
	elements and associates in $R$, but do not divide $y_1, \dots, y_{N-1}$. So, we may
	assume that $m_N = m'_N = 0$, by replacing $e$ with $e y_N^{-m_N}$ and multiplying
	$\beta'$ by an appropriate scalar. Applying this reduction repeatedly, we reduce to the
	case where $m_j = m'_j = 0$ for all $j \in [k+1, N]$.

	We must now get rid of the ``obstacles'', $y_k$ and $y'_k$. Write, using
	\cref{thm:y_prime_swapped_cgl},
	\begin{equation*}
		y_k y'_k - \alpha_{kp(k)}y_{p(k)}y_{k+1} = u \in R_{k-1}.
	\end{equation*}
	%
	Assume that $m_k > 0$. Then,
	\begin{equation*}
		e y_k' = \beta \left(\prod_{j \in [1, k-1]}y_j^{m_j}y_k^{m_k-1}\right)(u+\alpha_{kp(k)}y_{p(k)}y_{k+1}).
	\end{equation*}
	%
	In this expression, only $y_{k+1} \in R_{k+1}$, and it follows that $ey'_k$ has degree
	1 with respect to $x_{k+1}$. On the other hand, we can also write
	\begin{equation*}
		ey'_k = \beta'\left(\prod_{j \in [1, k-1]}(y'_j)^{m'_j}\right)(y'_k)^{m'_k + 1},
	\end{equation*}
	where $ey'_k$ has degree $m'_k + 1$ with respect to $x_{k+1}$. So, we must have $m'_k = 0$ and consequently
	\begin{equation*}
		e = \beta' \prod_{j\in [1, k-1]}(y'_j)^{m'_j} \in R_{k-1}.
	\end{equation*}
	This contradicts the assumption that $m_k > 0$. Hence, $m_k = 0$ and by symmetry $m'_k = 0$. We can then continue as above to conclude that also $m_j = m'_j$ for all $j \in [1, k-1]$, which is what we needed to show.
\end{proof}

We now state and prove 3 lemmas that we will need for the proof of
\cref{thm:minimal_denominators}.

\begin{lemma}\label{lem:prime_in_ore_localization}
	%
	Let $R$ be a $\bbK$-algebra that is a domain and $E$ a left or right Ore set in $R$.
	Let $p \in R$ be a prime element that is normal in $\bbK^\times E$ and such that $Rp
		\cap E = \emptyset$. Then $p$ is a prime element of $R[E\inv]$. Furthermore, if $s \in
		R$ and $p \nmid s$ as elements of $R$, then $p \nmid s$ as elements of $R[E\inv]$.
\end{lemma}
\begin{proof}
	%
	Take $e \in E$. By normality of $p$ in $\bbK^\times E$, we can write $pe = \alpha f p$
	and $ep = p \beta g$ for some $\alpha, \beta \in \bbK^\times$ and $f,g \in E$. Then $p
		e \inv = \alpha\inv f\inv p$ and $e\inv p = p \beta\inv g \inv$. Since $p$ is prime it
	is also normal in $R$, and we obtain that $p$ is normal in $R[E\inv]$.

	To see that it is prime, we go for the brute-force approach. Take $xe\inv, yf\inv \in
		R[E\inv]$ such that their product lies in $pR[E\inv]$. We want to show that either
	$xe\inv$ or $yf\inv$ must lie in $pR[E\inv]$. We can write
	\begin{equation*}
		xe\inv yf\inv = p z g\inv
	\end{equation*}
	%
	for some $z \in R$ and $g \in E$. Using that $E$ is an Ore set we can write
	\begin{equation*}
		x e\inv y f\inv = x y' (e')\inv f\inv = xy' (fe')\inv = p z g\inv.
	\end{equation*}
	%
	Using \cref{lem:ore_set_properties}, we find that the above is equivalent to the
	existence of $a,b \in R$ such that
	\begin{equation*}
		xy'a = pzb \quad \text{and} \quad fe'a = gb \in E.
	\end{equation*}
	%
	Since $p$ is a prime element of $R$, we must have that either $x,y'$ or $a$ is an
	element of $Rp$. If $x \in Rp$ then $xe\inv \in pR[E\inv]$. If $y' \in Rp$, then
	\begin{equation*}
		ye' = ey' \in Rp,
	\end{equation*}
	%
	implies $y \in Rp$ as $Rp \cap E = \emptyset$ by assumption. Thus, $y f\inv \in
		pR[E\inv]$. Finally, $a \in Rp$ is impossible as
	\begin{equation*}
		fe'a = gb \in E \cap Rp
	\end{equation*}
	gives a contradiction.

	For the last statement, take some $pxe\inv \in R[E\inv]p \cap R$, with $x \in R$ and $e
		\in E$. Then $pxe\inv = y$ for some $y \in R$, and hence $px = ye$. So, since $p$ is
	prime in $Rp$, we must have $y \in Rp$ or $e\in Rp$. By assumption, $Rp \cap E =
		\emptyset$, so $y \in Rp$ which shows that $R[E\inv] \cap R \subseteq Rp$ since the
	other inclusion is immediate. Now, note that if $s\notin Rp$ for some $s\in R$, then if
	$s \in R[E\inv]p$ we would have $s \in R[E\inv]p \cap R \subseteq Rp$, a contradiction.
\end{proof}

Let us write
\begin{equation*}
	s = \sum_{l_j, \dots, l_N \in \bbZ_{\geq 0}} s_{l_j,\ldots,l_N}x_j^{l_j} \cdots x_N^{l_N}
\end{equation*}
for $s \in R$ and $j \in [1, N]$ where each $s_{l_j, \dots, l_N} \in R_{j-1}$.

\begin{lemma}\label{lem:y_divides_ys}
	If
	\begin{equation*}
		y_j \mid_l y_1^{n_1}\cdots y_{j-1}^{n_j-1}s
	\end{equation*}
	for some $j \in [1, N], s\in R$ and $n_1,\dots,n_{j-1}\in \bbZ_{\geq 0}$, then $y_j \mid_l s$.
\end{lemma}
\begin{proof}
	%
	By assumption, $y_j s' = y_1^{n_1}\cdots y_{j-1}^{n_j - 1}s$ for some $s' \in R$. Since
	the set
	\begin{equation*}
		\{x_j^{l_{j+1}}\cdots x_N^{l_N} \mid l_{j+1}, \dots, l_N \in \bbZ_{\geq 0}\},
	\end{equation*}
	forms a basis for $R_{N}$ as an $R_j$-module, we must have
	\begin{equation*}
		y_j \mid_l y_1^{n_1}\cdots y_{j-1}^{n_j -1} s_{l_{j+1}, \dots, l_N}
	\end{equation*}
	%
	for all $l_{j+1}, \dots, l_N \in \bbZ_{\geq 0}$. Then, because $y_j \nmid_l y_1, \dots,
		y_{j-1}$, and $y_j$ is a prime element of $R_j$, we must have
	\begin{equation*}
		y_j \mid_l s_{l_{j+1}, \ldots, l_N}
	\end{equation*}
	for all $l_{j+1}, \dots, l_N \in \bbZ_{\geq 0}$. Hence, also $y_j \mid_l s$.
\end{proof}

\begin{lemma}\label{lem:y_divides_sy_prime}
	%
	If $y_k \mid_l s (y'_k)^n$ for some $s \in R_{k+1}$ and $n \in \bbZ_{\geq 0}$, then
	$y_k \mid_l s$.
\end{lemma}
\begin{proof}
	%
	Using a similar argument as in the previous lemma, we find that $y_k \mid_l s$ is
	equivalent to $y_k \mid s_l$ for all $l \in \bbZ_{\geq 0}$, where $s = \sum_{l \in
			\bbZ_{\geq 0 }} s_l x^{k+l}$ for $s_l \in R_k$. Write
	\begin{equation*}
		s' = \sum \{s_l x_{k+1}^l \mid l \in \bbZ_{\geq 0}, y_k \mid s_l\}.
	\end{equation*}
	%
	Then $y_k \mid_l s'$, and $y_k \mid_l s$ if and only if $s = s'$. Assume that $s \neq
		s'$. Since $y_k \mid_l s (y'_k)^n$ and $y_k \mid_l s' (y'_k)^n$, we have that
	\begin{equation*}
		y_k \mid_l (s - s') (y'_k)^n.
	\end{equation*}
	Writing
	\begin{equation*}
		s - s' = s_L x^L_{k+1} + \sum_{l=0}^{L-1}s_l x_{k+1}^l
	\end{equation*}
	%
	for some $L \in \bbZ_{\geq 0}$ with $s_L \neq 0$, we have $y_k \mid_l s_L$. The highest
	degree term of $(s-s')(y'_k)^n$ with respect to $x_{k+1}$ is given by
	\begin{equation*}
		\xi s_L y_{p(k)}^n x_{k+1}^{L+n}
	\end{equation*}
	%
	for some $\xi \in \bbK^\times$. Like in the previous lemma, we then must have $y_k \mid
		s_L y^n_{p(k)}$, but this contradicts $y_k$ being a prime element of $R_k$ which does
	not divide $s_L$ or $y_{p(k)}$.
\end{proof}

\begin{proof}[Proof of \cref{thm:minimal_denominators}]
	%
	By assumption, we have
	\begin{equation*}
		v = y_1^{-m_1}\cdots y_N^{-m_N} s = y_1^{-m_1'} \cdots y_{k-1}^{-m_{k-1}'}(y'_k)^{-m'_k}y_{k+1}^{-m_{k+1}'}\cdots y_N^{-m'_N}s'
	\end{equation*}
	%
	for some $s, s' \in R$. Take $i\in [k+1, N]$ maximal such that $m_i \neq m'_i$. Without
	loss of generality, we may assume that $m'_i > m_i$. Then we can write
	\begin{equation*}
		y_i^{m'_i - m_i}\left(\prod_{j\in [1, i-1] \setminus \{k\}}y_j^{m'_j}\right)s = \xi \left(\prod_{j = 1}^{i-1}y_j^{m_i}\right)(y'_k)^{-m'_k} s',
	\end{equation*}
	%
	for some $\xi \in \bbK^\times$, making use of \cref{eq:y_quasi_commute}. Now, $y_i$ is
	a prime element of $R_i$ which does not divide $y_1, \dots, y_{i-1}$. By
	\cref{lem:prime_in_ore_localization}, we find that $y_i$ is prime in $R_i[(y'_k)\inv]$
	and that it also doesn't divide $y_1, \dots, y_{i-1}$ in $R_i[(y'_k)\inv]$. By
	comparing the coefficients of $x_{i+1}^{l_{i+1}}\cdots x_N^{l_N}$, we find
	\begin{equation*}
		y_i^{m'_i - m_i}\left(\prod_{j\in [1, i-1] \setminus \{k\}}y_j^{m'_j}\right)s_{l_{i+1},\dots, l_N} = \xi \left(\prod_{j = 1}^{i-1}y_j^{m_i}\right)(y'_k)^{-m'_k} s'_{l_{i+1}, \dots, l_N} \in R_i.
	\end{equation*}
	%
	Thus, we must have, for all $l_{i+1}, \dots, l_N \in \bbZ_{\geq 0}$, that $y_i \mid
		s'_{l_{i+1}, \dots, l_N}$ in $R_i[(y'_k)\inv]$ and hence also in $R_i$ due to
	\cref{lem:prime_in_ore_localization}. Consequently, $y_i \mid_l s'$, which contradicts
	the minimality of the denominators.

	We now need to prove that $m_k = m'_k = 0$. Assume that $m_k > 0$. Then, as above, we
	obtain that
	\begin{equation*}
		\left(\prod_{j=1}^{k-1}y_j^{m'_j}\right)s_{l_{k+2}, \dots, l_N} = \xi y_k^{m_k}\left(\prod_{j=1}^{k-1}y_j^{m_j}\right)(y'_k)^{-m_k'}s'_{l_{k+2}, \dots, l_N} \in R_{k+1},
	\end{equation*}
	%
	for all $l_{k+2}, \dots, l_N \in \bbZ_{\geq 0}$, for some $\xi \in \bbK^\times$. Write
	\begin{equation*}
		(y'_k)^{-m'_s}s'_{l_{k+2}\dots, l_N} = s''_{l_{k+2}\dots, l_N}(y'_k)^{-m''_k},
	\end{equation*}
	%
	for some $s''_{l_{k+2}, \dots, l_N} \in R_{k+1}$ and $m''_k \in \bbZ_{\geq 0}$ using
	the fact that $\{(y'_k)^m \mid m \in \bbZ_{\geq 0}\}$ is an Ore set in $R_{k+1}$ by
	\cref{lem:ore_set_ore_extension}. Then,
	\begin{equation*}
		y_k \mid_l \left(\prod_{j=1}^{k-1}y_j^{m'_j}\right)s_{l_{k+2}, \dots, l_N}(y'_k)^{m''_k}.
	\end{equation*}
	%
	By \cref{lem:y_divides_ys}, we find that $y_k \mid_l s_{l_{k+2}, \dots
				l_N}(y'_k)^{m''_k}$. Hence, $y_k \mid_l s_{l_{k+2}, \dots, l_N}$ by
	\cref{lem:y_divides_sy_prime}. Since this holds for all $l_{k+2}, \dots, l_N \in
		\bbZ_{\geq 0}$, we find that $y_k \mid_l s$, which contradicts the minimality of the
	denominators. Thus, $m_k = 0$, and by symmetry also $m'_k = 0$.

	In the same way as we showed that $m_i = m_i'$ for all $i \in [k+1, N]$, one shows that
	$m_i = m'_i$ for all $i \in [1, k-1]$.
\end{proof}

\subsection{Proof of parts (d) and (e) of the main result}

Let, in what follows, $R$ be a symmetric CGL extension of length $N$, and fix a
function $\eta \colon [1, N] \to \bbZ$ satisfying the assumptions of
\cref{thm:homogeneous_primes}. Then, for each $\tau \in \Xi_N$, we have a CGL extension
presentation of the form
\begin{equation*}
	R = \bbK[x_{\tau(1)}][x_{\tau(2)}; \sigma''_{\tau(2)}, \delta''_{\tau(2)}] \cdots [x_{\tau(N)}; \sigma''_{\tau(N)}, \delta''_{\tau(N)}].
\end{equation*}
%
By \cref{prop:eta_invariance} we may choose $\eta_\tau = \eta\tau$ as the
$\eta$-function corresponding to this presentation. Write $p_\tau$ and $s_\tau$ for the
predecessor and successor functions corresponding to $\eta_\tau$ and let $y_{\tau, 1},
	\dots, y_{\tau, N}$ be the sequence of homogeneous prime elements of
\cref{thm:homogeneous_primes} for this presentation. Finally, denote
\begin{align*}
	\mcA_\tau & \defeq \text{ the $\bbK$-subalgebra of $R$ generated by } \{y_{\tau, k} \mid k \in [1, N]\}                                                   \\
	\mcT_\tau & \defeq \text{ the $\bbK$-subalgebra of $\Fract(R)$ generated by } \{y_{\tau, k}^{\pm 1} \mid k \in [1, N]\}                                   \\
	E_\tau    & \defeq \text{ the multiplicative subset of $\mcA_\tau$ generated by } \bbK \sqcup \{y_{\tau, k} \mid k \in [1, N], s_\tau(k) \neq + \infty\}.
\end{align*}
\index{A tau@$\mcA_\tau$}\index{T tau@$\mcT_\tau$}\index{E tau@$E_\tau$%}

Note that $\mcT_\tau$ is a quantum torus because of \cref{eq:y_quasi_commute}.
Consequently, $E_\tau$ consists of normal elements in $\mcA_\tau$, and is thus an Ore
set in $\mcA_\tau$, so that $\mcA_\tau[E\inv_\tau]$ makes sense to write down.

The following lemma ensures that every element $j \in \ex$ gets mutated when
considering only the elements of $\Gamma_N$. The first part of the lemma will be used
to describe the set $E_\tau$ in terms of the cluster variables of the toric frame
$M_\tau$.

\begin{lemma}\label{lem:tau_bullet_ex_gamma}
	\leavevmode
	\begin{enumerate}[(a)]
		\item For any $\tau \in \Xi_N$, the permutation $(\tau_\bullet\tau)\inv$ maps $\ex$
		      bijectively onto the set $\{j \in [1, N] \mid s_\tau(j) \neq + \infty\}$.
		\item For each $j \in \ex$ there exist $\tau, \tau'\in \Gamma_N$ such that $\tau' = \tau(k,
			      k+1)$ for some $k \in [1, N-1]$ with $\eta(\tau(k)) = \eta(\tau(k+1))$ and
		      $\tau_\bullet\tau(k) = j$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	\begin{enumerate}[(a)]
		\item Take $j\in [1, N]$ and let $k = (\tau_\bullet \tau)\inv(j)$. Since $\tau_\bullet$
		      preserves the level sets, we have $\eta(j) = \eta(\tau(k))$. So, $j \in \ex$ if and
		      only if $s(j) \neq + \infty$, if and only if $j$ is not the largest element of
		      $\eta\inv(\eta(j))$, if and only if $k$ is not the largest element of
		      $\tau\inv(\eta\inv(\eta(j))) = \eta_\tau\inv(\eta_\tau(k))$, if and only if $s_\tau(k)
			      \neq + \infty$.
		\item Write $j = O_{-}(j) \in \bbZ_{\geq 0}$. Then $i = p^m(j) \in [1, N]$ is such that $p(i)
			      = -\infty$, and $s^m(i) = j$. Since $i < s(j) < + \infty$, we may take $\tau = \tau_{i,
				      s(j) - 1}\in \Gamma_N$ and $\tau' = \tau_{i, s(j)} \in \Gamma_N$. Then, as we have
		      observed before, $\tau' = \tau(k, k+1)$ where $k = s(j) - i$, and $\tau(k) = i,
			      \tau(k+1) = s(j)$. Thus, $\eta(\tau(k)) = \eta(i) = \eta(s(j)) = \eta(\tau(k+1))$.
		      Write $L = \eta\inv(\eta(\tau(k)))$. Since $\tau$ is increasing on $[1, k - 1]$, we
		      find that $\tau$ maps the elements of $[1, k] \cap \tau\inv(L)$ to $s(i), \dots,
			      s^m(i), i$ in that order. So, $\tau_\bullet\tau(k) = \tau_\bullet(i)$ equals the
		      $(m+1)$-st element of $L$, when $L$ is written in increasing order. Since $p(i) =
			      -\infty$, that element is $s^m(i) = j$.
	\end{enumerate}
\end{proof}

With this lemma out of the way, we can prove the following theorem, which proves the
necessary inclusions for \cref{thm:gy_main_result} parts (d) and (e).

\begin{theorem}\label{thm:intersections}
	Let $R$ be a symmetric CGL extension of length $N$.
	\begin{enumerate}[(a)]
		\item $\mcA_\tau \subseteq R \subseteq \mcA_\tau[E\inv_\tau]\subseteq \mcT_\tau \subseteq \Fract(R)$ for all $\tau \in \Xi_N$.
		\item $R$ is generated as a $\bbK$-algebra by $\{y_{\tau, k} \mid \tau \in \Gamma_N, k \in [1, N]\}$.
		\item Each $E_\tau$ is an Ore set in $R$, and $R[E\inv_\tau] = \mcA_\tau[E\inv_\tau]$.
		\item $R = \bigcap_{\tau \in \Gamma_N} R[E\inv_\tau] = \bigcap_{\tau\in\Gamma_N}\mcA_\tau[E\inv_\tau]$.
		\item Let $\binv$ be any subset of $\{k \in [1, N] \mid s(k) = +\infty \}$. Then
		      \begin{equation*}
			      R[y_k^{-1} \mid k \in \binv] = \bigcap_{\tau \in \Gamma_N} R[E\inv_\tau][y\inv_k \mid k \in \binv].
		      \end{equation*}
	\end{enumerate}
\end{theorem}
\begin{proof}
	\leavevmode
	\begin{enumerate}[(a)]
		\item The inclusions $\mcA_\tau \subseteq R$ and $\mcA_\tau[E\inv_\tau] \subseteq \mcT_\tau
			      \subseteq \Fract(R)$ are clear from the definitions. The remaining inclusion, $R
			      \subseteq \mcA_\tau[E\inv_\tau]$, will follow if we can show $x_{\tau(k)} \in
			      \mcA_\tau[E\inv_\tau]$ for all $k \in [1, N]$. To do this we proceed by induction on
		      $k$, using \cref{thm:homogeneous_primes}. If $p_\tau(k) = -\infty$, then $x_{\tau, k} =
			      y_{\tau, k} \in \mcA_\tau \subseteq \mcA_\tau[E\inv_\tau]$. This also covers the base
		      case, $k=1$. Otherwise,
		      \begin{equation*}
			      y_{\tau, k} = y_{\tau, p_\tau(k)}x_{\tau(k)} - c_{\tau, k}
		      \end{equation*}
		      %
		      for some $c_{\tau, k} \in R_{\tau, k-1}$. By induction, $c_{\tau, k} \in
			      \mcA_\tau[E\inv_\tau]$, and hence
		      \begin{equation*}
			      x_{\tau(k)} = y_{\tau, p_\tau(k)}\inv (y_{\tau, k} + c_{\tau, k}) \in \mcA_\tau[E\inv_\tau],
		      \end{equation*}
		      %
		      because $y_{\tau, p_\tau(k)} \in E_\tau$ as $s_\tau(p_\tau(k)) = k \neq +\infty$.
		\item For each $k \in [1, N]$ we have $x_k = y_{[k , k]}$. By \cref{lem:y_tauk_y_brackets},
		      we have that $y_{\tau, 1}$ is a scalar multiple of $y_{[k,k]}$, where $\tau =
			      \tau_{k,k} \in \Gamma_N$.
		\item Recall that we showed using \cref{lem:ore_set_ore_extension} that $E_\tau$ was an Ore
		      set in $R$. Then the inclusions $\mcA_\tau \subseteq R \subseteq \mcA_\tau[E\inv_\tau]$
		      imply the equality $R[E\inv_\tau] = \mcA_\tau[E\inv_\tau]$.
		\item The second equality is just part (c). Since $R \subseteq R[E\inv_\tau]$ for all $\tau
			      \in \Gamma_N$, it suffices to prove that $v\in R$ for any $v \in \bigcap_{\tau\in
				      \Gamma_N} R[E\inv_\tau]$. We may assume $v$ to be nonzero. For each $\tau \in
			      \Gamma_N$, let
		      \begin{equation*}
			      \prod_{l \in [1, N]}y_{\tau, l}^{m_{\tau, l}}
		      \end{equation*}
		      %
		      be a minimal denominator of $v$ with respect to the localization $R[E\inv_\tau]$. So,
		      all $m_{\tau, l} \in \bbZ_{\geq 0}$ and $m_{\tau, l} = 0$ when $s_\tau(l) = + \infty$.
		      We now claim that for all $\tau, \tau' \in \Gamma_N$ such that $\tau' = \tau(k, k+1)$
		      for some $k \in [1, N- 1]$:
		      \begin{enumerate}
			      \item $m_{\tau, (\tau_\bullet\tau)\inv(j)} = m_{\tau', ((\tau')_\bullet\tau')\inv(j)}$ for all $j \in [1, N]$.
			      \item If $\eta(\tau(k)) = \eta(\tau(k+1))$, then $m_{\tau, k} = 0$.
		      \end{enumerate}
		      %
		      Indeed, if $\eta(\tau(k)) = \eta(\tau(k + 1))$, then this follows from
		      \cref{lem:tau_bullet,thm:minimal_denominators}. Otherwise, we obtain from
		      \cref{thm:y_prime_swapped_cgl} that $y_{\tau', j} = y_{\tau, (k, k+1)j}$ for all $j\in
			      [1, N]$. Consequently, $E_\tau = E_{\tau'}$, and $m_{\tau', l} = m_{\tau, (k, k+1)j}$
		      for all $j \in [1, N]$. The claim then follows from \cref{lem:tau_bullet} (c).

		      By using the total order on $\Gamma_N$, the first part of the claim then shows that
		      \begin{equation*}
			      m_{\sigma, (\sigma_\bullet\sigma)\inv(j)} = m_{\tau, (\tau_\bullet\tau)\inv(j)}
		      \end{equation*}
		      %
		      for all $\sigma, \tau \in \Gamma_N$ and $j \in [1, N]$. Because of
		      \cref{lem:tau_bullet_ex_gamma} (b), we can find $\tau, \tau' \in \Gamma_N$ such that
		      $\tau' = \tau(k, k+1)$ for some $k\in[1, N-1]$ with $\eta(\tau(k)) = \eta(\tau(k+1))$
		      and $\tau_\bullet(\tau(k)) = j$, for any $j \in \ex$. So, the second part of the claim
		      then implies that $m_{\tau, (\tau_\bullet\tau)\inv(j)} = 0$, and hence $m_{\sigma,
					      (\sigma_\bullet\sigma)\inv(j)} = 0$ for all $\sigma\in \Gamma_N$. In particular, this
		      holds for $\tau = \id$, and it follows that $v \in R$.
		\item Again, one inclusion is clear. It suffices to show $v \in R[y_k\inv \mid k \in \binv]$
		      for
		      \begin{equation*}
			      v \in \bigcap_{\tau \in \Gamma_N} R[E_\tau\inv][y_k\inv \mid k \in \binv].
		      \end{equation*}
		      %
		      For each $\tau \in \Gamma_N$, we can write $v = xy\inv$ for some $x \in R[E\inv_\tau]$
		      and $y$ in the multiplicative set generated by $\{y_k \mid k \in \binv\}$. Now, we can
		      choose $y$ to be the same for each $\tau \in \Gamma_N$, and hence $vy \in
			      R[E\inv_\tau]$ for all $\tau \in \Gamma_N$ (cf. \cref{lem:ore_set_properties}). Thus,
		      $vy\in R$ by part (d), and $v \in R[y_k\inv \mid k \in \binv]$ as we needed to show.
	\end{enumerate}
\end{proof}

Proving parts (d) and (e) of \cref{thm:gy_main_result}, is now just a matter of putting
together the inclusions from \cref{thm:intersections,thm:quantum_laurent} with some
simple observations.
\begin{proof}[Proof of \cref{thm:gy_main_result} parts (d) and (e).]
	First observe that for each $\tau\in \Xi_N$, we have
	\begin{equation*}
		E_\tau = \{\xi M_\tau(f) \mid \xi \in \bbK^\times, f \in \sum_{j \in \ex} \bbZ_{\geq 0} e_j\}.
	\end{equation*}
	%
	Indeed, the right-hand side is multiplicatively generated by $\bbK^\times$ together
	with the set $\{ M_\tau(e_j) \mid j \in \ex\}$. By \cref{lem:tau_bullet_ex_gamma} (a),
	this last set is the same as the set
	\begin{equation*}
		\{ \wh{M}_\tau(e_j) \mid j \in [1, N],\, s_\tau(j) \neq + \infty\} = \{ \oy_{\tau, j} \mid j \in [1, N],\, s_\tau(j) \neq + \infty\}.
	\end{equation*}

	As noted in the proof of \cref{thm:intersections}, for each $j \in [1, N]$
	\cref{thm:y_square_brackets} implies $x_j = \oy_{[j, j]} = \oy_{\tau_{j,j}, 1}$ where
	$\tau_{j,j} \in \Gamma_N$. Since, by \cref{thm:gy_main_result} (c), all the quantum
	seeds $(M_\tau, \tB_\tau)$ for $\tau \in \Xi_N$ are mutation-equivalent to each other,
	we find that the cluster algebra $\mcA(M, \tB, \emptyset)_{\bbK}$ contains all the
	generators of $R$, and hence
	\begin{equation*}
		R \subseteq \mcA(M, \tB, \emptyset)_{\bbK}.
	\end{equation*}
	%
	The quantum Laurent phenomenon (\cref{thm:quantum_laurent}) yields
	\begin{equation*}
		\mcA(M, \tB, \emptyset)_\bbK \subseteq \mcU (M, \tB, \emptyset)_{\bbK}.
	\end{equation*}
	%
	By our observation that $E_\tau$ is also generated by the $M(e_j), j\in \ex$ we find
	\begin{equation*}
		\mcU(M, \tB, \emptyset)_{\bbK} \subseteq \bigcap_{\tau \in \Gamma_N} R[E\inv_\tau].
	\end{equation*}
	%
	These three inclusions, together with \cref{thm:intersections} (d) then give
	\begin{equation*}
		R \subseteq \mcA(M, \tB, \emptyset)_{\bbK} \subseteq \mcU (M, \tB, \emptyset)_{\bbK}\subseteq \bigcap_{\tau \in \Gamma_N} R[E\inv_\tau] = R,
	\end{equation*}
	yielding the equalities
	\begin{equation*}
		R = \mcA(M, \tB, \emptyset)_{\bbK} = \mcU (M, \tB, \emptyset)_{\bbK}
	\end{equation*}
	%
	of \cref{thm:gy_main_result} (d). In the same way, one obtains the inclusions
	\begin{equation*}
		R[y_k\inv \mid k \in \binv] \subseteq \mcA(M, \tB, \binv)_{\bbK} \subseteq \mcU(M, \tB, \binv)_{\bbK} \subseteq \bigcap_{\tau \in \Gamma} R[y_k\inv \mid k \in \binv][E\inv_\tau] ,
	\end{equation*}
	%
	from which we obtain \cref{thm:gy_main_result} (e), after applying
	\cref{thm:intersections} (e).
\end{proof}
